---
title: "CVR Cleaning Quality Analysis"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    output_dir <- here::here("output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(here)
library(dplyr)
library(knitr)
library(tidyverse)
library(ggplot2)

report_project_dir <- here::here()
report_clean_data_dir <- file.path(report_project_dir, "data", "clean")

source(file.path(report_project_dir, "config.R"))
source(file.path(report_project_dir, "code", "functions.R"))

input_files <- c(
  file.path(report_clean_data_dir, "clean_winner_data_kfst.rds"),
  file.path(report_clean_data_dir, "clean_winner_data_kfst_name_matched.rds"),
  file.path(report_clean_data_dir, "clean_buyer_data_kfst_name_matched.rds"),
  file.path(report_clean_data_dir, "clean_winner_data_ot.rds"),
  file.path(report_clean_data_dir, "clean_winner_data_ot_name_matched.rds"),
  file.path(report_clean_data_dir, "clean_buyer_data_ot_name_matched.rds")
)

missing_files <- input_files[!file.exists(input_files)]

if (length(missing_files) > 0) {
  stop(
    "Run the cleaning and matching scripts first. Missing files: ",
    paste(missing_files, collapse = ", ")
  )
}

kfst_clean <- readRDS(input_files[1])
kfst_matched <- readRDS(input_files[2])
kfst_buyer_matched <- readRDS(input_files[3])
ot_clean <- readRDS(input_files[4])
ot_matched <- readRDS(input_files[5])
ot_buyer_matched <- readRDS(input_files[6])

# Graph settings
theme_set(theme_light())
theme_update(plot.title = element_text(hjust = 0.5, face = "bold"))
theme_update(plot.subtitle = element_text(hjust = 0.5))
```

<style>
body {
  color: #24323d;
  font-size: 16px;
  line-height: 1.6;
}

h1, h2, h3 {
  color: #17324d;
}

.section-note {
  background: #f4f8fb;
  border-left: 5px solid #2f6f9f;
  border-radius: 4px;
  margin: 1.2rem 0;
  padding: 0.9rem 1.1rem;
}

.warning-note {
  background: #fff7e8;
  border-left: 5px solid #d88916;
  border-radius: 4px;
  margin: 1.2rem 0;
  padding: 0.9rem 1.1rem;
}

.flow {
  align-items: stretch;
  display: grid;
  gap: 0.6rem;
  grid-template-columns: 1fr auto 1fr auto 1fr auto 1fr auto 1fr;
  margin: 1.5rem 0 1rem;
}

.flow-step {
  align-items: center;
  background: #edf5fa;
  border: 2px solid #2f6f9f;
  border-radius: 8px;
  display: flex;
  justify-content: center;
  min-height: 88px;
  padding: 0.7rem;
  text-align: center;
}

.flow-arrow {
  align-items: center;
  color: #2f6f9f;
  display: flex;
  font-size: 1.6rem;
  font-weight: 700;
}

.ot-flow {
  background: #fff7e8;
  border: 2px solid #d88916;
  border-radius: 8px;
  margin: 0.7rem auto 1.5rem;
  max-width: 760px;
  padding: 0.8rem 1rem;
  text-align: center;
}

.ot-label {
  color: #a45f00;
  display: block;
  font-size: 0.85rem;
  font-weight: 700;
  letter-spacing: 0.04em;
  margin-bottom: 0.2rem;
  text-transform: uppercase;
}

table {
  margin-bottom: 1.5rem;
  width: 100%;
}

thead {
  background: #17324d;
  color: white;
}

th, td {
  padding: 0.55rem 0.7rem !important;
  vertical-align: top !important;
}

tbody tr:nth-child(even) {
  background: #f5f7f9;
}

@media (max-width: 900px) {
  .flow {
    grid-template-columns: 1fr;
  }

  .flow-arrow {
    justify-content: center;
    transform: rotate(90deg);
  }
}
</style>

# Introduction
In this note, I summarise the CVR number cleaning process for the KFST and OpenTender datasets. I also describe the name-matching process and provide some examples of how names are cleaned and matched. I also provide summary tables of the cleaning and matching results for both datasets.

# Process overview

Both datasets follow the same main process. OpenTender needs one extra check for winner names that may contain several firms.

<div class="flow">
  <div class="flow-step"><strong>1. Clean source CVRs</strong></div>
  <div class="flow-arrow">&rarr;</div>
  <div class="flow-step"><strong>2. Expand multiple winners</strong></div>
  <div class="flow-arrow">&rarr;</div>
  <div class="flow-step"><strong>3. Find candidates with a name but no CVR</strong></div>
  <div class="flow-arrow">&rarr;</div>
  <div class="flow-step"><strong>4. Match names to the CVR register</strong></div>
  <div class="flow-arrow">&rarr;</div>
  <div class="flow-step"><strong>5. Keep the match or send it to review</strong></div>
</div>

<div class="ot-flow">
  <span class="ot-label">OpenTender only</span>
  Before fuzzy matching, identify rows that might contain multiple firm names and split them if necessary.
</div>

# Matching process

The process follows the approach in *Bisnode matching documentation_V7*. It starts with strict exact matches. It then makes the names more general. Rows that match are removed before the next step. The same cleaning is applied to the winner names and to the registered main names and binames in the CVR keys. 

This section illustrates how the matching names are created in the winner data.

## Step 1: `winner_name_basic`
The first matching name is called `winner_name_basic`. To get this name, I

1. Convert to lowercase
2. Remove spaces at the start and end of the string
3. Replace Danish and other accented letters with a common spelling
4. Standardise legal forms, after detecting them as a standalone term (i.e. not as part of another word)

The keys for step (3) and (4) are below.

```{r letter-standardisation}
letter_standardisation <- tibble::tribble(
  ~Original, ~Replacement,
  "ø", "oe",
  "æ", "ae",
  "å", "aa",
  "ö", "oe",
  "ä", "ae",
  "á or à", "a",
  "é or è", "e"
)

kable(
  letter_standardisation,
  align = c("l", "l"),
  caption = "Letter standardisation"
)
```

```{r firm-type-standardisation}
firm_type_standardisation <- tibble::tribble(
  ~Terms.recognised, ~Stored.firm.type,
  "A/S, AS, A/, aktieselskab, aktieselskabet, GmbH", "a/s",
  "ApS, anpartsselskab, anpartsselskabet, AB", "aps",
  "I/S", "i/s",
  "K/S, KS", "k/s",
  "IVS", "ivs",
  "P/S", "p/s",
  "AMBA, A.M.B.A., A M B A", "amba",
  "SMBA, S.M.B.A.", "smba",
  "FMBA, F.M.B.A.", "fmba"
)

kable(
  firm_type_standardisation,
  align = c("l", "l"),
  caption = "Legal-form standardisation"
)
```

If no legal form is found, the firm type is stored as `Undetermined`. 

## Steps 2, 3, and 5: `winner_name_match` and `winner_name_no_spaces`

The next stage follows step 2 of the original documentation. It makes the following character changes:

- `oe` becomes `o`, and `aa` becomes `a`.
- `&` becomes `og`.
- `v/` becomes a space, while other slashes are removed.
- Hyphens and parentheses become spaces.
- Commas, periods, colons, and quotation marks are removed.
- Repeated spaces are collapsed.

The script also standardises selected whole words. It only replaces complete words. It does not replace text found inside a longer word.

```{r word-standardisation}
word_standardisation <- tibble::tribble(
  ~Original.words, ~Replacement,
  "international", "int",
  "and", "og",
  "av, of", "af",
  "limited", "ltd",
  "denmark, danmark", "dk",
  "holdings", "holding",
  "sweden, sverige", "se",
  "corporation", "corp",
  "company, comp", "co",
  "copenhagen, kobenhavn, cph, kopenhamn", "kbh",
  "i, ii, iii", "1, 2, 3"
)

kable(
  word_standardisation,
  align = c("l", "l"),
  caption = "Whole-word standardisation"
)
```

This set of cleaning produces:

1. `winner_name_match`, which keeps spaces and is used in fuzzy step 5.
2. `winner_name_no_spaces`, which is `winner_name_match` after removing spaces. This match variable is used for exact matching in steps 2 and 3.

## Steps 4 and 6: `winner_name_broad`

Exact step 4 and fuzzy step 6 use `winner_name_broad`. This variable is created from `winner_name_match`, but in addition: 

1. Removes common words with little information about firm identity.
2. Sorts remaining words alphabetically.
3. Joins words without spaces.

<div class="section-note">
<strong>Common words removed:</strong> af, arhus, asset, assets, broderna,
brdr, brodrerne, co, dansk, data, development, dk, ejendomsselskabet, finans,
forsikring, group, holding, hotels, hotel, int, invest, kbh,
komplementaerssaelskabet, livforsikringsselskab, management, media, nordic,
nordisk, og, scandinavia, scandinavian, se, service, services, skandia,
software, system, systems, ltd, filial, and for.
</div>

The four prepared name fields therefore have distinct uses:

```{r prepared-name-fields}
prepared_name_fields <- tibble::tribble(
  ~Prepared.field, ~Cleaning.level, ~Used.in,
  "winner_name_basic",
  "Lowercase; accented letters standardised; legal form extracted; extra spaces removed",
  "Exact step 1",
  
  "winner_name_no_spaces",
  "Built from winner_name_match; all spaces removed",
  "Exact steps 2 and 3",
  
  "winner_name_match",
  "Built from winner_name_basic; punctuation and selected words standardised; spaces retained",
  "Fuzzy step 5",
  
  "winner_name_broad",
  "Built from winner_name_match; common words removed; remaining words sorted and joined",
  "Exact step 4 and fuzzy step 6"
)

kable(
  prepared_name_fields,
  align = c("l", "l", "l"),
  caption = "Prepared name fields used in matching"
)
```

## Check against the original documentation

The current R code follows the documented core process. It applies the same letter changes, legal-form extraction, character changes, whole-word replacements, space removal, common-word removal, and word sorting.

The current implementation adds a few conservative safeguards:

- It recognises FMBA as an additional legal form.
- A fuzzy match is not accepted when several CVRs share the highest score.
- Repeated appearances of the same CVR are collapsed during candidate ranking.
  If the same prepared name points to different CVRs, those CVRs are retained
  and the match is marked as ambiguous instead of silently dropping one.

```{r matching-steps}
matching_steps <- tibble::tribble(
  ~Stage, ~Prepared.name, ~Comparison, ~Purpose,
  "Exact 1", "winner_name_basic", "Basic name and firm type", "Find names that already agree.",
  "Exact 2", "winner_name_no_spaces", "Prepared name without spaces and firm type", "Allow punctuation and spacing differences.",
  "Exact 3", "winner_name_no_spaces", "Prepared name without spaces", "Allow the firm type to differ.",
  "Exact 4", "winner_name_broad", "Broad name", "Remove common words and ignore word order.",
  "Fuzzy 5", "winner_name_match", "Prepared main names and binames", "Allow small spelling differences. The score must be above 85.",
  "Fuzzy 6", "winner_name_broad", "Broad main names and binames", "Use the broad name. Main names must score above 86. Binames must score above 89.",
  "Review", "—", "Remaining or uncertain rows", "Check fuzzy, ambiguous, and unmatched rows by hand."
)

kable(
  matching_steps,
  align = c("l", "l", "l", "l"),
  caption = "Name-matching stages"
)
```

## Real examples of name cleaning

The table below uses two winner names from the KFST matching candidates. OpenTender uses the same four name fields before its extra multiple-firm checks.

Exact steps 2 and 3 use the same cleaned name. Step 2 also requires the firm type to match. Step 3 ignores the firm type.

```{r real-name-cleaning-examples}
name_cleaning_example_names <- c(
  "XL-Byg Vorup Tømmerhandel & Byggecenter A/S",
  "Struensee & Co. Management Consulting P/S"
)

name_cleaning_examples <- kfst_matched %>%
  filter(
    flag_check_fuzzy_match,
    toupper(trimws(winner_country)) == "DK"
  ) %>%
  filter(winner_name %in% name_cleaning_example_names) %>%
  distinct(
    winner_name,
    winner_name_basic,
    winner_name_no_spaces,
    winner_name_broad,
    winner_firm_type
  ) %>%
  mutate(Example = match(winner_name, name_cleaning_example_names))

name_cleaning_examples_long <- bind_rows(
  name_cleaning_examples %>%
    transmute(
      Example,
      `Original winner name` = winner_name,
      Step = "Exact 1",
      `Name used for matching` = winner_name_basic,
      `Firm type rule` = paste("Must match", winner_firm_type)
    ),
  name_cleaning_examples %>%
    transmute(
      Example,
      `Original winner name` = winner_name,
      Step = "Exact 2",
      `Name used for matching` = winner_name_no_spaces,
      `Firm type rule` = paste("Must match", winner_firm_type)
    ),
  name_cleaning_examples %>%
    transmute(
      Example,
      `Original winner name` = winner_name,
      Step = "Exact 3",
      `Name used for matching` = winner_name_no_spaces,
      `Firm type rule` = "Ignored"
    ),
  name_cleaning_examples %>%
    transmute(
      Example,
      `Original winner name` = winner_name,
      Step = "Exact 4",
      `Name used for matching` = winner_name_broad,
      `Firm type rule` = "Ignored"
    )
) %>%
  mutate(
    Step = factor(
      Step,
      levels = c("Exact 1", "Exact 2", "Exact 3", "Exact 4")
    )
  ) %>%
  arrange(Example, Step) %>%
  select(-Example)

kable(
  name_cleaning_examples_long,
  align = c("l", "l", "l", "l"),
  caption = "Real examples of names used in the four exact-match steps"
)
```

Potential matches must also fit the tender date. The registered name can start
or end up to two years before or after the tender date. When several matches
remain, the script prefers:

1. A main registered name over a biname.
2. A name active on the tender date.
3. The oldest registered name.

## Simple examples

These examples come from the original matching documentation.

```{r matching-examples}
matching_examples <- tibble::tribble(
  ~Winner.name, ~Registered.name, ~Result,
  "Electro Oil Int", "Electro-Oil International", "Both become 'electrooilint'. They match at Exact 2.",
  "NGI Holdig", "NGI Holding", "The fuzzy score is 95. This is above the step 5 threshold."
)

kable(
  matching_examples,
  align = c("l", "l", "l"),
  caption = "Illustrative matching examples"
)
```

# KFST

## First CVR cleaning

The KFST source has separate fields for the winner CVR, winner name, and winner country. Some notes on the data:

* _The CVR numbers are generally already pretty clean_. While many rows feature punctuation, those punctuation marks (in particular the ';') are used to separate multiple winners. The script first checks whether a row has one or several valid CVRs. It then removes repeated CVRs and creates one row for each remaining CVR. After separation, `r format(sum(kfst_clean$flag_cvr_standardised, na.rm = TRUE), big.mark = ",")` rows had their CVR number standardised (removing white space, hyphens, alphabetical letters, punctuation). More detail available in the table below.

* A row is treated as a clear single winner when its CVR is exactly eight digits. Spaces can be removed first. Remaining non-missing rows may contain several winners. **For these rows, the script splits the CVR, name, and country fields together.** It then creates one row for each winner. This keeps each CVR beside the correct name and country.

```{r kfst-cleaning-summary}

kfst_clean %>% 
  summarise(across(starts_with("flag_cvr_"), sum)) %>% 
  kable(caption = "CVR number standardisation counts after multi-firm separation")

kfst_original_count <- kfst_clean %>%
  distinct(tender_id, lot_id) %>%
  summarise(Total = n()) %>%
  pull(Total)

kfst_clean_count <- kfst_clean %>%
  summarise(Total = n()) %>%
  pull(Total)

kfst_cleaning_summary <- bind_rows(
  kfst_clean %>%
    filter(source == "single winners") %>%
    summarise(
      Measure = "Original rows identified as single winners",
      Count = n(),
      Share = Count / kfst_original_count,
      Share.of = "Original winner rows"
    ),
  kfst_clean %>%
    filter(source == "multiple winners") %>%
    distinct(tender_id, lot_id) %>%
    summarise(
      Measure = "Original rows treated as multiple winners",
      Count = n(),
      Share = Count / kfst_original_count,
      Share.of = "Original winner rows"
    ),
  kfst_clean %>%
    filter(source == "multiple winners") %>%
    summarise(
      Measure = "Winner rows after multiple-winner expansion",
      Count = n(),
      Share = Count / kfst_clean_count,
      Share.of = "Final winner rows"
    ),
  kfst_clean %>%
    summarise(
      Measure = "Winner rows with a valid CVR after cleaning",
      Count = sum(valid_cvr, na.rm = TRUE),
      Share = Count / kfst_clean_count,
      Share.of = "Final winner rows"
    ),
  kfst_clean %>%
    summarise(
      Measure = "Winner rows with a missing CVR after cleaning",
      Count = sum(flag_missing_winner_cvr, na.rm = TRUE),
      Share = Count / kfst_clean_count,
      Share.of = "Final winner rows"
    )
) %>%
  mutate(
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  ) %>%
  rename(`Share of` = Share.of)

kable(
  kfst_cleaning_summary,
  align = c("l", "r", "r", "l"),
  caption = "KFST Cleaning"
)
```

## Candidates for name matching

A **matching candidate** is a Danish firm with a winner name but no cleaned CVR. There are **`r format(kfst_candidate_count, big.mark = ",")` KFST matching candidates**.

```{r kfst-candidates}
kfst_candidates <- kfst_matched %>%
  filter(
    flag_check_fuzzy_match,
    toupper(trimws(winner_country)) == "DK"
  )

kfst_candidate_count <- kfst_candidates %>%
  summarise(Count = n()) %>%
  pull(Count)
```


## Matching results
Most matches are exact. Fuzzy matches are less common, and some rows remain unmatched.
```{r kfst-matching-results}
kfst_matching_results <- kfst_candidates %>%
  mutate(
    Result = case_when(
      name_match_method == "exact" ~ "Exact match",
      name_match_method == "fuzzy" ~ "Fuzzy match",
      TRUE ~ "No automatic match"
    ),
    Result = factor(
      Result,
      levels = c("Exact match", "Fuzzy match", "No automatic match")
    )
  ) %>%
  count(Result, .drop = FALSE, name = "Count") %>%
  mutate(
    Share = Count / sum(Count),
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  kfst_matching_results,
  align = c("l", "r", "r"),
  caption = "KFST matching results"
)
```

The next table separates successful matches by the specific matching stage. `name_match_method` identifies exact or fuzzy matching. `name_match_step_code` identifies the specific step.

```{r kfst-matching-results-by-step}
kfst_step_results <- kfst_candidates %>%
  filter(flag_name_match_found) %>%
  count(
    name_match_method,
    name_match_step,
    name_match_step_code,
    name = "Count"
  ) %>%
  mutate(
    name_match_method = factor(
      name_match_method,
      levels = c("exact", "fuzzy")
    ),
    Share = Count / sum(Count)
  ) %>%
  arrange(name_match_method, name_match_step, name_match_step_code) %>%
  transmute(
    Method = tools::toTitleCase(as.character(name_match_method)),
    Step = name_match_step,
    `Matching stage` = name_match_step_code,
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    `Share of matches` = sprintf("%.1f%%", 100 * Share)
  ) 

kable(
  kfst_step_results,
  align = c("l", "r", "l", "r", "r"),
  caption = "KFST successful matches by matching step"
)
```

```{r kfst-review-summary}
kfst_review_summary <- bind_rows(
  kfst_candidates %>%
    filter(name_match_method == "fuzzy") %>%
    summarise(
      Review.reason = "Fuzzy match",
      Count = n(),
      Share = Count / kfst_candidate_count
    ),
  kfst_candidates %>%
    filter(name_match_method == "exact", flag_name_match_ambiguous) %>%
    summarise(
      Review.reason = "Ambiguous exact match",
      Count = n(),
      Share = Count / kfst_candidate_count
    ),
  kfst_candidates %>%
    filter(!flag_name_match_found) %>%
    summarise(
      Review.reason = "No automatic match",
      Count = n(),
      Share = Count / kfst_candidate_count
    )
) %>%
  mutate(
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  kfst_review_summary,
  align = c("l", "r", "r"),
  caption = "KFST rows that need name-match review"
)
```

<div class="warning-note">
<strong>A fuzzy match is not treated as fully confirmed.</strong> Fuzzy matches,
ambiguous exact matches, and unmatched rows remain in the manual-review file.
</div>

## KFST buyer match quality

KFST buyer data do not contain buyer CVRs in the raw source. The buyer matching workflow therefore tries to recover buyer CVRs from the CVR-name key.

```{r kfst-buyer-match-quality}
kfst_buyer_candidates <- kfst_buyer_matched %>%
  filter(flag_check_fuzzy_match)

kfst_buyer_candidate_count <- kfst_buyer_candidates %>%
  summarise(Count = n()) %>%
  pull(Count)

kfst_buyer_status_results <- kfst_buyer_candidates %>%
  count(name_match_status, name = "Count") %>%
  mutate(
    Share = Count / kfst_buyer_candidate_count
  ) %>%
  arrange(desc(Count)) %>%
  transmute(
    Status = name_match_status,
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  kfst_buyer_status_results,
  align = c("l", "r", "r"),
  caption = "KFST buyer matching status"
)
```

There are **`r format(kfst_buyer_candidate_count, big.mark = ",")` KFST buyer
matching candidates**.


```{r kfst-buyer-match-type}
kfst_buyer_type_results <- kfst_buyer_candidates %>%
  mutate(
    Result = case_when(
      name_match_method == "exact" ~ "Exact match",
      name_match_method == "fuzzy" ~ "Fuzzy match",
      TRUE ~ "No automatic match"
    ),
    Result = factor(
      Result,
      levels = c("Exact match", "Fuzzy match", "No automatic match")
    )
  ) %>%
  count(Result, .drop = FALSE, name = "Count") %>%
  mutate(
    Share = Count / sum(Count),
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  kfst_buyer_type_results,
  align = c("l", "r", "r"),
  caption = "KFST buyer matches by match type"
)
```

```{r kfst-buyer-match-step}
kfst_buyer_step_results <- kfst_buyer_candidates %>%
  filter(flag_name_match_found) %>%
  count(
    name_match_method,
    name_match_step,
    name_match_step_code,
    name = "Count"
  ) %>%
  mutate(
    name_match_method = factor(
      name_match_method,
      levels = c("exact", "fuzzy")
    ),
    Share = Count / sum(Count)
  ) %>%
  arrange(name_match_method, name_match_step, name_match_step_code) %>%
  transmute(
    Method = tools::toTitleCase(as.character(name_match_method)),
    Step = name_match_step,
    `Matching stage` = name_match_step_code,
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    `Share of matches` = sprintf("%.1f%%", 100 * Share)
  )

kable(
  kfst_buyer_step_results,
  align = c("l", "r", "l", "r", "r"),
  caption = "KFST buyer successful matches by matching step"
)
```

```{r kfst-buyer-review-summary}
kfst_buyer_review_summary <- bind_rows(
  kfst_buyer_candidates %>%
    filter(name_match_method == "fuzzy") %>%
    summarise(
      Review.reason = "Fuzzy match",
      Count = n(),
      Share = Count / kfst_buyer_candidate_count
    ),
  kfst_buyer_candidates %>%
    filter(name_match_method == "exact", flag_name_match_ambiguous) %>%
    summarise(
      Review.reason = "Ambiguous exact match",
      Count = n(),
      Share = Count / kfst_buyer_candidate_count
    ),
  kfst_buyer_candidates %>%
    filter(!flag_name_match_found) %>%
    summarise(
      Review.reason = "No automatic match",
      Count = n(),
      Share = Count / kfst_buyer_candidate_count
    )
) %>%
  mutate(
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  kfst_buyer_review_summary,
  align = c("l", "r", "r"),
  caption = "KFST buyer rows that need name-match review"
)
```

# OpenTender

## First CVR cleaning

OpenTender has more variation in the winner CVR field. It can contain country
prefixes, spaces, repeated CVRs, and longer non-Danish identifiers.

The script first extracts distinct eight-digit CVRs. It only standardises
delimiters when a row has more than one distinct valid CVR. It then removes
repeated CVRs and creates one row for each remaining CVR.

Before name matching, the script can also fill a missing CVR when the same
winner name has exactly one valid CVR elsewhere in OpenTender. The source row is
kept for audit.

```{r ot-cleaning-summary}
ot_original_count <- ot_clean %>%
  distinct(row_id) %>%
  summarise(Total = n()) %>%
  pull(Total)

ot_clean_count <- ot_clean %>%
  summarise(Total = n()) %>%
  pull(Total)

ot_cleaning_summary <- bind_rows(
  ot_clean %>%
    filter(source == "single winner") %>%
    distinct(row_id) %>%
    summarise(
      Measure = "Original rows with zero or one valid CVR",
      Count = n(),
      Share = Count / ot_original_count,
      Share.of = "Original source rows"
    ),
  ot_clean %>%
    filter(source == "multiple confirmed winners") %>%
    distinct(row_id) %>%
    summarise(
      Measure = "Original rows with several valid CVRs",
      Count = n(),
      Share = Count / ot_original_count,
      Share.of = "Original source rows"
    ),
  ot_clean %>%
    filter(source == "multiple confirmed winners") %>%
    summarise(
      Measure = "Winner rows after multiple-CVR expansion",
      Count = n(),
      Share = Count / ot_clean_count,
      Share.of = "Final winner rows"
    ),
  ot_clean %>%
    summarise(
      Measure = "Missing CVRs filled from the same winner name",
      Count = sum(flag_fill_missing_cvr, na.rm = TRUE),
      Share = Count / ot_clean_count,
      Share.of = "Final winner rows"
    ),
  ot_clean %>%
    summarise(
      Measure = "Winner rows with a valid CVR before name matching",
      Count = sum(valid_cvr, na.rm = TRUE),
      Share = Count / ot_clean_count,
      Share.of = "Final winner rows"
    ),
  ot_clean %>%
    summarise(
      Measure = "Winner rows with a missing CVR before name matching",
      Count = sum(flag_missing_winner_cvr, na.rm = TRUE),
      Share = Count / ot_clean_count,
      Share.of = "Final winner rows"
    )
) %>%
  mutate(
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  ) %>%
  rename(`Share of` = Share.of)

kable(
  ot_cleaning_summary,
  align = c("l", "r", "r", "l"),
  caption = "OpenTender first-pass cleaning"
)
```

## Candidates for name matching

The OpenTender definition is the same as the KFST definition. A candidate is a
Danish winner with a name but no cleaned CVR.

OpenTender can later split one source row into several firms. Candidate counts
therefore use distinct source `row_id` values.

```{r ot-candidates}
ot_candidates <- ot_matched %>%
  filter(
    flag_check_fuzzy_match,
    toupper(trimws(winner_country)) == "DK"
  )

ot_candidate_count <- ot_candidates %>%
  distinct(row_id) %>%
  summarise(Count = n()) %>%
  pull(Count)
```

There are **`r format(ot_candidate_count, big.mark = ",")` OpenTender matching
candidates**.


## OpenTender multiple-firm checks

OpenTender first uses the same four whole-name exact stages as KFST. It then
does two extra checks before fuzzy matching.

### Remove consortium language

Some rows contain words such as *consortium*, *joint venture*, or *JV*. The script removes this wording from a temporary copy of the full name. It then repeats the four exact matching stages above on this cleaned name.

### Test possible name splits

The OpenTender data are ambiguous as to whether and how multiple firm names are separated. Identifying precisely whether a row contains multiple firm names is challenging, since by visual inspection of the data the separators between firms are inconsistent and aren't obviously not part of a single firm name. For example, the firm name "Stenner & Sons" could plausibly be one firm "Stenner & Sons" or two firms "Stenner" and "Sons". 

Being too generous with identifying possible multi-firm rows is a major risk, since we could have many false positives in the final analysis dataset. **To minimise the risk of false positives**, I opted for a conservative flag for potential multiple firm status. A row is eligible for multi-firm separation ONLY when:

- It contains collaboration language (e.g. `consortium`, `joint venture`, and other variants); OR
- It contains at least two legal forms (e.g. `A/S` and  `ApS` both present in the row). 

After identifying candidate rows, I then create all possible splits of the provided firm name at plausible boundaries. The table below illustrates how this process works for the example "Firm A, Firm B & Firm C".  

```{r eg-splitting-process}
partition_example <- make_name_partitions("Firm A, Firm B & Firm C")
partition_example$partitions %>% 
  kable(caption = "Partition Example")
```

The script tests possible splits at plausible boundaries (e.g. ampersand, comma, semi-colon, `og`, etc). It ONLY accepts a split when:

1. every segment has exactly ONE exact match
2. every segment maps to a different CVR
3. only one `partition_id` satisfies requirements (1) and (2).

For tractability, I make two assumptions. Firstly, firm names appear sequentially from left to right. This means I don't test the partition "Firm A & Firm C; Firm B" for the example above. Secondly, only rows with at most 5 identified delimiters are tested. This keeps the number of partitions capped at 31. 

Unclear rows stay unchanged and are sent off for review.

```{r ot-segmentation-summary}
ot_eligible_count <- ot_candidates %>%
  filter(flag_name_partition_eligible) %>%
  distinct(row_id) %>%
  summarise(Total = n()) %>%
  pull(Total)

ot_candidate_output_count <- ot_candidates %>%
  summarise(Total = n()) %>%
  pull(Total)

ot_segmentation_summary <- bind_rows(
  ot_candidates %>%
    filter(flag_name_partition_eligible) %>%
    distinct(row_id) %>%
    summarise(
      Measure = "Source rows eligible for the split test",
      Count = n(),
      Share = Count / ot_candidate_count,
      Share.of = "Matching candidates"
    ),
  ot_candidates %>%
    filter(flag_name_partition_expanded) %>%
    distinct(row_id) %>%
    summarise(
      Measure = "Source rows with one accepted split",
      Count = n(),
      Share = Count / ot_eligible_count,
      Share.of = "Rows eligible for the split test"
    ),
  ot_candidates %>%
    filter(flag_name_partition_expanded) %>%
    summarise(
      Measure = "Firm rows produced by accepted splits",
      Count = n(),
      Share = Count / ot_candidate_output_count,
      Share.of = "Winner rows after name matching"
    ),
  ot_candidates %>%
    filter(
      name_partition_status ==
        "not accepted: multiple complete partitions"
    ) %>%
    distinct(row_id) %>%
    summarise(
      Measure = "Source rows with several possible complete splits",
      Count = n(),
      Share = Count / ot_eligible_count,
      Share.of = "Rows eligible for the split test"
    )
) %>%
  mutate(
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  ) %>%
  rename(`Share of` = Share.of)

kable(
  ot_segmentation_summary,
  align = c("l", "r", "r", "l"),
  caption = "OpenTender multiple-firm split results"
)
```

### Examples of accepted splits

The examples below are selected directly from the current accepted results. One example is shown for each available eligibility reason.

```{r ot-segmentation-examples}
ot_segmentation_examples <- ot_candidates %>%
  filter(flag_name_partition_expanded) %>%
  group_by(
    row_id,
    winner_name_original,
    name_partition_eligibility_reason,
    proposed_name_partition
  ) %>%
  summarise(
    Separated.firms = paste(winner_name, collapse = "; "),
    Matched.CVRs = paste(winner_cvr_name_match, collapse = "; "),
    .groups = "drop"
  ) %>%
  arrange(
    name_partition_eligibility_reason,
    nchar(winner_name_original),
    row_id
  ) %>%
  group_by(name_partition_eligibility_reason) %>%
  slice_head(n = 1) %>%
  ungroup() %>%
  transmute(
    `Why tested` = name_partition_eligibility_reason,
    `Original winner name` = winner_name_original,
    `Accepted split` = proposed_name_partition,
    `Matched CVRs` = Matched.CVRs
  )

kable(
  ot_segmentation_examples,
  align = c("l", "l", "l", "l"),
  caption = "Examples of OpenTender winner-name splitting"
)
```

## Matching results

An accepted split creates several firm rows. The results below count the original source row once.

```{r ot-matching-results}
ot_candidate_results <- ot_candidates %>%
  group_by(row_id) %>%
  summarise(
    Result = case_when(
      any(flag_name_partition_expanded, na.rm = TRUE) ~ "Exact match",
      any(name_match_method == "exact", na.rm = TRUE) ~ "Exact match",
      any(name_match_method == "fuzzy", na.rm = TRUE) ~ "Fuzzy match",
      TRUE ~ "No automatic match"
    ),
    Ambiguous.exact = any(
      name_match_method == "exact" & flag_name_match_ambiguous,
      na.rm = TRUE
    ),
    .groups = "drop"
  )

ot_matching_results <- ot_candidate_results %>%
  mutate(
    Result = factor(
      Result,
      levels = c("Exact match", "Fuzzy match", "No automatic match")
    )
  ) %>%
  count(Result, .drop = FALSE, name = "Count") %>%
  mutate(
    Share = Count / sum(Count),
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  ot_matching_results,
  align = c("l", "r", "r"),
  caption = "OpenTender matching results"
)
```

The next table separates successful matches by the specific matching stage. It counts matched winner rows. When an accepted OpenTender partition creates several firms, each separated firm contributes one row.

```{r ot-matching-results-by-step}
ot_step_results <- ot_candidates %>%
  filter(flag_name_match_found) %>%
  count(
    name_match_method,
    name_match_step,
    name_match_step_code,
    name = "Count"
  ) %>%
  mutate(
    name_match_method = factor(
      name_match_method,
      levels = c("exact", "fuzzy")
    ),
    Share = Count / sum(Count)
  ) %>%
  arrange(name_match_method, name_match_step, name_match_step_code) %>%
  transmute(
    Method = tools::toTitleCase(as.character(name_match_method)),
    Step = name_match_step,
    `Matching stage` = name_match_step_code,
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    `Share of matches` = sprintf("%.1f%%", 100 * Share)
  )

kable(
  ot_step_results,
  align = c("l", "r", "l", "r", "r"),
  caption = "OpenTender successful matches by matching step"
)
```

```{r ot-review-summary}
ot_review_summary <- bind_rows(
  ot_candidate_results %>%
    filter(Result == "Fuzzy match") %>%
    summarise(
      Review.reason = "Fuzzy match",
      Count = n(),
      Share = Count / ot_candidate_count
    ),
  ot_candidate_results %>%
    filter(Ambiguous.exact) %>%
    summarise(
      Review.reason = "Ambiguous exact match",
      Count = n(),
      Share = Count / ot_candidate_count
    ),
  ot_candidate_results %>%
    filter(Result == "No automatic match") %>%
    summarise(
      Review.reason = "No automatic match",
      Count = n(),
      Share = Count / ot_candidate_count
    )
) %>%
  mutate(
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  ot_review_summary,
  align = c("l", "r", "r"),
  caption = "OpenTender rows that need name-match review"
)
```

<div class="warning-note">
<strong>The same review rule applies to OpenTender.</strong> Fuzzy matches,
ambiguous exact matches, and unresolved multiple-firm names still need review.
</div>

## OpenTender buyer match quality

OpenTender buyer data often already contain a cleaned buyer CVR. The matching workflow is only used for rows where the buyer CVR is missing but a buyer name is available. The tables below focus on those buyer name-matching candidates.

```{r ot-buyer-match-quality}
ot_buyer_candidates <- ot_buyer_matched %>%
  filter(flag_check_fuzzy_match)

ot_buyer_candidate_count <- ot_buyer_candidates %>%
  summarise(Count = n()) %>%
  pull(Count)

ot_buyer_status_results <- ot_buyer_candidates %>%
  count(name_match_status, name = "Count") %>%
  mutate(
    Share = Count / ot_buyer_candidate_count
  ) %>%
  arrange(desc(Count)) %>%
  transmute(
    Status = name_match_status,
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  ot_buyer_status_results,
  align = c("l", "r", "r"),
  caption = "OpenTender buyer matching status"
)
```

There are **`r format(ot_buyer_candidate_count, big.mark = ",")` OpenTender buyer matching candidates**.

```{r ot-buyer-match-type}
ot_buyer_type_results <- ot_buyer_candidates %>%
  mutate(
    Result = case_when(
      name_match_method == "exact" ~ "Exact match",
      name_match_method == "fuzzy" ~ "Fuzzy match",
      TRUE ~ "No automatic match"
    ),
    Result = factor(
      Result,
      levels = c("Exact match", "Fuzzy match", "No automatic match")
    )
  ) %>%
  count(Result, .drop = FALSE, name = "Count") %>%
  mutate(
    Share = Count / sum(Count),
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  ot_buyer_type_results,
  align = c("l", "r", "r"),
  caption = "OpenTender buyer matches by match type"
)
```

The OpenTender buyer matching script can split accepted multiple-buyer names into several final buyer rows. The table below counts final matched buyer rows, so accepted splits can contribute more than one row.

```{r ot-buyer-match-step}
ot_buyer_step_results <- ot_buyer_candidates %>%
  filter(flag_name_match_found) %>%
  count(
    name_match_method,
    name_match_step,
    name_match_step_code,
    name = "Count"
  ) %>%
  mutate(
    name_match_method = factor(
      name_match_method,
      levels = c("exact", "fuzzy")
    ),
    Share = Count / sum(Count)
  ) %>%
  arrange(name_match_method, name_match_step, name_match_step_code) %>%
  transmute(
    Method = tools::toTitleCase(as.character(name_match_method)),
    Step = name_match_step,
    `Matching stage` = name_match_step_code,
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    `Share of matches` = sprintf("%.1f%%", 100 * Share)
  )

kable(
  ot_buyer_step_results,
  align = c("l", "r", "l", "r", "r"),
  caption = "OpenTender buyer successful matches by matching step"
)
```

```{r ot-buyer-review-summary}
ot_buyer_review_summary <- bind_rows(
  ot_buyer_candidates %>%
    filter(name_match_method == "fuzzy") %>%
    summarise(
      Review.reason = "Fuzzy match",
      Count = n(),
      Share = Count / ot_buyer_candidate_count
    ),
  ot_buyer_candidates %>%
    filter(name_match_method == "exact", flag_name_match_ambiguous) %>%
    summarise(
      Review.reason = "Ambiguous exact match",
      Count = n(),
      Share = Count / ot_buyer_candidate_count
    ),
  ot_buyer_candidates %>%
    filter(!flag_name_match_found) %>%
    summarise(
      Review.reason = "No automatic match",
      Count = n(),
      Share = Count / ot_buyer_candidate_count
    )
) %>%
  mutate(
    Count = format(Count, big.mark = ",", scientific = FALSE, trim = TRUE),
    Share = sprintf("%.1f%%", 100 * Share)
  )

kable(
  ot_buyer_review_summary,
  align = c("l", "r", "r"),
  caption = "OpenTender buyer rows that need name-match review"
)
```

# Overall quality review
For a final analysis, I would only fully trust the first three steps of the exact matching procedure. Exact matching recovers many missing CVRs, but the match quality varies substantially by step. Early exact matches that retain firm type look relatively reliable, while later “exact” matches based on broad/generalised names can produce clear false positives, especially for buyers and OpenTender records. Ambiguous and fuzzy matches are correctly flagged for manual review, but they still populate the final CVR columns, so downstream analysis should not use `*_cvr_final` without filtering or separately handling `flag_manual_name_review == TRUE`. 

# Other quality analyses

## Potential typoes in CVR names
I’ve noticed that some firm names appear with multiple CVR numbers. In some cases these look like typos, since only one CVR number exists in virk.dk and the two differ by only one digit. In other cases, all the different CVR numbers exist in virk.dk and the numbers are completely different. I think these correspond to different arms of some larger firm (e.g. the investment arm versus the consulting arm; both listed under the same name in OpenTender but have different CVR numbers).

```{r multiple-cvr-number-by-name}

# KFST and OT typo analysis datasets
kfst_typo <- kfst_clean %>% 
  filter((!is.na(winner_cvr_clean) & winner_cvr_clean != "" & !is.na(winner_name) & winner_name != "") & valid_cvr)
ot_typo <- ot_clean %>% 
    filter((!is.na(winner_cvr_clean) & winner_cvr_clean != "" & !is.na(winner_name) & winner_name != "") & valid_cvr)

# For KFST
kfst_hist_data <- kfst_typo %>%
  summarise(n_cvr = n_distinct(winner_cvr_clean), 
            .by = winner_name) %>% 
  count(n_cvr, name = "Count") %>% 
  mutate(Share = round(Count / sum(Count), 4))

# For OpenTender
ot_hist_data <- ot_typo %>%
    summarise(n_cvr = n_distinct(winner_cvr_clean), 
              .by = winner_name) %>% 
    count(n_cvr, name = "Count") %>% 
    mutate(Share = round(Count / sum(Count), 4))

```

Of these, I test how many differ within-firm by only 1 digit. This suggests a typo.

```{r typo-count, fig.align='center'}
make_cvr_pairs <- function(data) {
  
  # Keep distinct name-CVR combinations and names linked to multiple CVRs
  cvr_name_key <- data %>%
    distinct(winner_name, winner_cvr_clean) %>%
    mutate(
      n_cvr = n_distinct(winner_cvr_clean),
      pair_id = row_number(),
      .by = winner_name
    ) %>%
    filter(n_cvr > 1) %>%
    arrange(desc(n_cvr), winner_name)
  
  # Create every unique CVR pair within each winner name
  cvr_pairs <- inner_join(
    cvr_name_key,
    cvr_name_key,
    by = "winner_name",
    suffix = c("_1", "_2"),
    relationship = "many-to-many"
  ) %>%
    filter(pair_id_1 < pair_id_2) %>%
    mutate(
      l_dist = stringdist::stringdist(
        winner_cvr_clean_1,
        winner_cvr_clean_2,
        method = "lv"
      )
    )
  
  return(cvr_pairs)
}


# Map over both datasets.
cvr_pairs <- map(list(kfst_typo, ot_typo),
                 make_cvr_pairs) %>%
  setNames(c("kfst", "ot")) %>% 
  bind_rows(., .id = "source")

# Convert to proportions
cvr_pair_hist <- cvr_pairs %>%
  count(source, l_dist, name = "count") %>%
  mutate(
    proportion = count / sum(count),
    .by = source
  )

# Create firm count label
firm_count_label <- cvr_pairs %>%
  distinct(source, winner_name) %>%
  count(source, name = "n_firms") %>%
  mutate(
    label = paste0(
      toupper(source),
      ": ",
      scales::comma(n_firms),
      " firms"
    )
  ) %>%
  summarise(label = paste(label, collapse = "\n")) %>%
  pull(label)

# Produce bar plot
ggplot(
  cvr_pair_hist,
  aes(x = l_dist, y = proportion, fill = source)
) +
  geom_col(position = "dodge") +
  annotate(
    "label",
    x = Inf,
    y = Inf,
    label = firm_count_label,
    hjust = 1.05,
    vjust = 1.1,
    size = 3.5
  ) +
  scale_x_continuous(
    breaks = sort(unique(cvr_pair_hist$l_dist))
  ) +
  scale_y_continuous(
    labels = scales::label_percent()
  ) +
  labs(
    title = "Levenshtein distance between CVRs for the same firm name",
    x = "Levenshtein distance",
    y = "Proportion",
    fill = "Dataset"
  ) +
  theme(
    legend.position = "bottom"
  )

```

## Improved fuzzy matching
We could improve the fuzzy matching by requiring that the second best candidate name is much worse than the first best candidate. This prevents fragile differences from being detected as highly likely matches.

```{r elbow-fuzzy-matching, fig.align='center', fig.width=11, fig.height=7}
elbow_examples <- kfst_matched %>%
  filter(winner_name %in% c(
    "Skovbon Consulting",
    "William Cook Europw Aps"
  )) %>%
  select(
    winner_name,
    starts_with("fuzzy_candidate_name_"),
    starts_with("fuzzy_candidate_score_")
  ) %>%
  distinct() %>%
  mutate(
    example = case_when(
      winner_name == "Skovbon Consulting" ~
        "Fragile match\nOriginal name: Skovbon Consulting",
      winner_name == "William Cook Europw Aps" ~
        "Strong elbow\nOriginal name: William Cook Europw Aps"
    )
  ) %>%
  tidyr::pivot_longer(
    starts_with("fuzzy_candidate_"),
    names_to = c(".value", "candidate_rank"),
    names_pattern = "fuzzy_candidate_(name|score)_(\\d)"
  ) %>%
  mutate(candidate_rank = as.integer(candidate_rank))

ggplot(
  elbow_examples,
  aes(x = candidate_rank, y = score)
) +
  geom_line(linewidth = 1, colour = "#36648B") +
  geom_point(size = 3, colour = "#36648B") +
  ggrepel::geom_label_repel(
    data = elbow_examples %>% filter(candidate_rank <= 2),
    aes(
      label = paste0(
        "Rank ", candidate_rank, ": ",
        stringr::str_wrap(name, width = 24),
        "\nScore: ", round(score, 1)
      )
    ),
    size = 3,
    lineheight = 1,
    seed = 123,
    nudge_x = 0.35,
    box.padding = 0.6,
    point.padding = 0.3,
    force = 2,
    min.segment.length = 0,
    max.overlaps = Inf,
    segment.colour = "#7a8791",
    fill = scales::alpha("white", 0.95)
  ) +
  facet_wrap(~example) +
  scale_x_continuous(breaks = 1:5) +
  scale_y_continuous(
    breaks = seq(70, 100, 10),
    limits = c(65, 103)
  ) +
  labs(
    title = "A high match score is not enough",
    subtitle = paste(
      "A reliable match should have a clear drop",
      "between the first and second candidates"
    ),
    x = "Candidate rank",
    y = "Name similarity score"
  ) +
  theme(
    strip.text = element_text(face = "bold"),
    panel.spacing = unit(1, "lines"),
    plot.margin = margin(10, 10, 10, 10)
  )
```

## Updating firm-cvr number key

The matching process relies on a key of firm names and CVR numbers that ends in
2020. I test whether this limits matching by comparing the unmatched rate across
tender years. The unmatched rate is the number of candidates without an
automatic match divided by all matching candidates in that year. This is more
useful than the unmatched count because the number of tenders changes over time.

For KFST, I use the tender publication year. For OpenTender, I use the year of
the first contract award publication. This is also the date used in the matching
process. OpenTender source rows are counted once, including rows that were later
split into several firms. Each panel shows its observed year range. The KFST
series begins in 2017 because there are no KFST matching candidates with an
earlier publication year.

```{r unmatched-candidates-by-year}
key_end_year <- 2020

kfst_tender_age <- kfst_candidates %>%
  transmute(
    Dataset = "KFST",
    Tender.year = as.integer(format(pub_date, "%Y")),
    Unmatched = !flag_name_match_found
  )

ot_tender_age <- ot_candidates %>%
  group_by(row_id) %>%
  summarise(
    Dataset = "OpenTender",
    Tender.year = as.integer(substr(
      first(tender_publications_firstdContractAwardDate),
      1,
      4
    )),
    Unmatched = !any(flag_name_match_found, na.rm = TRUE),
    .groups = "drop"
  )

tender_age_candidates <- bind_rows(
  kfst_tender_age,
  ot_tender_age
) %>%
  filter(!is.na(Tender.year))

unmatched_by_year <- tender_age_candidates %>%
  group_by(Dataset, Tender.year) %>%
  summarise(
    Candidates = n(),
    Unmatched.count = sum(Unmatched),
    Unmatched.rate = mean(Unmatched),
    .groups = "drop"
  ) %>%
  mutate(
    Key.period = if_else(
      Tender.year <= key_end_year,
      "Key covers this year",
      "After key coverage (2021+)"
    )
  )

ggplot(
  unmatched_by_year,
  aes(x = Tender.year, y = Unmatched.rate)
) +
  geom_vline(
    xintercept = key_end_year + 0.5,
    linetype = "dashed",
    colour = "#d88916"
  ) +
  geom_line(aes(group = 1), colour = "#7a8791", linewidth = 0.8) +
  geom_point(
    aes(fill = Key.period),
    shape = 21,
    size = 3,
    colour = "white",
    stroke = 0.5
  ) +
  facet_wrap(
    ~Dataset,
    ncol = 1,
    scales = "free_x"
  ) +
  scale_fill_manual(
    values = c(
      "Key covers this year" = "#2f6f9f",
      "After key coverage (2021+)" = "#d88916"
    )
  ) +
  scale_x_continuous(
    breaks = function(year_range) {
      if (diff(range(year_range)) <= 10) {
        seq(
          ceiling(min(year_range)),
          floor(max(year_range)),
          by = 1
        )
      } else {
        scales::breaks_width(2)(year_range)
      }
    }
  ) +
  scale_y_continuous(labels = scales::label_percent()) +
  labs(
    title = "Unmatched candidate rate by tender year",
    subtitle = "The firm-CVR key ends in 2020",
    x = "Tender year",
    y = "Share of candidates without an automatic match",
    fill = NULL
  ) +
  theme(
    legend.position = "bottom"
  )
```

```{r unmatched-candidates-by-key-period}
unmatched_by_key_period <- tender_age_candidates %>%
  mutate(
    Period = if_else(
      Tender.year <= key_end_year,
      "Up to 2020",
      "2021 onwards"
    ),
    Period = factor(
      Period,
      levels = c("Up to 2020", "2021 onwards")
    )
  ) %>%
  group_by(Dataset, Period) %>%
  summarise(
    Candidates = n(),
    Unmatched.count = sum(Unmatched),
    `Unmatched rate` = mean(Unmatched),
    .groups = "drop"
  ) %>%
  mutate(
    Candidates = format(
      Candidates,
      big.mark = ",",
      scientific = FALSE,
      trim = TRUE
    ),
    Unmatched.count = format(
      Unmatched.count,
      big.mark = ",",
      scientific = FALSE,
      trim = TRUE
    ),
    `Unmatched rate` = sprintf("%.1f%%", 100 * `Unmatched rate`)
  ) %>%
  rename(
    Unmatched = Unmatched.count
  )

kable(
  unmatched_by_key_period,
  align = c("l", "l", "r", "r", "r"),
  caption = "Unmatched candidates before and after the end of the key"
)
```

## Verifying data
We could also use the CVR number to name key to verify that the name in the source data is correct. This would help validate the data splitting process I've undertaken, for example.
