---
title: "CVR Cleaning Summary Statistics"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(file.path(dirname(inputFile), ".."), mustWork = TRUE)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(here)
library(dplyr)
library(knitr)
library(tidyverse)
library(ggplot2)

report_project_dir <- if (file.exists("config.R")) {
  getwd()
} else {
  normalizePath("..", mustWork = TRUE)
}
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)
report_clean_data_dir <- file.path(report_project_dir, "data", "clean")

source(file.path(report_project_dir, "config.R"))

input_files <- c(
  file.path(report_clean_data_dir, "clean_winner_data_kfst_name_matched.rds"),
  file.path(report_clean_data_dir, "clean_buyer_data_kfst_name_matched.rds"),
  file.path(report_clean_data_dir, "clean_winner_data_ot_name_matched.rds"),
  file.path(report_clean_data_dir, "clean_buyer_data_ot_name_matched.rds")
)

missing_files <- input_files[!file.exists(input_files)]

if (length(missing_files) > 0) {
  stop(
    "Run the cleaning scripts first. Missing files: ",
    paste(missing_files, collapse = ", ")
  )
}

winner_summary_cols <- c(
  "data_source", "tender_id", "lot_id", "tender_amount", "lot_amount",
  "n_bidders", "award_date", "winner_number", "winner_cvr", "winner_cvr_clean",
  "winner_cvr_final", "buyer_name", "name_match_step", "name_match_method",
  "name_match_status", "name_match_step_code", "flag_name_match_found"
)

buyer_summary_cols <- c(
  "data_source", "tender_id", "lot_id", "tender_amount", "lot_amount",
  "n_bidders", "award_date", "buyer_number", "buyer_name", "buyer_cvr",
  "buyer_cvr_clean", "buyer_cvr_final"
)

parse_summary_date <- function(x) {
  x <- as.character(x)
  x[x == ""] <- NA_character_
  
  parsed <- suppressWarnings(lubridate::ymd(x))
  excel_serial <- !is.na(x) & str_detect(x, "^[0-9]+$")
  parsed[excel_serial] <- as.Date(as.numeric(x[excel_serial]), origin = "1899-12-30")
  
  parsed
}

prepare_winner_summary_data <- function(path, source_label) {
  data <- readRDS(path)
  
  if (!"winner_cvr_final" %in% names(data)) {
    stop("Matched winner file is missing winner_cvr_final: ", path)
  }

  if (!"winner_cvr_clean" %in% names(data)) {
    data$winner_cvr_clean <- NA_character_
  }
  
  data %>%
    mutate(
      data_source = source_label,
      tender_id = as.character(tender_id),
      lot_id = as.character(lot_id),
      award_date = parse_summary_date(award_date),
      winner_cvr_clean = as.character(winner_cvr_clean),
      winner_cvr_final = as.character(winner_cvr_final),
      winner_cvr = coalesce(winner_cvr_final, winner_cvr_clean),
      tender_amount = suppressWarnings(as.numeric(tender_amount)),
      lot_amount = suppressWarnings(as.numeric(lot_amount)),
      n_bidders = suppressWarnings(as.numeric(n_bidders))
    ) %>%
    select(any_of(winner_summary_cols))
}

prepare_buyer_summary_data <- function(path, source_label) {
  data <- readRDS(path)
  
  if (!"buyer_cvr_final" %in% names(data)) {
    stop("Matched buyer file is missing buyer_cvr_final: ", path)
  }

  if (!"buyer_cvr_clean" %in% names(data)) {
    data$buyer_cvr_clean <- NA_character_
  }
  
  data %>%
    mutate(
      data_source = source_label,
      tender_id = as.character(tender_id),
      lot_id = as.character(lot_id),
      award_date = parse_summary_date(award_date),
      buyer_cvr_clean = as.character(buyer_cvr_clean),
      buyer_cvr_final = as.character(buyer_cvr_final),
      buyer_cvr = coalesce(buyer_cvr_final, buyer_cvr_clean),
      tender_amount = suppressWarnings(as.numeric(tender_amount)),
      lot_amount = suppressWarnings(as.numeric(lot_amount)),
      n_bidders = suppressWarnings(as.numeric(n_bidders))
    ) %>%
    select(any_of(buyer_summary_cols))
}

kfst_winners <- prepare_winner_summary_data(input_files[1], "KFST")
kfst_buyers <- prepare_buyer_summary_data(input_files[2], "KFST")
ot_winners <- prepare_winner_summary_data(input_files[3], "OpenTender")
ot_buyers <- prepare_buyer_summary_data(input_files[4], "OpenTender")

winner_data <- bind_rows(kfst_winners, ot_winners)
buyer_data <- bind_rows(kfst_buyers, ot_buyers)

# One row per tender lot, so tender/lot-level quantities are not repeated for
# each winner or buyer row.
lot_data <- winner_data %>%
  distinct(data_source, tender_id, lot_id, .keep_all = TRUE) %>%
  mutate(
    log_tender_amount = if_else(
      !is.na(tender_amount) & tender_amount > 0,
      log(tender_amount),
      NA_real_
    ),
    log_lot_amount = if_else(
      !is.na(lot_amount) & lot_amount > 0,
      log(lot_amount),
      NA_real_
    )
  )

theme_set(theme_light())
theme_update(plot.title = element_text(hjust = 0.5, face = "bold"))
theme_update(plot.subtitle = element_text(hjust = 0.5))

summary_inset <- function(data, value_col, digits = 2) {
  data %>%
    filter(!is.na(.data[[value_col]])) %>%
    summarise(
      label = paste0(
        "N = ", format(n(), big.mark = ","), "\n",
        "Mean = ", round(mean(.data[[value_col]]), digits), "\n",
        "Median = ", round(median(.data[[value_col]]), digits), "\n",
        "P25 = ", round(quantile(.data[[value_col]], 0.25, names = FALSE), digits), "\n",
        "P75 = ", round(quantile(.data[[value_col]], 0.75, names = FALSE), digits)
      ),
      .by = data_source
    )
}

histogram_with_inset <- function(data, value_col, x_label, title, bins = 30, digits = 2) {
  inset <- summary_inset(data, value_col, digits)

  ggplot(
    data %>% filter(!is.na(.data[[value_col]])),
    aes(x = .data[[value_col]])
  ) +
    geom_histogram(bins = bins, fill = "#2f6f9f", color = "white") +
    geom_label(
      data = inset,
      aes(x = Inf, y = Inf, label = label),
      inherit.aes = FALSE,
      hjust = 1.05,
      vjust = 1.1,
      size = 3,
      label.size = 0.2
    ) +
    facet_wrap(vars(data_source), scales = "free_y") +
    labs(
      title = title,
      x = x_label,
      y = "Count"
    )
}
```

<style>
body {
  color: #24323d;
  font-size: 16px;
  line-height: 1.6;
}

h1, h2, h3 {
  color: #17324d;
}

.section-note {
  background: #f4f8fb;
  border-left: 5px solid #2f6f9f;
  border-radius: 4px;
  margin: 1.2rem 0;
  padding: 0.9rem 1.1rem;
}

table {
  margin-bottom: 1.5rem;
  width: 100%;
}

thead {
  background: #17324d;
  color: white;
}

th, td {
  padding: 0.55rem 0.7rem !important;
  vertical-align: top !important;
}

tbody tr:nth-child(even) {
  background: #f5f7f9;
}

.overview-table {
  border-collapse: collapse;
  font-size: 0.95rem;
}

.overview-table caption {
  color: #17324d;
  font-weight: 700;
  margin-bottom: 0.6rem;
}
</style>

# Introduction

This note gives a first-pass set of descriptive statistics for the cleaned and matched KFST and OpenTender tender data. It is intended as an exploratory companion to the cleaning pipeline rather than a data quality report.

Tender and lot amount fields are source-specific. The tender-size summaries below use the natural log of positive numeric amounts. 

## Measurement of tender amounts
**For KFST**, there are four measures of tender/lot amount.

* `Estimat af samlet kontraktværdi - angivet i udbud` which is `estimated_tender_amount`. Measured in DKK. This is the estimated value of the tender stated in the contract notice. The estimate is performed by the contracting authority. Some contracts state the estimated value as a range, in which case the maximum is taken. For tenders with several lots, the estimated tender contract value is the sum of the estimated value of each individual lot. If a total estimated tender value is available in addition to estimates for each lot, and those two differ, then the sum of the lots is preferred.  Values below 1000DKK are removed and values stated in currencies other than DKK are converted to DKK. Amount excludes VAT. 
* `Estimat af delkontraktens kontraktværdi` which is `estimated_lot_amount`. Essentially the same principles as above, except for specific lots within the tender. Excludes VAT, converted to DKK, values below 1000DKK are removed, etc.
* `Endelig kontraktværdi` which is `final_tender_amount`. This is the final total amount recorded in the TED contract award notice ("bekendtgørelse om indgået kontrakt" in Danish). [Here](https://ted.europa.eu/da/notice/-/detail/224608-2022) is an example of what the contract document looks like, where tender amounts are taken from sections II.1.7 or V.2.4 (if the amounts disagree, KFST usually takes the number from V.2.4). If specific lot values are provided, then the sum of those are preferred to the `final_tender_amount`. Excludes VAT, converted to DKK, values below 1000DKK are removed. Upper limits of ranges are taken as the truth, where relevant.
* `Endelig værdi af delaftaler` which is `final_lot_amount`. Same as all other variables, but applies to individual lots. In cases where a single lot amount is missing and the total tender amount is known, the missing lot amount is imputed as the difference between the final tender amount and the sum of all the other final lot amounts

I have two variables: `tender_amount` and `lot_amount`. If the `final_*` amount is available, I use that, otherwise I fill missings with the `estimated_*`.

The fields are similar for **OpenTender**, except they are measured in Euros. Unfortunately I haven't found documentation with comparable detail, so I cannot confirm the precleaning rules applied.

# Overview

```{r overview-table}
valid_cvr <- function(x) {
  !is.na(x) & str_detect(x, "^\\d{8}$")
}

format_int <- function(x) {
  if_else(is.na(x), "n/a", format(round(x), big.mark = ",", scientific = FALSE))
}

format_decimal <- function(x, digits = 2) {
  if_else(is.na(x), "n/a", format(round(x, digits), nsmall = digits, scientific = FALSE))
}

format_mean_sd <- function(mean, sd, digits = 2) {
  paste0(
    format_decimal(mean, digits),
    "<br>[",
    format_decimal(sd, digits),
    "]"
  )
}

format_percent <- function(x, digits = 1) {
  if_else(
    is.na(x),
    "n/a",
    paste0(format(round(100 * x, digits), nsmall = digits, scientific = FALSE), "%")
  )
}

# Create valid CVR flag for winners and buyers
winner_data <- winner_data %>%
  mutate(flag_valid_winner_cvr = valid_cvr(winner_cvr))
buyer_data <- buyer_data %>% 
  mutate(flag_valid_buyer_cvr = valid_cvr(buyer_cvr))

# Years spanned by each dataset
year_span <- lot_data %>%
  mutate(year = lubridate::year(award_date)) %>%
  filter(!is.na(year)) %>%
  summarise(
    years_spanned = paste0(min(year), "-", max(year)),
    .by = data_source
  )


# Summary of winner CVR rows and unique winner firms
winner_cvr_summary <- winner_data %>%
  summarise(
    valid_winner_cvr_rows = sum(flag_valid_winner_cvr),
    unique_winner_firms = n_distinct(winner_cvr[flag_valid_winner_cvr]),
    .by = data_source
  )

# Tenders per winner
tenders_per_winner_cvr <- winner_data %>%
  filter(flag_valid_winner_cvr) %>%
  distinct(data_source, winner_cvr, tender_id) %>%
  count(data_source, winner_cvr, name = "n_tenders")

tenders_per_winner_summary <- tenders_per_winner_cvr %>%
  summarise(
    mean_tenders_per_winner_firm = mean(n_tenders),
    sd_tenders_per_winner_firm = sd(n_tenders),
    .by = data_source
  )

# Mean log value
log_value_summary <- lot_data %>%
  summarise(
    mean_log_tender_amount = mean(log_tender_amount, na.rm = TRUE),
    sd_log_tender_amount = sd(log_tender_amount, na.rm = TRUE),
    mean_log_lot_amount = mean(log_lot_amount, na.rm = TRUE),
    sd_log_lot_amount = sd(log_lot_amount, na.rm = TRUE),
    .by = data_source
  )

# Buyer CVR summayr
buyer_cvr_summary <- buyer_data %>%
  summarise(
    unique_buyers_by_cvr = if_else(
      sum(flag_valid_buyer_cvr) > 0,
      n_distinct(buyer_cvr[flag_valid_buyer_cvr]),
      NA_integer_
    ),
    .by = data_source
  )

tenders_per_buyer_cvr <- buyer_data %>%
  filter(valid_cvr(buyer_cvr)) %>%
  distinct(data_source, buyer_cvr, tender_id) %>%
  count(data_source, buyer_cvr, name = "n_tenders")

tenders_per_buyer_summary <- tenders_per_buyer_cvr %>%
  summarise(
    mean_tenders_per_buyer = mean(n_tenders),
    sd_tenders_per_buyer = sd(n_tenders),
    .by = data_source
  )

front_summary <- winner_cvr_summary %>%
  left_join(year_span, by = "data_source") %>%
  left_join(tenders_per_winner_summary, by = "data_source") %>%
  left_join(log_value_summary, by = "data_source") %>%
  left_join(buyer_cvr_summary, by = "data_source") %>%
  left_join(tenders_per_buyer_summary, by = "data_source") %>%
  transmute(
    `Data source` = data_source,
    `Valid winner CVR rows` = format_int(valid_winner_cvr_rows),
    `Unique winner firms` = format_int(unique_winner_firms),
    `Years spanned` = years_spanned,
    `Mean tenders per winner firm` = format_mean_sd(
      mean_tenders_per_winner_firm,
      sd_tenders_per_winner_firm
    ),
    `Mean log tender amount` = format_mean_sd(
      mean_log_tender_amount,
      sd_log_tender_amount
    ),
    `Mean log lot amount` = format_mean_sd(
      mean_log_lot_amount,
      sd_log_lot_amount
    ),
    `Unique buyers by CVR` = format_int(unique_buyers_by_cvr),
    `Mean tenders per buyer CVR` = format_mean_sd(
      mean_tenders_per_buyer,
      sd_tenders_per_buyer
    )
  )

kable(
  front_summary,
  caption = "Overview of cleaned tender data by source",
  align = c("l", rep("r", ncol(front_summary) - 1)),
  escape = FALSE,
  table.attr = 'class="overview-table"'
)
```

```{r winner-overview-groups}
winner_summary_groups <- bind_rows(
  winner_data %>%
    mutate(`Winner sample` = "Whole sample"),
  winner_data %>%
    filter(
      valid_cvr(winner_cvr_clean),
      !coalesce(flag_name_match_found, FALSE)
    ) %>%
    mutate(`Winner sample` = "Original CVRs only"),
  winner_data %>%
    filter(name_match_method == "exact", name_match_step %in% 1:3) %>%
    mutate(`Winner sample` = "Exact match steps 1-3"),
  winner_data %>%
    filter(
      coalesce(flag_name_match_found, FALSE),
      !(name_match_method == "exact" & name_match_step %in% 1:3)
    ) %>%
    mutate(`Winner sample` = "Other matching steps")
) %>%
  mutate(
    `Winner sample` = factor(
      `Winner sample`,
      levels = c(
        "Whole sample",
        "Original CVRs only",
        "Exact match steps 1-3",
        "Other matching steps"
      )
    )
  )

winner_group_lot_data <- winner_summary_groups %>%
  distinct(data_source, `Winner sample`, tender_id, lot_id, .keep_all = TRUE) %>%
  mutate(
    log_tender_amount = if_else(
      !is.na(tender_amount) & tender_amount > 0,
      log(tender_amount),
      NA_real_
    ),
    log_lot_amount = if_else(
      !is.na(lot_amount) & lot_amount > 0,
      log(lot_amount),
      NA_real_
    )
  )

winner_group_year_span <- winner_group_lot_data %>%
  mutate(year = lubridate::year(award_date)) %>%
  filter(!is.na(year)) %>%
  summarise(
    years_spanned = paste0(min(year), "-", max(year)),
    .by = c(data_source, `Winner sample`)
  )

winner_group_cvr_summary <- winner_summary_groups %>%
  summarise(
    valid_winner_cvr_rows = sum(flag_valid_winner_cvr),
    unique_winner_firms = n_distinct(winner_cvr[flag_valid_winner_cvr]),
    .by = c(data_source, `Winner sample`)
  )

winner_group_tenders_per_firm <- winner_summary_groups %>%
  filter(flag_valid_winner_cvr) %>%
  distinct(data_source, `Winner sample`, winner_cvr, tender_id) %>%
  count(data_source, `Winner sample`, winner_cvr, name = "n_tenders") %>%
  summarise(
    mean_tenders_per_winner_firm = mean(n_tenders),
    sd_tenders_per_winner_firm = sd(n_tenders),
    .by = c(data_source, `Winner sample`)
  )

winner_group_log_value_summary <- winner_group_lot_data %>%
  summarise(
    mean_log_tender_amount = mean(log_tender_amount, na.rm = TRUE),
    sd_log_tender_amount = sd(log_tender_amount, na.rm = TRUE),
    mean_log_lot_amount = mean(log_lot_amount, na.rm = TRUE),
    sd_log_lot_amount = sd(log_lot_amount, na.rm = TRUE),
    .by = c(data_source, `Winner sample`)
  )

winner_group_summary <- winner_group_cvr_summary %>%
  left_join(winner_group_year_span, by = c("data_source", "Winner sample")) %>%
  left_join(winner_group_tenders_per_firm, by = c("data_source", "Winner sample")) %>%
  left_join(winner_group_log_value_summary, by = c("data_source", "Winner sample")) %>%
  arrange(data_source, `Winner sample`) %>%
  transmute(
    `Data source` = data_source,
    `Winner sample`,
    `Valid winner CVR rows` = format_int(valid_winner_cvr_rows),
    `Unique winner firms` = format_int(unique_winner_firms),
    `Years spanned` = years_spanned,
    `Mean tenders per winner firm` = format_mean_sd(
      mean_tenders_per_winner_firm,
      sd_tenders_per_winner_firm
    ),
    `Mean log tender amount` = format_mean_sd(
      mean_log_tender_amount,
      sd_log_tender_amount
    ),
    `Mean log lot amount` = format_mean_sd(
      mean_log_lot_amount,
      sd_log_lot_amount
    )
  )

kable(
  winner_group_summary,
  caption = "Winner-side overview by CVR source group",
  align = c("l", "l", rep("r", ncol(winner_group_summary) - 2)),
  escape = FALSE,
  table.attr = 'class="overview-table"'
)
```

# CVR overlap
```{r winner-cvr-overlap}

# Split data into data sourcess
winner_data_ls <- winner_data %>% 
  split(.$data_source) 

# Extract unique valid CVRs
unique_valid_winner_cvr <- map(winner_data_ls, ~unique(.x$winner_cvr[.x$flag_valid_winner_cvr]))

# Take intersection
winner_cvr_intersection <- unique_valid_winner_cvr %>%
  purrr::reduce(intersect) %>%
  length()

# In KFST, not in OpenTender 
winner_cvr_kfst_only <- unique_valid_winner_cvr[[1]] %>%
  setdiff(unique_valid_winner_cvr[[2]]) %>%
  length() 

# In OpenTender, not in KFST 
winner_cvr_ot_only <- unique_valid_winner_cvr[[2]] %>%
  setdiff(unique_valid_winner_cvr[[1]]) %>%
  length() 

# Create table
winner_partition <- tibble::tibble(
  "Type" = "Winners",
  "Intersection" = winner_cvr_intersection,
  "KFST only" = winner_cvr_kfst_only,
  "OpenTender only" = winner_cvr_ot_only
)

```

```{r buyers-cvr-overlap}

# Split data into data sourcess
buyer_data_ls <- buyer_data %>% 
  split(.$data_source) 

# Extract unique valid CVRs
unique_valid_buyer_cvr <- map(buyer_data_ls, ~unique(.x$buyer_cvr[.x$flag_valid_buyer_cvr]))

# Take intersection
buyer_cvr_intersection <- unique_valid_buyer_cvr %>%
  purrr::reduce(intersect) %>%
  length()

# In KFST, not in OpenTender 
buyer_cvr_kfst_only <- unique_valid_buyer_cvr[[1]] %>%
  setdiff(unique_valid_buyer_cvr[[2]]) %>%
  length() 

# In OpenTender, not in KFST 
buyer_cvr_ot_only <- unique_valid_buyer_cvr[[2]] %>%
  setdiff(unique_valid_buyer_cvr[[1]]) %>%
  length() 

# Create table
buyer_partition <- tibble::tibble(
  "Type" = "buyers",
  "Intersection" = buyer_cvr_intersection,
  "KFST only" = buyer_cvr_kfst_only,
  "OpenTender only" = buyer_cvr_ot_only
)

```

```{r partition-table}

# Combine winner and buyer partitions
bind_rows(winner_partition, buyer_partition) %>%
  kable(
    caption = "Unique CVR number partition",
    align = c("l", rep("r", 3))
  )

```

# Tender Sizes

```{r amount-coverage-table}
amount_coverage <- bind_rows(
  lot_data %>%
    summarise(
      variable = "Tender amount",
      n_lots = n(),
      n_nonmissing = sum(!is.na(tender_amount)),
      n_positive = sum(!is.na(tender_amount) & tender_amount > 0),
      .by = data_source
    ),
  lot_data %>%
    summarise(
      variable = "Lot amount",
      n_lots = n(),
      n_nonmissing = sum(!is.na(lot_amount)),
      n_positive = sum(!is.na(lot_amount) & lot_amount > 0),
      .by = data_source
    )
) %>%
  transmute(
    `Data source` = data_source,
    `Amount variable` = variable,
    `Tender lots` = format_int(n_lots),
    `Non-missing` = format_int(n_nonmissing),
    `Non-missing share` = format_percent(n_nonmissing / n_lots),
    `Positive for log` = format_int(n_positive),
    `Positive share` = format_percent(n_positive / n_lots)
  )

kable(
  amount_coverage,
  caption = "Coverage of tender and lot amount variables",
  align = c("l", "l", rep("r", ncol(amount_coverage) - 2))
)
```

```{r log-tender-value-histogram, fig.height=5, fig.width=9}
histogram_with_inset(
  lot_data,
  value_col = "log_tender_amount",
  x_label = "Log tender amount",
  title = "Distribution of log tender amounts"
)
```

```{r log-lot-value-histogram, fig.height=5, fig.width=9}
histogram_with_inset(
  lot_data,
  value_col = "log_lot_amount",
  x_label = "Log lot amount",
  title = "Distribution of log lot amounts"
)
```

```{r bidder-count-histogram, fig.height=5, fig.width=9}
histogram_with_inset(
  lot_data,
  value_col = "n_bidders",
  x_label = "Number of bidders",
  title = "Distribution of bidders per tender lot"
)
```

# Years

```{r year-plot, fig.height=5, fig.width=9}
lot_data %>%
  mutate(year = lubridate::year(award_date)) %>%
  count(data_source, year, name = "n_lots") %>%
  filter(!is.na(year)) %>%
  ggplot(aes(x = year, y = n_lots)) +
  geom_col(fill = "#2f6f9f") +
  facet_wrap(vars(data_source), scales = "free_y") +
  labs(
    title = "Tender lots by award year",
    x = "Award year",
    y = "Tender lots"
  )
```

# Number of Tenders

```{r tender-count-summary}
tender_level_data <- lot_data %>%
  group_by(data_source, tender_id) %>%
  summarise(
    n_lots = n(),
    tender_amount = {
      nonmissing_tender_amount <- tender_amount[!is.na(tender_amount)]
      if (length(nonmissing_tender_amount) == 0) NA_real_ else nonmissing_tender_amount[1]
    },
    sum_lot_amount = if_else(sum(!is.na(lot_amount)) > 0, sum(lot_amount, na.rm = TRUE), NA_real_),
    .groups = "drop"
  )

tender_count_summary <- tender_level_data %>%
  group_by(data_source) %>% 
  summarise(
    total_tenders = n_distinct(tender_id),
    total_lots = sum(n_lots),
    mean_lots_per_tender = total_lots / total_tenders,
    median_lots_in_tender = median(n_lots),
    max_lots_per_tender = max(n_lots),
    n_multi_lot_tenders = n_distinct(tender_id[n_lots > 1]),
    share_multi_lot_tenders = n_distinct(tender_id[n_lots > 1]) / total_tenders,
    n_tenders_for_amount_correlation = sum(
      !is.na(tender_amount) & !is.na(sum_lot_amount)
    ),
    lot_sum_tender_amount_correlation = if_else(
      n_tenders_for_amount_correlation >= 2,
      cor(
        tender_amount,
        sum_lot_amount,
        use = "complete.obs"
      ),
      NA_real_
    )
  ) %>%
  ungroup() %>% 
  transmute(
    `Data source` = data_source,
    `Tenders` = format_int(total_tenders),
    `Tender lots` = format_int(total_lots),
    `Lots per tender` = format_decimal(mean_lots_per_tender),
    `Median lots in tender` = format_int(median_lots_in_tender),
    `Max lots per tender` = format_int(max_lots_per_tender),
    `Multi-lot tenders` = format_int(n_multi_lot_tenders),
    `Share multi-lot` = format_percent(share_multi_lot_tenders),
    `Tenders in amount correlation` = format_int(n_tenders_for_amount_correlation),
    `Corr(sum lot amount, tender amount)` = format_decimal(
      lot_sum_tender_amount_correlation,
      digits = 3
    )
  )

kable(
  tender_count_summary,
  caption = "Tender-level lot structure and amount consistency",
  align = c("l", rep("r", ncol(tender_count_summary) - 1)),
  escape = FALSE
)
```

# Distribution of Firms

```{r unique-winner-firms}
unique_winner_firms <- winner_data %>%
  filter(flag_valid_winner_cvr, !is.na(winner_cvr), winner_cvr != "") %>%
  summarise(
    unique_winner_firms = n_distinct(winner_cvr),
    winner_rows_with_cvr = n(),
    .by = data_source
  )

kable(
  unique_winner_firms,
  caption = "Unique winner firms identified by cleaned CVR"
)
```

```{r winner-firm-lot-distribution}
winner_lots_per_firm <- winner_data %>%
  filter(flag_valid_winner_cvr, !is.na(winner_cvr), winner_cvr != "") %>%
  distinct(data_source, winner_cvr, lot_id) %>%
  count(data_source, winner_cvr, name = "n_lots")

histogram_with_inset(
  winner_lots_per_firm,
  value_col = "n_lots",
  x_label = "Tender lots per winner firm",
  title = "Distribution of tender lots per winner firm"
)
```

# Tenders per Firm

```{r tenders-per-winner-firm}
tenders_per_firm <- winner_data %>%
  filter(flag_valid_winner_cvr, !is.na(winner_cvr), winner_cvr != "") %>%
  distinct(data_source, winner_cvr, tender_id) %>%
  count(data_source, winner_cvr, name = "n_tenders")

histogram_with_inset(
  tenders_per_firm,
  value_col = "n_tenders",
  x_label = "Tenders per winner firm",
  title = "Distribution of tenders per winner firm"
)
```

# Buyer Side

```{r buyer-summary}
buyer_summary <- buyer_data %>%
  filter(flag_valid_buyer_cvr, !is.na(buyer_name), buyer_name != "") %>%
  summarise(
    unique_buyers_by_name = n_distinct(buyer_name),
    unique_buyer_cvrs = n_distinct(buyer_cvr[!is.na(buyer_cvr) & buyer_cvr != ""]),
    buyer_rows = n(),
    .by = data_source
  )

kable(
  buyer_summary,
  caption = "Buyer-side summary"
)
```

```{r tenders-per-buyer}
tenders_per_buyer <- buyer_data %>%
  filter(flag_valid_buyer_cvr) %>%
  distinct(data_source, buyer_cvr, tender_id) %>%
  count(data_source, buyer_cvr, name = "n_tenders")

histogram_with_inset(
  tenders_per_buyer,
  value_col = "n_tenders",
  x_label = "Tenders per buyer name",
  title = "Distribution of tenders per buyer name"
)
```

# Multi-Winner Tenders

```{r multi-winner-lots}
multi_winner_lots <- winner_data %>%
  summarise(
    n_winners = n(),
    .by = c(data_source, tender_id, lot_id)
  )

histogram_with_inset(
  multi_winner_lots,
  value_col = "n_winners",
  x_label = "Winners per tender lot",
  title = "Distribution of winners per tender lot"
)
```

```{r multi-winner-lot-summary}
multi_winner_lot_summary <- multi_winner_lots %>%
  summarise(
    n_lots = n(),
    n_multi_winner_lots = sum(n_winners > 1),
    share_multi_winner_lots = mean(n_winners > 1),
    .by = data_source
  )

kable(
  multi_winner_lot_summary,
  digits = 3,
  caption = "Multi-winner tender lots"
)
```

```{r multi-winner-tenders}
multi_winner_tender_summary <- multi_winner_lots %>%
  summarise(
    tender_has_multiple_winners = any(n_winners > 1),
    .by = c(data_source, tender_id)
  ) %>%
  summarise(
    n_tenders = n(),
    n_multi_winner_tenders = sum(tender_has_multiple_winners),
    share_multi_winner_tenders = mean(tender_has_multiple_winners),
    .by = data_source
  )

kable(
  multi_winner_tender_summary,
  digits = 3,
  caption = "Tenders with at least one multi-winner lot"
)
```
