---
title: "CVR Key Concordance"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(file.path(dirname(inputFile), ".."), mustWork = TRUE)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

# Clean up environment
rm(list = ls())

# Packages
library(here)
library(data.table)
library(knitr)

# Paths
report_project_dir <- if (file.exists("config.R")) {
  getwd()
} else {
  normalizePath("..", mustWork = TRUE)
}
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)
report_cvr_key_dir <- file.path(report_project_dir, "data", "cvr_matching_data")

source(file.path(report_project_dir, "config.R"))

# Input files
official_old_file <- file.path(report_cvr_key_dir, "cvr_names_full.csv")
alternative_old_file <- file.path(report_cvr_key_dir, "cvr_binavne_full.csv")

official_new_files <- list.files(
  report_cvr_key_dir,
  pattern = "^cvr_names_virk_[0-9]{8}_[0-9]{6}\\.csv$",
  full.names = TRUE
)
alternative_new_files <- list.files(
  report_cvr_key_dir,
  pattern = "^cvr_binavne_virk_[0-9]{8}_[0-9]{6}\\.csv$",
  full.names = TRUE
)

if (length(official_new_files) == 0) {
  stop("No Virk-generated official-name key found.", call. = FALSE)
}

if (length(alternative_new_files) == 0) {
  stop("No Virk-generated alternative-name key found.", call. = FALSE)
}

official_new_file <- official_new_files[
  order(file.info(official_new_files)$mtime, decreasing = TRUE)
][1]
alternative_new_file <- alternative_new_files[
  order(file.info(alternative_new_files)$mtime, decreasing = TRUE)
][1]

missing_files <- c(
  official_old_file,
  official_new_file,
  alternative_old_file,
  alternative_new_file
)
missing_files <- missing_files[!file.exists(missing_files)]

if (length(missing_files) > 0) {
  stop("Missing required CVR key files: ", paste(missing_files, collapse = ", "))
}
```

## Inputs

```{r inputs}
kable(data.table(
  key_type = c("Official names", "Alternative names"),
  original_file = c(basename(official_old_file), basename(alternative_old_file)),
  latest_virk_file = c(basename(official_new_file), basename(alternative_new_file))
))
```

## Official Names

### Distinct CVR numbers
The below table summarises the number of distinct CVR numbers in each of the old and new keys, and shows how large the intersection is. 

```{r official}
# Read the original and new official-name keys exactly as stored.
official_old <- fread(
  official_old_file,
  select = c("cvr", "name"),
  colClasses = "character",
  encoding = "Latin-1"
)
official_new <- fread(
  official_new_file,
  select = c("cvr", "name"),
  colClasses = "character",
  encoding = "UTF-8"
)

setnames(official_old, "name", "old_name")
setnames(official_new, "name", "new_name")

# Keep one row per raw CVR-name pair so repeated validity periods do not drive
# the concordance counts.
official_old <- unique(official_old[!is.na(cvr) & !is.na(old_name)])
official_new <- unique(official_new[!is.na(cvr) & !is.na(new_name)])

# Coverage by CVR number.
official_old_cvrs <- unique(official_old$cvr)
official_new_cvrs <- unique(official_new$cvr)
official_common_cvrs <- intersect(official_old_cvrs, official_new_cvrs)

official_coverage <- data.table(
  measure = "distinct CVRs",
  old_n = length(official_old_cvrs),
  new_n = length(official_new_cvrs),
  in_both_n = length(official_common_cvrs),
  old_only_n = length(setdiff(official_old_cvrs, official_new_cvrs)),
  new_only_n = length(setdiff(official_new_cvrs, official_old_cvrs)),
  pct_old_in_new = scales::percent(length(official_common_cvrs) / length(official_old_cvrs), accuracy = 0.1),
  pct_new_in_old = scales::percent(length(official_common_cvrs) / length(official_new_cvrs), accuracy = 0.1)
)

```

### Firm name concordance
The below table summarises the how many firm names are exactly equal between the old and new keys, conditional on the CVR number being the same.
```{r name-concordance}

# Use the old key as the reference
official_old[, cvr_in_new_key := cvr %in% official_new_cvrs]
official_join <- official_new[official_old, on = "cvr"]

# Test equality of name
official_join[, firm_name_equal := new_name == old_name]

# Create summary table
official_name_concordance <- data.table(
  measure = c(
    "old CVR-name pairs",
    "old CVR-name pairs where CVR is in new key",
    "old CVR-name pairs with exact same name after CVR join"
  ),
  n = c(
    nrow(official_old),
    official_old[cvr_in_new_key == TRUE, .N],
    official_join[firm_name_equal == TRUE, .N]
  )
)
official_name_concordance[
  ,
  share_of_old_pairs := scales::percent(n / nrow(official_old), accuracy = 0.1)
]

kable(official_coverage)
kable(official_name_concordance)

```

## Alternative Names
### Distinct CVR numbers
The below table summarises the number of distinct CVR numbers in each of the old and new alternative name keys, and shows how large the intersection is. 
```{r alternative}
# Read the original and new alternative-name keys exactly as stored.
alternative_old <- fread(
  alternative_old_file,
  select = c("cvr", "binavn"),
  colClasses = "character",
  encoding = "Latin-1"
)
alternative_new <- fread(
  alternative_new_file,
  select = c("cvr", "binavn"),
  colClasses = "character",
  encoding = "UTF-8"
)

setnames(alternative_old, "binavn", "old_name")
setnames(alternative_new, "binavn", "new_name")

# Keep one row per raw CVR-name pair so repeated validity periods do not drive
# the concordance counts.
alternative_old <- unique(alternative_old[!is.na(cvr) & !is.na(old_name)])
alternative_new <- unique(alternative_new[!is.na(cvr) & !is.na(new_name)])

# Coverage by CVR number.
alternative_old_cvrs <- unique(alternative_old$cvr)
alternative_new_cvrs <- unique(alternative_new$cvr)
alternative_common_cvrs <- intersect(alternative_old_cvrs, alternative_new_cvrs)

alternative_coverage <- data.table(
  measure = "distinct CVRs",
  old_n = length(alternative_old_cvrs),
  new_n = length(alternative_new_cvrs),
  in_both_n = length(alternative_common_cvrs),
  old_only_n = length(setdiff(alternative_old_cvrs, alternative_new_cvrs)),
  new_only_n = length(setdiff(alternative_new_cvrs, alternative_old_cvrs)),
  pct_old_in_new = scales::percent(length(alternative_common_cvrs) / length(alternative_old_cvrs), accuracy = 0.1),
  pct_new_in_old = scales::percent(length(alternative_common_cvrs) / length(alternative_new_cvrs), accuracy = 0.1)
)

```

### Firm name concordance
The below table summarises the how many firm names are exactly equal between the old and new alternative name keys, conditional on the CVR number being the same.
```{r alt-name-concordance}

# Use the old key as the reference. Join to the new key on both CVR and the raw
# alternative name, so each old CVR-name pair is only counted once.
alternative_old[, cvr_in_new_key := cvr %in% alternative_new_cvrs]
alternative_new[, firm_name_equal := TRUE]
alternative_join <- alternative_new[alternative_old, 
                                    on = .(cvr, new_name = old_name)]
alternative_join[is.na(firm_name_equal), firm_name_equal := FALSE]

alternative_name_concordance <- data.table(
  measure = c(
    "old CVR-name pairs",
    "old CVR-name pairs with CVR in new key",
    "old CVR-name pairs with exact same name under same CVR"
  ),
  n = c(
    nrow(alternative_old),
    alternative_old[cvr_in_new_key == TRUE, .N],
    alternative_join[firm_name_equal == TRUE, .N]
  )
)
alternative_name_concordance[
  ,
  share_of_old_pairs := scales::percent(n / nrow(alternative_old), accuracy = 0.1)
]

kable(alternative_coverage)
kable(alternative_name_concordance)

```
