---
title: "Employment Data Quality"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(file.path(dirname(inputFile), ".."), mustWork = TRUE)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

# Clean up environment
rm(list = ls())

# Packages
library(here)
library(data.table)
library(tidyverse)
library(knitr)
library(fixest)
library(lubridate)
library(kableExtra)

# Paths
report_project_dir <- if (file.exists("config.R")) {
  getwd()
} else {
  normalizePath("..", mustWork = TRUE)
}
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)

source(file.path(report_project_dir, "config.R"))
clean_data_dir <- dirs$clean_data
key_dir <- dirs$cvr_key

valid_cvrs <- function(x) {
  x <- trimws(as.character(x))
  x <- gsub("[^0-9]", "", x)
  x <- x[grepl("^[0-9]{1,8}$", x)]
  unique(sprintf("%08d", as.integer(x)))
}

# 1 Load data
## 1.1 Firm data
firm_data_raw <- fread(file.path(clean_data_dir, "cvr_employment_history_virk.csv"))
setDT(firm_data_raw)

firm_data <- copy(firm_data_raw)
setDT(firm_data)
firm_data[, firm_by := year(lifecycle_start)]
firm_data[, firm_dy := year(lifecycle_end)]
firm_data[, firm_age := as.integer(floor(as.numeric(period_end - lifecycle_start) / 365.25))]
firm_data_ls <- firm_data %>% 
  split(.$frequency)

## 1.2 Tender data
data_ot <- readRDS(file.path(clean_data_dir, "clean_winner_data_ot_name_matched.rds")) %>% 
  mutate(data_source = "OpenTender")
data_kfst <- readRDS(file.path(clean_data_dir, "clean_winner_data_kfst_name_matched.rds")) %>% 
  mutate(data_source = "KFST")
data_ot_buyers <- readRDS(file.path(clean_data_dir, "clean_buyer_data_ot_name_matched.rds")) %>% 
  mutate(data_source = "OpenTender")
data_kfst_buyers <- readRDS(file.path(clean_data_dir, "clean_buyer_data_kfst_name_matched.rds")) %>% 
  mutate(data_source = "KFST")
data_tender <- rbindlist(list(data_ot, data_kfst), fill = TRUE, ignore.attr = TRUE) %>% 
  select(data_source, tender_id, lot_id, award_date, winner_cvr_final, tender_amount, lot_amount, contract_type, cpv_category, cpv_sector)
unique_cvrs <- unique(data_tender$winner_cvr_final)


## 1.3 CVR key (includes firm registration and death dates)
virk_data <- fread(file.path(key_dir, "cvr_names_virk_20260710_182823.csv"))
virk_data[, tender_firm := FALSE]
virk_data[cvr %in% unique_cvrs, tender_firm := TRUE]
```

# Introduction
The `virk.dk` API contains has employment data on a monthly, quarterly, and annual frequency. I pulled these data for every firm in the tender datasets. This note describes the quality of these data.

# Availability/coverage
```{r availability, fig.align='center'}

# How many CVRs actually appear in the employment data?

emp_cvrs <- valid_cvrs(firm_data_raw$cvr)

coverage_cvrs <- rbindlist(list(
  data.table(
    data_source = "OpenTender",
    firm_role = "Winner",
    cvr = valid_cvrs(data_ot$winner_cvr_final)
  ),
  data.table(
    data_source = "OpenTender",
    firm_role = "Buyer",
    cvr = valid_cvrs(data_ot_buyers$buyer_cvr_final)
  ),
  data.table(
    data_source = "KFST",
    firm_role = "Winner",
    cvr = valid_cvrs(data_kfst$winner_cvr_final)
  ),
  data.table(
    data_source = "KFST",
    firm_role = "Buyer",
    cvr = valid_cvrs(data_kfst_buyers$buyer_cvr_final)
  )
))

coverage_table <- coverage_cvrs[, .(
  n_cvrs = uniqueN(cvr),
  n_in_employment_data = uniqueN(cvr[cvr %in% emp_cvrs]),
  share_in_employment_data = round(uniqueN(cvr[cvr %in% emp_cvrs]) / uniqueN(cvr), 5)
), by = .(data_source, firm_role)]

kable(
  coverage_table,
  caption = "Share of valid firm CVRs in the tender data that appear in the pulled employment data"
)

# How many rows have non-missing data
missingness_table <- firm_data_raw[, .(
  # Counts
  n = .N, 
  n_nonmissing_fte = sum(!is.na(fte)),
  n_nonmissing_emp = sum(!is.na(employees)),
  n_nonmissing_emp_with_owner = sum(!is.na(employees_including_owners)),
  
  # Shares
  share_nonmissing_fte = round(sum(!is.na(fte)) / .N, 5),
  share_nonmissing_emp = round(sum(!is.na(employees)) / .N, 5),
  share_nonmissing_emp_with_owner = round(sum(!is.na(employees_including_owners)) / .N, 5)


), by = frequency]

kable(missingness_table,
      caption = "Employment data availability for firms that appear in the employment data")

```

# Balance
Below is a balance table of age for firms in our tender dataset compared to those not in the tender dataset. Firms appearing in our tender dataset tend are older than firms not in the tender dataset. This could be because firms who win tenders are usually more productive/cost competitive than firms who do not win them (especially if price is heavily weighted in deciding which firm to award a tender to).

```{r age-balance}

# Calculate firm age
anchor_date <- lubridate::floor_date(Sys.Date(), unit = "year") # Beginning of this year
virk_data[!is.na(lifecycle_end), firm_age := lifecycle_end - registration_date] # If firm ended, calculate total age
virk_data[is.na(lifecycle_end), firm_age := anchor_date - registration_date] # Otherwise, calculate from today's date
virk_data[, firm_age_yrs := as.numeric(firm_age) / 365.25]
virk_data[, firm_dissolved := fifelse(is.na(lifecycle_end), "Still registered", "Dissolved")]
age_regs <- feols(firm_age_yrs ~ i(tender_firm) - 1, fsplit = ~firm_dissolved, data = virk_data)

# Make table
age_table <- coeftable(age_regs) %>% 
  mutate(
    group = ifelse(str_detect(coefficient, "TRUE"), "Won tender", "No tender")
  ) %>% 
  select(sample, group, Estimate) %>% 
  pivot_wider(id_cols = group, names_from = sample, values_from = Estimate)

kable(
  age_table,
  caption = "Firm Age by Tender Winning Status",
  escape = FALSE,
  align = "lcc"
) %>%
  kable_styling(full_width = FALSE)
```

# Employment by firm age
```{r emp-by-firm-age, fig.align='center'}

# Regression data
reg_data <- firm_data[
  frequency == "annual" &
    exists_during_period == TRUE &
    !is.na(fte) &
    fte > 0 &
    !is.na(firm_age) &
    firm_age >= 0 &
    firm_age <= 100
]

regression_sample_table <- reg_data[, .(
  n = .N,
  n_firms = uniqueN(cvr),
  min_firm_age = min(firm_age),
  max_firm_age = max(firm_age)
)]

kable(
  regression_sample_table,
  caption = "Annual employment observations used in the firm-age regression"
)

# Regression
fte_reg <- feols(log(fte) ~ i(firm_age) - 1 | cvr, 
                 data = reg_data, 
                 cluster = ~cvr)
iplot(fte_reg)
```

# Event study around tender award

```{r es-plot-helper, include=FALSE}
# Helper: plot a pair of fixest models as one event-study figure
# (models[[1]] = FTE, models[[2]] = employees).
plot_es <- function(models, main, xlab = "Quarters relative to contract win") {
  iplot(list(models[[1]], models[[2]]),
        main   = main,
        xlab   = xlab,
        col    = c("steelblue", "darkred"),
        pt.pch = c(16, 17),
        ci.lty = c(1, 1))
  legend("bottomleft",
         legend = c("FTE", "Employees"),
         col    = c("steelblue", "darkred"),
         pch    = c(16, 17),
         lty    = c(1, 1),
         bty    = "n")
}
```

## Annual {.tabset}

Event studies around the **first** tender award (employment relative to the award year). Click through the tabs for each sample.

```{r tender-award-estudy-data, include=FALSE}

# Build universe of events
## Get unique events
setDT(data_tender)
setorder(data_tender, winner_cvr_final, data_source, award_date)
valid_winner_events <- data_tender[winner_cvr_final %in% coverage_cvrs[firm_role == "Winner"]$cvr, ]
valid_winner_events <- unique(valid_winner_events, by = c("winner_cvr_final", "award_date"))

## Create event identifier (chronological: event_id == 1 is the earliest award).
## Sort by award_date within firm *before* numbering. The earlier setorder puts
## data_source ahead of award_date, so numbering off that order would not be
## chronological for firms appearing in more than one source.
setorder(valid_winner_events, winner_cvr_final, award_date)
valid_winner_events[, event_id := seq_len(.N), by = winner_cvr_final]

## Flag "isolated" events: no other award by the same firm within 4 quarters on
## either side. Used by the all-events quarterly event study so the +/-4 quarter
## window around each event is not polluted by another award.
valid_winner_events[, award_qidx := year(award_date) * 4 + quarter(award_date)]
valid_winner_events[, gap_prev := award_qidx - shift(award_qidx), by = winner_cvr_final]
valid_winner_events[, gap_next := shift(award_qidx, type = "lead") - award_qidx, by = winner_cvr_final]
valid_winner_events[, isolated_event := (is.na(gap_prev) | gap_prev > 4) &
                                        (is.na(gap_next) | gap_next > 4)]

## Coerce firm data CVR to a zero-padded 8-digit string.
## fread reads the all-numeric cvr column as integer and drops leading zeros,
## whereas the tender CVRs are 8-digit strings. Pad here so the join matches.
firm_data[, winner_cvr_final := sprintf("%08d", as.integer(cvr))]

## Join every event to each firms employment history
firm_data_annual <- firm_data[frequency == "annual", ]
estudy_data <- firm_data_annual[valid_winner_events, on = "winner_cvr_final", allow.cartesian = TRUE]

## Create event time
estudy_data[, award_year := year(award_date)]
estudy_data[, event_year := year - award_year]
estudy_data[, event_year_binned := fcase(
  event_year <= -5, -5,
  event_year >= 5, 5,
  default = event_year  
)]

## Order more nicely
setorder(estudy_data, winner_cvr_final, event_id, year)

## Remove join failures
estudy_data <- estudy_data[!is.na(year), ]

## Balanced sample
# Get firms observed in the full -3 to 3 window around each event
# A firm-event is "balanced" if it has an observation in every year from -3 to 3
required_years <- -3:3

balanced_events <- estudy_data[
  event_year %in% required_years,
  .(n_years = uniqueN(event_year)),
  by = .(winner_cvr_final, event_id)
][n_years == length(required_years)]

# Filter estudy_data to only those firm-events
estudy_data_balanced <- estudy_data[
  balanced_events, 
  on = .(winner_cvr_final, event_id)
]
```

### All firms

Employment tends to fall after the first tender award. This is likely biased by firms dying as time passes.

```{r estudy-reg-all, fig.align='center'}

models <- feols(c(fte, employees) ~ i(event_year_binned, ref = -1) | year + winner_cvr_final, 
      cluster = ~winner_cvr_final, 
      data = estudy_data[event_id == 1 & 
                           year >= firm_by & 
                           (year <= firm_dy | is.na(lifecycle_end)), ])

# Plot
iplot(list(models[[1]], models[[2]]),
      main   = "Effect on employment",
      xlab   = "Years relative to first contract win",
      col    = c("steelblue", "darkred"),
      pt.pch = c(16, 17),
      ci.lty = c(1, 1))

legend("bottomleft",
       legend = c("FTE", "Employees"),
       col    = c("steelblue", "darkred"),
       pch    = c(16, 17),
       lty    = c(1, 1),
       bty    = "n")
```

### Current firms only

Restricting to firms currently still registered. This doesn't correct the issue.

```{r estudy-regs-alive-firms, fig.align='center'}
models <- feols(c(fte, employees) ~ i(event_year_binned, ref = -1) |
                  year + winner_cvr_final,
                cluster = ~winner_cvr_final,
                data = estudy_data[event_id == 1 &
                                     year >= firm_by &
                                     is.na(lifecycle_end), ])

plot_es(models, "Effect on employment; only current firms",
        xlab = "Years relative to first contract win")
```

```{r estudy-regs-1-tender-models, include=FALSE}
# Number of tenders won per firm, then split the first-award event study by it.
estudy_data[, total_tenders_won   := max(event_id, na.rm = TRUE), by = winner_cvr_final]
estudy_data[, total_tenders_group := fifelse(total_tenders_won > 1, "more than 1", "only 1")]

models_by_tenders <- feols(c(fte, employees) ~ i(event_year_binned, ref = -1) |
                             year + winner_cvr_final,
                           cluster = ~winner_cvr_final,
                           split  = ~total_tenders_group,
                           data   = estudy_data[event_id == 1 &
                                                  year >= firm_by &
                                                  (year <= firm_dy | is.na(lifecycle_end))])
```

### More than 1 tender

Firms that go on to win more than one tender.

```{r estudy-regs-multi-tender, fig.align='center'}
plot_es(models_by_tenders[sample = "more than 1"],
        "Effect on employment; more than 1 tender won",
        xlab = "Years relative to first contract win")
```

### Only 1 tender

Firms that win exactly one tender.

```{r estudy-regs-single-tender, fig.align='center'}
plot_es(models_by_tenders[sample = "only 1"],
        "Effect on employment; only 1 tender won",
        xlab = "Years relative to first contract win")
```

## Quarterly {.tabset}

Quarterly event studies. The **First award** tab uses the first award per firm; the remaining tabs use *all isolated events* (firms with no other award within four quarters on either side), with a balanced ±4-quarter window and firm + calendar-year + season fixed effects, shown in three functional forms.

```{r qtr-estudy_data, include=FALSE}

## Join every event to each firms employment history
firm_data_qtr <- firm_data[frequency == "quarterly", ]
estudy_data <- firm_data_qtr[valid_winner_events,
                                on = "winner_cvr_final",
                                allow.cartesian = TRUE]

# Extract award year and quarter
estudy_data[, award_year    := year(award_date)]
estudy_data[, award_quarter := quarter(award_date)]

# Define event_quarter as number of quarters after event quarter
# First create a unique quarter index for both the observation and award date
estudy_data[, obs_quarter_index   := year * 4 + quarter]
estudy_data[, award_quarter_index := award_year * 4 + award_quarter]
estudy_data[, event_quarter       := obs_quarter_index - award_quarter_index]

# Bin
estudy_data[, event_quarter_binned := fcase(
  event_quarter >= 8, 8,
  event_quarter <= -8, -8,
  default = event_quarter
)]

```

```{r estudy-reg-all-events-models, include=FALSE}
# All isolated events, in the clean +/-4 quarter window, within the firm's life.
window_quarters <- -4:4
estudy_all_events <- estudy_data[
  isolated_event == TRUE &
    event_quarter %in% window_quarters &
    year >= firm_by &
    (year <= firm_dy | is.na(lifecycle_end))
]

# Unique identifier for each stacked event (firm x event)
estudy_all_events[, event_uid := paste(winner_cvr_final, event_id, sep = "_")]

# Balanced window: keep only events observed in every event-quarter from -4 to +4,
# so each coefficient is estimated off the same composition of events.
balanced_q_events <- estudy_all_events[
  , .(n_q = uniqueN(event_quarter)), by = event_uid
][n_q == length(window_quarters)]
estudy_all_events <- estudy_all_events[balanced_q_events, on = "event_uid"]

# Employment outcomes in three functional forms. log() is NA for non-positive
# values; asinh() (inverse hyperbolic sine) keeps zeros while giving ~% effects.
estudy_all_events[, `:=`(
  log_fte   = fifelse(fte > 0, log(fte), NA_real_),
  log_emp   = fifelse(employees > 0, log(employees), NA_real_),
  asinh_fte = asinh(fte),
  asinh_emp = asinh(employees)
)]

# firm + year + quarter FE: firm and calendar-year as before, plus quarter-of-year
# to absorb employment seasonality. (event_quarter dummies stay identified because
# year/quarter enter additively, not as the full calendar-quarter interaction.)
models_levels <- feols(c(fte, employees) ~ i(event_quarter, ref = -1) |
                         winner_cvr_final + year + quarter,
                       cluster = ~winner_cvr_final, data = estudy_all_events)
models_log    <- feols(c(log_fte, log_emp) ~ i(event_quarter, ref = -1) |
                         winner_cvr_final + year + quarter,
                       cluster = ~winner_cvr_final, data = estudy_all_events)
models_asinh  <- feols(c(asinh_fte, asinh_emp) ~ i(event_quarter, ref = -1) |
                         winner_cvr_final + year + quarter,
                       cluster = ~winner_cvr_final, data = estudy_all_events)
```

### First award

Employment tends to fall after the first tender award. This is likely biased by firms dying as time passes.

```{r estudy-reg-all-qtr, fig.align='center'}
models <- feols(c(fte, employees) ~ i(event_quarter_binned, ref = -1) |
                  year + winner_cvr_final,
                cluster = ~winner_cvr_final,
                data = estudy_data[event_id == 1 &
                                     year >= firm_by &
                                     (year <= firm_dy | is.na(lifecycle_end)), ])

plot_es(models, "Effect on employment",
        xlab = "Quarters relative to first contract win")
```

### All isolated events — levels

```{r qtr-es-levels, fig.align='center'}
plot_es(models_levels, "Effect on employment (levels); all isolated events")
```

### All isolated events — log

```{r qtr-es-log, fig.align='center'}
plot_es(models_log, "Effect on log employment; all isolated events")
```

### All isolated events — asinh

```{r qtr-es-asinh, fig.align='center'}
plot_es(models_asinh, "Effect on asinh(employment); all isolated events")
```
