---
title: "Employment Data Quality"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(file.path(dirname(inputFile), ".."), mustWork = TRUE)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

# Clean up environment
rm(list = ls())

# Packages
library(here)
library(data.table)
library(tidyverse)
library(knitr)
library(fixest)
library(lubridate)
library(kableExtra)

# Paths
report_project_dir <- if (file.exists("config.R")) {
  getwd()
} else {
  normalizePath("..", mustWork = TRUE)
}
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)

source(file.path(report_project_dir, "config.R"))
clean_data_dir <- dirs$clean_data
key_dir <- dirs$cvr_key

valid_cvrs <- function(x) {
  x <- trimws(as.character(x))
  x <- gsub("[^0-9]", "", x)
  x <- x[grepl("^[0-9]{1,8}$", x)]
  unique(sprintf("%08d", as.integer(x)))
}

# 1 Load data
## 1.1 Firm data
firm_data_raw <- fread(file.path(clean_data_dir, "cvr_employment_history_virk.csv"))
setDT(firm_data_raw)

firm_data <- copy(firm_data_raw)
setDT(firm_data)
firm_data[, firm_by := year(lifecycle_start)]
firm_data[, firm_dy := year(lifecycle_end)]
firm_data[, firm_age := as.integer(floor(as.numeric(period_end - lifecycle_start) / 365.25))]
firm_data_ls <- firm_data %>% 
  split(.$frequency)

## 1.2 Tender data
data_ot <- readRDS(file.path(clean_data_dir, "clean_winner_data_ot_name_matched.rds")) %>% 
  mutate(data_source = "OpenTender")
data_kfst <- readRDS(file.path(clean_data_dir, "clean_winner_data_kfst_name_matched.rds")) %>% 
  mutate(data_source = "KFST")
data_ot_buyers <- readRDS(file.path(clean_data_dir, "clean_buyer_data_ot_name_matched.rds")) %>% 
  mutate(data_source = "OpenTender")
data_kfst_buyers <- readRDS(file.path(clean_data_dir, "clean_buyer_data_kfst_name_matched.rds")) %>% 
  mutate(data_source = "KFST")
data_tender <- rbindlist(list(data_ot, data_kfst), fill = TRUE, ignore.attr = TRUE) %>% 
  select(data_source, tender_id, lot_id, award_date, winner_cvr_final, tender_amount, lot_amount)
unique_cvrs <- unique(data_tender$winner_cvr_final)


## 1.3 CVR key (includes firm registration and death dates)
virk_data <- fread(file.path(key_dir, "cvr_names_virk_20260710_182823.csv"))
virk_data[, tender_firm := FALSE]
virk_data[cvr %in% unique_cvrs, tender_firm := TRUE]
```

# Introduction
The `virk.dk` API contains has employment data on a monthly, quarterly, and annual frequency. I pulled these data for every firm in the tender datasets. This note describes the quality of these data.

# Availability/coverage
```{r availability, fig.align='center'}

# How many CVRs actually appear in the employment data?

emp_cvrs <- valid_cvrs(firm_data_raw$cvr)

coverage_cvrs <- rbindlist(list(
  data.table(
    data_source = "OpenTender",
    firm_role = "Winner",
    cvr = valid_cvrs(data_ot$winner_cvr_final)
  ),
  data.table(
    data_source = "OpenTender",
    firm_role = "Buyer",
    cvr = valid_cvrs(data_ot_buyers$buyer_cvr_final)
  ),
  data.table(
    data_source = "KFST",
    firm_role = "Winner",
    cvr = valid_cvrs(data_kfst$winner_cvr_final)
  ),
  data.table(
    data_source = "KFST",
    firm_role = "Buyer",
    cvr = valid_cvrs(data_kfst_buyers$buyer_cvr_final)
  )
))

coverage_table <- coverage_cvrs[, .(
  n_cvrs = uniqueN(cvr),
  n_in_employment_data = uniqueN(cvr[cvr %in% emp_cvrs]),
  share_in_employment_data = round(uniqueN(cvr[cvr %in% emp_cvrs]) / uniqueN(cvr), 5)
), by = .(data_source, firm_role)]

kable(
  coverage_table,
  caption = "Share of valid firm CVRs in the tender data that appear in the pulled employment data"
)

# How many rows have non-missing data
missingness_table <- firm_data_raw[, .(
  # Counts
  n = .N, 
  n_nonmissing_fte = sum(!is.na(fte)),
  n_nonmissing_emp = sum(!is.na(employees)),
  n_nonmissing_emp_with_owner = sum(!is.na(employees_including_owners)),
  
  # Shares
  share_nonmissing_fte = round(sum(!is.na(fte)) / .N, 5),
  share_nonmissing_emp = round(sum(!is.na(employees)) / .N, 5),
  share_nonmissing_emp_with_owner = round(sum(!is.na(employees_including_owners)) / .N, 5)


), by = frequency]

kable(missingness_table,
      caption = "Employment data availability for firms that appear in the employment data")

```

# Balance
We should construct a balance table of the following partition of firms: firms that have employment history AND are in the tender datasets, firms that do not have employment history AND are in the tender data, and firms that are not in the tender dataset. The only thing we can compare at the moment is firm age.

```{r age-balance}

# Calculate firm age
anchor_date <- lubridate::floor_date(Sys.Date(), unit = "year") # Beginning of this year
virk_data[!is.na(lifecycle_end), firm_age := lifecycle_end - registration_date] # If firm ended, calculate total age
virk_data[is.na(lifecycle_end), firm_age := anchor_date - registration_date] # Otherwise, calculate from today's date
virk_data[, firm_age_yrs := as.numeric(firm_age) / 365.25]
virk_data[, firm_dissolved := fifelse(is.na(lifecycle_end), "Still registered", "Dissolved")]
age_regs <- feols(firm_age_yrs ~ i(tender_firm) - 1, fsplit = ~firm_dissolved, data = virk_data)

# Make table
age_table <- coeftable(age_regs) %>% 
  mutate(
    group = ifelse(str_detect(coefficient, "TRUE"), "Won tender", "No tender")
  ) %>% 
  select(sample, group, Estimate) %>% 
  pivot_wider(id_cols = group, names_from = sample, values_from = Estimate)

kable(
  age_table,
  caption = "Firm Age by Tender Winning Status",
  escape = FALSE,
  align = "lcc"
) %>%
  kable_styling(full_width = FALSE)
```

# Employment by firm age
```{r emp-by-firm-age, fig.align='center'}

# Regression data
reg_data <- firm_data[
  frequency == "annual" &
    exists_during_period == TRUE &
    !is.na(fte) &
    fte > 0 &
    !is.na(firm_age) &
    firm_age >= 0 &
    firm_age <= 100
]

regression_sample_table <- reg_data[, .(
  n = .N,
  n_firms = uniqueN(cvr),
  min_firm_age = min(firm_age),
  max_firm_age = max(firm_age)
)]

kable(
  regression_sample_table,
  caption = "Annual employment observations used in the firm-age regression"
)

# Regression
fte_reg <- feols(log(fte) ~ i(firm_age) - 1 | cvr, 
                 data = reg_data, 
                 cluster = ~cvr)
iplot(fte_reg)
```
