---
title: "Does the CVR-resolution method matter? TWFE event studies of KFST award wins on firm employment"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
suppressPackageStartupMessages({
  library(data.table)
  library(fixest)
  library(ggplot2)
  library(knitr)
})
source("config.R")
clean_data_dir <- dirs$clean_data
```

# Purpose

A **first, quick** test of whether the way we resolve a KFST award to a *firm CVR* actually changes the
estimated employment response to winning. We run the **same** two-way fixed-effects (TWFE) event study
of log FTE around a firm's first KFST award, on three different definitions of "which CVR won":

| Series | Winner CVR definition |
|---|---|
| **matched** | New consortium-aware production `winner_cvr_final` (field CVR + name matching + field-pairing). |
| **extraction** | Raw 8-digit CVRs extracted from the winner field, **no matching** (the naive floor). |
| **old matched** | Pre-consortium production `winner_cvr_final` (the previous method). |

If the three event-study paths coincide, the resolution method does not matter for this outcome. If they
diverge, it does — and by how much.

> **This is a scoping tool, not the final estimator.** Plain TWFE with staggered timing and heterogeneous
> effects is biased (Goodman-Bacon / de Chaisemartin–D'Haultfœuille). The rigorous design is the
> control-matched study in `6a_estudy_control.Rmd`; this note is only to get a fast sense of magnitude.

```{r config}
# ---- Design choices (edit here) ---------------------------------------------------------------------
ES_WINDOW      <- c(-8L, 8L)   # event-time window, in quarters, around the first award
REF_EVENT_TIME <- -1L          # omitted (reference) event time
MIN_FTE        <- 0            # keep firm-quarters with fte > MIN_FTE (log requires > 0)
EMP_FREQUENCY  <- "quarterly_spliced"  # continuous quarterly FTE series (matches 6_firm_employment_quality)
```

# Data

```{r load-employment}
# Winner/buyer employment panel pulled from virk.dk (one continuous quarterly FTE series per firm).
emp <- fread(
  file.path(clean_data_dir, "cvr_employment_history_virk.csv"),
  select = c("cvr", "frequency", "year", "quarter", "fte"),
  colClasses = list(character = "cvr")
)
emp <- emp[frequency == EMP_FREQUENCY & !is.na(year) & !is.na(quarter)]
emp[, cvr := as.character(cvr)]
# One quarterly index (…, 2015Q1 = 8060, …) so event time = qidx - event_qidx.
emp[, qidx := year * 4L + (quarter - 1L)]
# Collapse to one FTE per firm-quarter (should already be unique for a single frequency).
panel <- emp[!is.na(fte), .(fte = mean(fte, na.rm = TRUE)), by = .(cvr, qidx)]
panel <- panel[fte > MIN_FTE]
panel[, log_fte := log(fte)]
emp_cvrs <- unique(panel$cvr)
```

```{r load-winner-sets}
is8 <- function(x) !is.na(x) & grepl("^[0-9]{8}$", as.character(x))
to_qidx <- function(d) data.table::year(d) * 4L + (data.table::quarter(d) - 1L)

stack <- as.data.table(readRDS(file.path(clean_data_dir, "kfst_winner_datasets_stacked.rds")))

# Each winner set -> one treatment event per firm: the quarter of its FIRST KFST award.
first_award <- function(dt) {
  dt <- dt[is8(winner_cvr_final) & !is.na(award_date)]
  dt[, .(event_qidx = min(to_qidx(award_date))), by = .(cvr = as.character(winner_cvr_final))]
}

winner_sets <- list(
  matched    = first_award(stack[dataset == "base"]),
  extraction = first_award(stack[dataset == "extraction"])
)
# "old matched" (pre-consortium production) is a point-in-time comparison artifact, not regenerated by the
# pipeline -- include it only when present so this notebook still knits on a fresh checkout.
oldp_path <- file.path(clean_data_dir, "clean_winner_data_kfst_name_matched_OLDPROD.rds")
if (file.exists(oldp_path)) {
  winner_sets[["old matched"]] <- first_award(as.data.table(readRDS(oldp_path)))
}
```

## Employment-data coverage

The Virk pull now covers **every** winner CVR across all three methods (`Pulled` = 100%). But a firm is
only *usable* if Virk actually returns employment rows for it — `Has data` below. The ~6–9% with no data
are dissolved / foreign / non-employer / invalid CVRs. Note the ordering: **extraction has the lowest data
rate** — the extra CVRs it carries (that matching would fix or drop) disproportionately have no real
employer behind them, so they self-exclude from the study. That is largely *why* the three methods give
the same event study.

```{r coverage}
# Attempted = CVR queried in the pull (status file); has-data = returned employment rows (in the csv).
status_path <- file.path(clean_data_dir, "cvr_employment_history_virk_status.csv")
status_cvrs <- if (file.exists(status_path))
  unique(as.character(fread(status_path, colClasses = list(character = "cvr"))$cvr)) else character()
coverage <- rbindlist(lapply(names(winner_sets), function(nm) {
  ev <- winner_sets[[nm]]
  data.table(
    Series = nm,
    `Firm CVRs` = nrow(ev),
    `Pulled` = sprintf("%.1f%%", 100 * mean(ev$cvr %in% status_cvrs)),
    `Has data` = sum(ev$cvr %in% emp_cvrs),
    `Data coverage` = sprintf("%.1f%%", 100 * mean(ev$cvr %in% emp_cvrs))
  )
}))
kable(coverage, caption = "Coverage of each winner-CVR set: queried vs. has usable employment data")
```

# Event study

```{r estimate}
# Build the ±window event panel for one winner set and fit the TWFE event study:
#   log(fte) ~ Σ 1[event_time = e]  |  firm FE + calendar-quarter FE ,  clustered by firm.
run_es <- function(events, label) {
  d <- panel[events, on = "cvr", nomatch = 0L]           # all firm-quarters for these firms
  d[, event_time := qidx - event_qidx]
  d <- d[event_time >= ES_WINDOW[1] & event_time <= ES_WINDOW[2]]
  # keep firms observed at the reference quarter so every path shares a common base
  ok <- d[event_time == REF_EVENT_TIME, unique(cvr)]
  d  <- d[cvr %in% ok]
  m <- feols(log_fte ~ i(event_time, ref = REF_EVENT_TIME) | cvr + qidx,
             data = d, cluster = ~cvr)
  ct <- as.data.table(coeftable(m), keep.rownames = "term")
  setnames(ct, 1:3, c("term", "est", "se"))
  ct <- ct[grepl("event_time::", term)]
  ct[, event_time := as.integer(sub(".*event_time::", "", term))]
  ct <- rbind(ct[, .(event_time, est, se)],
              data.table(event_time = REF_EVENT_TIME, est = 0, se = 0))
  ct[, `:=`(lo = est - 1.96 * se, hi = est + 1.96 * se,
            Series = label, n_firms = uniqueN(d$cvr), n_obs = nrow(d))]
  ct[order(event_time)]
}

es <- rbindlist(lapply(names(winner_sets), function(nm) run_es(winner_sets[[nm]], nm)))
```

```{r sample-sizes}
kable(unique(es[, .(Series, `Firms in study` = n_firms, `Firm-quarters` = n_obs)]),
      caption = "Estimation samples (firms observed at the reference quarter, within the window)")
```

## The comparison

Coefficients are the log-FTE change relative to the quarter before the first award (event time −1). If the
CVR-resolution method did not matter, the three paths would lie on top of one another.

```{r plot-es, fig.width=9, fig.height=5.5}
fig_dir <- file.path("output", "figures")
dir.create(fig_dir, showWarnings = FALSE, recursive = TRUE)

p_overlay <- ggplot(es, aes(event_time, est, colour = Series, fill = Series)) +
  geom_hline(yintercept = 0, linetype = 2, colour = "grey40") +
  geom_vline(xintercept = REF_EVENT_TIME + 0.5, linetype = 3, colour = "grey40") +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.12, colour = NA) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.8) +
  scale_x_continuous(breaks = seq(ES_WINDOW[1], ES_WINDOW[2], 2)) +
  labs(x = "Quarters relative to first KFST award", y = "Δ log FTE (vs. quarter −1)",
       title = "Employment response to a KFST award win, by CVR-resolution method",
       subtitle = "TWFE: firm + calendar-quarter fixed effects; 95% CIs clustered by firm") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top")
p_overlay

# Persist the figure straight from this chunk (regenerated on every knit).
ggsave(file.path(fig_dir, "twfe_estudy_cvr_method_overlay.png"), p_overlay,
       width = 9, height = 5.5, dpi = 150)
ggsave(file.path(fig_dir, "twfe_estudy_cvr_method_overlay.pdf"), p_overlay,
       width = 9, height = 5.5)
```

## Each spec on its own panel

```{r plot-es-facets, fig.width=12, fig.height=4.5}
p_facets <- ggplot(es, aes(event_time, est)) +
  geom_hline(yintercept = 0, linetype = 2, colour = "grey40") +
  geom_vline(xintercept = REF_EVENT_TIME + 0.5, linetype = 3, colour = "grey40") +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.15, fill = "#2c7fb8") +
  geom_line(colour = "#2c7fb8", linewidth = 0.8) +
  geom_point(colour = "#2c7fb8", size = 1.6) +
  facet_wrap(~ Series, nrow = 1) +
  scale_x_continuous(breaks = seq(ES_WINDOW[1], ES_WINDOW[2], 4)) +
  labs(x = "Quarters relative to first KFST award", y = "Δ log FTE (vs. quarter −1)",
       title = "TWFE event study by CVR-resolution method (each spec on its own panel)") +
  theme_minimal(base_size = 12)
p_facets

ggsave(file.path(fig_dir, "twfe_estudy_cvr_method_facets.png"), p_facets,
       width = 12, height = 4.5, dpi = 150)
ggsave(file.path(fig_dir, "twfe_estudy_cvr_method_facets.pdf"), p_facets,
       width = 12, height = 4.5)
```

```{r coef-table}
wide <- dcast(es, event_time ~ Series, value.var = "est")
kable(wide, digits = 3,
      caption = "Point estimates (Δ log FTE vs. −1) by event time and CVR-resolution method")
```

# Reading this

- **Paths coincide** → the resolution method is second-order for the employment event study; the naive
  extraction floor would give you the same answer.
- **Extraction is attenuated / noisier** → wrong or missing field CVRs pull the wrong firm's employment,
  biasing the estimate toward zero; the matching work is buying real accuracy.
- **matched vs old matched** → what the consortium rework specifically changed for this outcome.

# Caveats and next steps

- **Estimator.** Plain TWFE event study with staggered timing — indicative only. For inference use the
  control-matched design (`6a_estudy_control.Rmd`) or a heterogeneity-robust estimator (Callaway–
  Sant'Anna, `did`; Sun–Abraham, `sunab()`).
- **Treatment.** First award only; repeat wins are ignored. Firms must be observed at event time −1.
- **Coverage.** All winner CVRs across the three methods have now been pulled (100% queried). The ~6–9%
  without employment rows have no data in Virk (dissolved / foreign / non-employer / invalid) and cannot be
  recovered by re-pulling. Extraction's lower data rate is itself informative (see the coverage section):
  the CVRs it carries that matching would fix or drop are disproportionately non-employers.
```
