---
title: "Winner CVR Provenance & Quality Counts"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
    code_folding: hide
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)

report_project_dir <- local({
  d <- normalizePath(getwd(), mustWork = TRUE)
  while (!file.exists(file.path(d, "cvr-cleaning.Rproj")) && dirname(d) != d) d <- dirname(d)
  d
})
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)
source(file.path(report_project_dir, "config.R"))
source(file.path(report_project_dir, "code", "functions.R"))
```

```{r load}
clean_dir <- dirs$clean_data
ted_dir   <- file.path(dirs$intermediates, "ted")

# "Full version" = the concatenated winner dataset from code/processing/5_combine_datasets.R.
# Fall back to stacking the per-source matched files if the combined file is not present.
combined_winner_path <- file.path(clean_dir, "clean_winner_data_all_name_matched.rds")
if (file.exists(combined_winner_path)) {
  all_winners <- as_tibble(readRDS(combined_winner_path))
} else {
  ted_path <- file.path(clean_dir, "clean_winner_data_ted_name_matched.rds")            # new location
  if (!file.exists(ted_path)) ted_path <- file.path(ted_dir, "ted_winner_data_name_matched.rds")  # pre-move
  all_winners <- bind_rows(
    readRDS(file.path(clean_dir, "clean_winner_data_kfst_name_matched.rds")) %>% mutate(dataset = "KFST"),
    readRDS(file.path(clean_dir, "clean_winner_data_ot_name_matched.rds"))   %>% mutate(dataset = "OpenTender"),
    readRDS(ted_path)                                                        %>% mutate(dataset = "TED")
  ) %>% as_tibble()
}

# Canonical 8-digit CVR; "valid" = well-formed 8 digits (format only). Whether the CVR is a *real
# registered firm* is the separate, airtight check `flag_cvr_final_in_registry` (shown as
# `in_cvr_registry` below).
norm_cvr <- function(x) {
  x <- gsub("[^0-9]", "", as.character(x))
  ifelse(x == "" | nchar(x) > 8, NA_character_, sprintf("%08d", suppressWarnings(as.integer(x))))
}
is_valid_cvr <- function(x) !is.na(norm_cvr(x))
```

```{r stack}
# Columns shared by all three winner datasets (TED also carries non-winning bidders -> is_winner).
shared <- c("tender_id", "lot_id", "ted_notice_id", "lot_number", "flag_awarded",
            "winner_cvr_clean", "winner_cvr_name_match", "winner_cvr_final", "winner_name", "winner_country",
            "cvr_number_source", "matching_candidate_type", "name_match_status", "name_match_method", "name_match_source",
            "cvr_name_match_quality", "cvr_name_match_quality_basic",
            "cvr_name_match_quality_nospaces", "cvr_name_match_quality_broad", "cvr_name_is_substring",
            "flag_name_match_found", "flag_name_match_ambiguous", "flag_review_name_match",
            "flag_manual_name_review", "flag_cvr_recovered_from_invalid", "flag_cvr_final_in_registry",
            "flag_missing_winner_cvr", "flag_missing_winner_cvr_final")

# KFST/OpenTender are winners-only and carry no is_winner column, so in the combined file their
# is_winner is NA -> treat as TRUE; TED keeps its TRUE/FALSE non-winning-bidder flag.
winners <- all_winners %>%
  mutate(is_winner = if ("is_winner" %in% names(.)) coalesce(is_winner, TRUE) else TRUE) %>%
  select(dataset, is_winner, any_of(shared)) %>%
  filter(is_winner %in% TRUE) %>%
  mutate(
    valid_clean    = is_valid_cvr(winner_cvr_clean),      # CVR from source extraction
    valid_namematch = is_valid_cvr(winner_cvr_name_match), # CVR from name matching only
    valid_final    = is_valid_cvr(winner_cvr_final),      # final combined CVR
    cvr_final_norm = norm_cvr(winner_cvr_final)
  )
```

# Headline counts

```{r headline}
winners %>%
  group_by(dataset) %>%
  summarise(
    rows                = n(),
    tenders             = n_distinct(tender_id),
    awarded_lots        = n_distinct(paste(tender_id, lot_id)[flag_awarded %in% TRUE]),
    valid_cvr_extracted = sum(valid_clean),
    valid_cvr_namematch = sum(valid_namematch),
    valid_cvr_final     = sum(valid_final),
    in_cvr_registry     = sum(flag_cvr_final_in_registry %in% TRUE),
    unique_final_cvrs   = n_distinct(cvr_final_norm[valid_final]),
    pct_final_valid     = round(100 * mean(valid_final), 1),
    .groups = "drop"
  ) %>%
  kable(caption = "Valid winner CVRs by dataset and provenance stage")
```

# Provenance columns

## `cvr_number_source` — how each final CVR was obtained

```{r cvr-number-source}
winners %>%
  count(dataset, cvr_number_source) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  arrange(desc(TED)) %>%
  kable(caption = "cvr_number_source (row counts)")
```

## `matching_candidate_type` and `name_match_status`

```{r cand-type}
winners %>%
  count(dataset, matching_candidate_type) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  kable(caption = "matching_candidate_type (row counts)")

winners %>%
  count(dataset, name_match_status) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  kable(caption = "name_match_status (row counts)")
```

## Provenance flags (count of TRUE)

```{r flags}
prov_flags <- c("flag_name_match_found", "flag_name_match_ambiguous", "flag_review_name_match",
                "flag_manual_name_review", "flag_cvr_recovered_from_invalid",
                "flag_cvr_final_in_registry", "flag_missing_winner_cvr", "flag_missing_winner_cvr_final")

winners %>%
  group_by(dataset) %>%
  summarise(across(all_of(prov_flags), ~ sum(.x %in% TRUE)), .groups = "drop") %>%
  pivot_longer(-dataset, names_to = "flag", values_to = "n_true") %>%
  pivot_wider(names_from = dataset, values_from = n_true) %>%
  kable(caption = "Provenance flags (rows flagged TRUE)")
```

## Multiple-CVR vs single-CVR records

```{r multiple-cvr}
# How many valid final CVRs came from a raw record whose winner-CVR field listed MULTIPLE CVRs (so the
# record was expanded into several winner rows) vs a single-CVR record vs no field CVR at all (the final
# CVR came from name matching). Per-source signal for "how many CVRs the raw field listed": OpenTender
# uses its own validated count `n_valid_cvr_raw`; KFST/TED parse distinct 8-digit tokens from
# `winner_cvr_original` (TED has one organisation per row, so it is effectively never a multi-CVR record).
tok_count <- function(x) { x <- as.character(x); x[is.na(x)] <- ""
  vapply(strsplit(x, "[^0-9]+"), function(t) { t <- unique(t[t != ""]); sum(nchar(t) == 8L) }, integer(1)) }

all_winners %>%
  mutate(is_winner = if ("is_winner" %in% names(.)) coalesce(is_winner, TRUE) else TRUE) %>%
  filter(is_winner %in% TRUE, is_valid_cvr(winner_cvr_final)) %>%
  mutate(
    n_field_cvr = if_else(dataset == "OpenTender",
                          suppressWarnings(as.integer(n_valid_cvr_raw)),
                          tok_count(winner_cvr_original)),
    cvr_record  = case_when(n_field_cvr >= 2 ~ "multiple-CVR record (expanded)",
                            n_field_cvr == 1 ~ "single-CVR record",
                            TRUE             ~ "no field CVR (name-matched)")
  ) %>%
  count(dataset, cvr_record) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  kable(caption = "Valid winner CVRs by raw-record CVR structure (multiple = field listed >=2 CVRs, expanded into several winner rows)")
```

## Name-match source and method

```{r match-source}
# Among rows whose CVR came from name matching: which registry key matched (official `name` vs `biname`
# alternative name) and by what method (`exact` vs `fuzzy`), per dataset.
winners %>%
  filter(!is.na(name_match_source)) %>%
  count(dataset, name_match_source) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  kable(caption = "Name-match source: registry key that matched (official name vs biname), by dataset")

winners %>%
  filter(!is.na(name_match_method)) %>%
  count(dataset, name_match_method) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  kable(caption = "Name-match method: exact vs fuzzy, by dataset")
```

# Name-match quality

```{r quality-summary}
winners %>%
  filter(!is.na(cvr_name_match_quality)) %>%
  group_by(dataset) %>%
  summarise(
    n_scored        = n(),
    mean_quality    = round(mean(cvr_name_match_quality), 1),
    median_quality  = round(median(cvr_name_match_quality), 1),
    pct_perfect_100 = round(100 * mean(cvr_name_match_quality == 100), 1),
    pct_substring   = round(100 * mean(cvr_name_is_substring %in% TRUE), 1),
    .groups = "drop"
  ) %>%
  kable(caption = "Name-match quality summary (scored rows only)")
```

```{r quality-buckets}
winners %>%
  filter(!is.na(cvr_name_match_quality)) %>%
  mutate(bucket = cut(cvr_name_match_quality, c(-Inf, 50, 80, 99.999, Inf),
                      labels = c("<50", "50–80", "80–<100", "100"))) %>%
  count(dataset, bucket) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  kable(caption = "cvr_name_match_quality distribution (scored rows)")
```

```{r quality-variants}
winners %>%
  filter(!is.na(cvr_name_match_quality)) %>%
  group_by(dataset) %>%
  summarise(across(starts_with("cvr_name_match_quality") & where(is.numeric),
                   ~ round(mean(.x, na.rm = TRUE), 1)), .groups = "drop") %>%
  kable(caption = "Mean of each name-match quality variant (scored rows)")
```

# Cross-source winner agreement

```{r agreement}
awarded_winners <- function(df) {
  if (!"is_winner" %in% names(df)) df$is_winner <- TRUE
  df %>% mutate(is_winner = coalesce(is_winner, TRUE)) %>%   # KFST/OT NA -> TRUE (winners-only)
    filter(is_winner %in% TRUE, flag_awarded %in% TRUE)
}

# Winner-CVR set per key, dropping rows with an invalid CVR or a blank key component.
winner_sets <- function(df, keys) {
  df %>%
    mutate(cvr = norm_cvr(winner_cvr_final), lot_number = trimws(as.character(lot_number))) %>%
    filter(!is.na(cvr), if_all(all_of(keys), ~ !is.na(.x) & .x != "")) %>%
    group_by(across(all_of(keys))) %>%
    summarise(cvrs = list(sort(unique(cvr))), .groups = "drop")
}

agree <- function(a_df, b_df, keys, label) {
  j <- inner_join(winner_sets(a_df, keys), winner_sets(b_df, keys), by = keys, suffix = c("_a", "_b"))
  tibble(
    comparison     = label,
    level          = if (length(keys) > 1) "lot" else "notice",
    comparable     = nrow(j),
    exact_pct      = round(100 * mean(map2_lgl(j$cvrs_a, j$cvrs_b, setequal)), 1),
    any_common_pct = round(100 * mean(map2_lgl(j$cvrs_a, j$cvrs_b, ~ length(intersect(.x, .y)) > 0)), 1)
  )
}

ted_w  <- awarded_winners(filter(all_winners, dataset == "TED"))
kfst_w <- awarded_winners(filter(all_winners, dataset == "KFST"))
ot_w   <- awarded_winners(filter(all_winners, dataset == "OpenTender"))

bind_rows(
  agree(ted_w,  kfst_w, "ted_notice_id", "TED vs KFST"),
  agree(ted_w,  ot_w,   "ted_notice_id", "TED vs OpenTender"),
  agree(kfst_w, ot_w,   "ted_notice_id", "KFST vs OpenTender"),
  agree(ted_w,  kfst_w, c("ted_notice_id", "lot_number"), "TED vs KFST"),
  agree(ted_w,  ot_w,   c("ted_notice_id", "lot_number"), "TED vs OpenTender")
) %>%
  arrange(level, comparison) %>%
  kable(caption = "Winner-CVR agreement (exact_pct = identical winner set; any_common_pct = >=1 shared winner)")
```

# Buyer datasets

```{r buyer-load}
combined_buyer_path <- file.path(clean_dir, "clean_buyer_data_all_name_matched.rds")
if (file.exists(combined_buyer_path)) {
  buyers_all <- as_tibble(readRDS(combined_buyer_path))
} else {
  tedb_path <- file.path(clean_dir, "clean_buyer_data_ted_name_matched.rds")            # new location
  if (!file.exists(tedb_path)) tedb_path <- file.path(ted_dir, "ted_buyer_data_name_matched.rds")  # pre-move
  buyers_all <- bind_rows(
    readRDS(file.path(clean_dir, "clean_buyer_data_kfst_name_matched.rds")) %>% mutate(dataset = "KFST"),
    readRDS(file.path(clean_dir, "clean_buyer_data_ot_name_matched.rds"))   %>% mutate(dataset = "OpenTender"),
    readRDS(tedb_path)                                                      %>% mutate(dataset = "TED")
  ) %>% as_tibble()
}

buyer_shared <- c("tender_id", "ted_notice_id",
                  "buyer_cvr_clean", "buyer_cvr_name_match", "buyer_cvr_final", "buyer_name", "buyer_country",
                  "cvr_number_source", "matching_candidate_type", "name_match_status",
                  "cvr_name_match_quality", "cvr_name_is_substring",
                  "flag_name_match_found", "flag_review_name_match", "flag_manual_name_review",
                  "flag_cvr_recovered_from_invalid", "flag_cvr_final_in_registry",
                  "flag_missing_buyer_cvr", "flag_missing_buyer_cvr_final")

buyers <- buyers_all %>%
  select(dataset, any_of(buyer_shared)) %>%
  mutate(
    valid_clean     = is_valid_cvr(buyer_cvr_clean),        # NA/0 for KFST (no extracted-CVR column)
    valid_namematch = is_valid_cvr(buyer_cvr_name_match),
    valid_final     = is_valid_cvr(buyer_cvr_final),
    cvr_final_norm  = norm_cvr(buyer_cvr_final)
  )
```

```{r buyer-headline}
buyers %>%
  group_by(dataset) %>%
  summarise(
    rows                = n(),
    valid_cvr_extracted = sum(valid_clean),
    valid_cvr_namematch = sum(valid_namematch),
    valid_cvr_final     = sum(valid_final),
    in_cvr_registry     = sum(flag_cvr_final_in_registry %in% TRUE),
    unique_final_cvrs   = n_distinct(cvr_final_norm[valid_final]),
    pct_final_valid     = round(100 * mean(valid_final), 1),
    .groups = "drop"
  ) %>%
  kable(caption = "Valid buyer CVRs by dataset and provenance stage")
```

```{r buyer-provenance}
buyers %>%
  count(dataset, cvr_number_source) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  arrange(desc(TED)) %>%
  kable(caption = "buyer cvr_number_source (row counts)")

buyers %>%
  count(dataset, name_match_status) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  kable(caption = "buyer name_match_status (row counts)")

buyers %>%
  filter(!is.na(cvr_name_match_quality)) %>%
  group_by(dataset) %>%
  summarise(n_scored = n(),
            mean_quality = round(mean(cvr_name_match_quality), 1),
            median_quality = round(median(cvr_name_match_quality), 1),
            pct_perfect_100 = round(100 * mean(cvr_name_match_quality == 100), 1),
            pct_substring = round(100 * mean(cvr_name_is_substring %in% TRUE), 1),
            .groups = "drop") %>%
  kable(caption = "buyer name-match quality summary (scored rows)")
```

# Foreign-language names on Danish-registered firms

```{r foreign-terms}
swedish_re <- paste(c("ö", "ä", "Köpenhamn", "kopenhamn", "Stockholm", "[Ss]verige", "[Ss]weden", "broderna",
                      "(?<![[:alnum:]])av(?![[:alnum:]])", "(?<![[:alnum:]])[Ss][Ee](?![[:alnum:]])"),
                    collapse = "|")

foreign_terms <- function(df, name_col, country_col, side) {
  ctry <- if (country_col %in% names(df)) df[[country_col]] else NA_character_
  tibble(dataset = df$dataset, nm = df[[name_col]],
         is_dk = is.na(ctry) | toupper(trimws(ctry)) == "DK") %>%      # no country -> Danish authority
    filter(is_dk, !is.na(nm)) %>%
    distinct(dataset, nm) %>%
    mutate(swedish = str_detect(nm, swedish_re)) %>%
    group_by(dataset) %>%
    summarise(side = side, danish_names = n(), swedish_term_names = sum(swedish),
              pct_swedish = round(100 * mean(swedish), 2), .groups = "drop")
}

bind_rows(
  foreign_terms(winners, "winner_name", "winner_country", "winner"),
  foreign_terms(buyers,  "buyer_name",  "buyer_country",  "buyer")
) %>%
  arrange(side, dataset) %>%
  kable(caption = "Swedish letters/terms on distinct Danish-registered winner/buyer names")
```

# Concat-and-dedup stacks: production vs extraction

Each stack rebuilds the **production** sample with `build_prod == TRUE` and the **extraction** sample with
`build_extr == TRUE`. Counts below are distinct valid `(tender, lot, CVR)`.

```{r stack-load}
win_stacks <- c(KFST = "kfst_winner_datasets_stacked.rds", OpenTender = "ot_winner_datasets_stacked.rds")
stacks <- imap_dfr(win_stacks, function(f, src) {
  p <- file.path(clean_dir, f)
  if (!file.exists(p)) return(tibble())
  as_tibble(readRDS(p)) %>% transmute(
    source = src, build_prod, build_extr,
    k = paste(tender_id, lot_id, norm_cvr(winner_cvr_final)),
    valid = is_valid_cvr(winner_cvr_final))
})
have_stacks <- nrow(stacks) > 0
```

## Sample sizes and method agreement (winner stacks)

```{r stack-agreement}
if (have_stacks) {
  stacks %>% filter(valid) %>% group_by(source) %>%
    summarise(production = n_distinct(k[build_prod]),
              extraction = n_distinct(k[build_extr]),
              both       = length(intersect(k[build_prod], k[build_extr])),
              .groups = "drop") %>%
    mutate(production_only = production - both, extraction_only = extraction - both) %>%
    kable(caption = "Winner stacks: production vs extraction (lot, CVR) coverage and overlap")
} else "Stacked files not found — run 3_1 / 3_2 to build them."
```

## OpenTender buyer stack

```{r stack-buyer}
buyer_stack <- file.path(clean_dir, "ot_buyer_datasets_stacked.rds")
if (file.exists(buyer_stack)) {
  as_tibble(readRDS(buyer_stack)) %>%
    transmute(build_prod, build_extr,
              k = paste(tender_id, lot_id, norm_cvr(buyer_cvr_final)),
              valid = is_valid_cvr(buyer_cvr_final)) %>%
    filter(valid) %>%
    summarise(production = n_distinct(k[build_prod]),
              extraction = n_distinct(k[build_extr]),
              both       = length(intersect(k[build_prod], k[build_extr]))) %>%
    mutate(production_only = production - both, extraction_only = extraction - both) %>%
    kable(caption = "OpenTender buyer stack: production vs extraction (lot, CVR) coverage and overlap")
} else "OpenTender buyer stack not found — run 3_3 to build it."
```
