---
title: "Winner & Buyer CVR Provenance & Quality Counts"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
    code_folding: hide
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)

report_project_dir <- local({
  d <- normalizePath(getwd(), mustWork = TRUE)
  while (!file.exists(file.path(d, "cvr-cleaning.Rproj")) && dirname(d) != d) d <- dirname(d)
  d
})
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)
source(file.path(report_project_dir, "config.R"))
source(file.path(report_project_dir, "code", "functions.R"))
```

```{r load}
clean_dir <- dirs$clean_data

# Canonical 8-digit CVR; "valid" = well-formed 8 digits (format only). Whether the CVR is a *real
# registered firm* is the separate flag `flag_valid_cvr_in_registry` (shown as `in_cvr_registry`).
norm_cvr <- function(x) {
  x <- gsub("[^0-9]", "", as.character(x))
  ifelse(x == "" | nchar(x) > 8, NA_character_, sprintf("%08d", suppressWarnings(as.integer(x))))
}
is_valid_cvr <- function(x) !is.na(norm_cvr(x))

# PRIMARY SOURCE = the delivered combined master table `clean_all_samples_combined` -- exactly what the
# server receives. Every count below is per (data_source, entity, sample), where `sample` is the
# cvr_method selection: production = grepl("production", cvr_method), extraction = grepl("extraction", cvr_method),
# name_match = grepl("name_match", cvr_method). A CVR produced by several methods (e.g. cvr_method ==
# "production; name_match") is ONE row that appears in each of those samples (the intended selection
# behaviour); the delivery is unique on (data_source, entity, tender_id, lot_id, cvr_final).
# read_clean() prefers the parquet, preserving types + leading-zero CVRs.
cmb <- as_tibble(read_clean(file.path(clean_dir, "clean_all_samples_combined.rds")))
smp <- bind_rows(
  cmb %>% filter(grepl("production", cvr_method)) %>% mutate(sample = "production"),
  cmb %>% filter(grepl("extraction", cvr_method)) %>% mutate(sample = "extraction"),
  cmb %>% filter(grepl("name_match", cvr_method)) %>% mutate(sample = "name_match")
)
# order the sample facet consistently wherever it appears
smp$sample <- factor(smp$sample, levels = c("production", "extraction", "name_match"))
```

# Combined-based counts (server-reproducible)

Everything in this section is computed directly from the de-identified server-delivery table
`clean_all_samples_combined`, so a recipient can reproduce it exactly. The raw source-CVR and firm-name
columns are removed for de-identification, so the CVR-resolution method is captured by the **sample**
selection on `cvr_method`, and all three methods are reported side by side:

- **`production`** (`grepl("production", cvr_method)`) — the canonical field+matching CVR the analyses use.
- **`extraction`** (`grepl("extraction", cvr_method)`) — raw 8-digit field CVRs, no matching.
- **`name_match`** (`grepl("name_match", cvr_method)`) — the name→registry CVR with the field CVR ignored
  (the mirror image of extraction, and the lowest-confidence method).

Per-CVR provenance is the `cvr_number_source` string; `cvr_name_match` is the name-matched CVR kept in the
delivery.

## Headline

```{r headline}
smp %>%
  group_by(data_source, entity, sample) %>%
  summarise(
    rows                = n(),
    awarded_lots        = n_distinct(paste(tender_id, lot_id)[flag_awarded %in% TRUE]),
    valid_cvr_final     = sum(is_valid_cvr(cvr_final)),
    valid_cvr_namematch = sum(is_valid_cvr(cvr_name_match)),
    in_cvr_registry     = sum(flag_valid_cvr_in_registry %in% TRUE),
    unique_final_cvrs   = n_distinct(norm_cvr(cvr_final)[is_valid_cvr(cvr_final)]),
    pct_final_valid     = round(100 * mean(is_valid_cvr(cvr_final)), 1),
    .groups = "drop"
  ) %>%
  arrange(data_source, entity, sample) %>%
  kable(caption = "Valid CVRs by data source, entity and sample (from the delivered combined)")
```

## `cvr_number_source` — how each final CVR was obtained

```{r cvr-number-source}
smp %>%
  count(data_source, entity, sample, cvr_number_source) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "cvr_number_source row counts, per data source / entity / sample")
```

## `matching_candidate_type` and `name_match_status`

Name matching underlies **two** of the three methods: `production` (field CVR reconciled with matching) and
`name_match` (name→registry, field CVR ignored). `extraction` pulls raw 8-digit field CVRs with no matching,
so it carries no match info by construction and is excluded here. All match-related tables below are therefore
computed on the **production and name_match samples**, shown side by side per `sample`.

```{r cand-type}
matched <- smp %>% filter(sample %in% c("production", "name_match"))

matched %>%
  count(data_source, entity, sample, matching_candidate_type) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "matching_candidate_type row counts (production & name_match samples)")

matched %>%
  count(data_source, entity, sample, name_match_status) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "name_match_status row counts (production & name_match samples)")
```

## Provenance flags (count of TRUE)

```{r flags}
# Entity-agnostic provenance flags (the entity-specific missing-CVR flags differ winner vs buyer, so
# they are excluded from this pooled table).
prov_flags <- c("flag_name_match_found", "flag_name_match_ambiguous", "flag_review_name_match",
                "flag_manual_name_review", "flag_cvr_recovered_from_invalid", "flag_valid_cvr_in_registry")
smp %>%
  filter(sample %in% c("production", "name_match")) %>%
  group_by(data_source, entity, sample) %>%
  summarise(across(all_of(prov_flags), ~ sum(.x %in% TRUE)), .groups = "drop") %>%
  pivot_longer(-c(data_source, entity, sample), names_to = "flag", values_to = "n_true") %>%
  arrange(data_source, entity, sample, flag) %>%
  kable(caption = "Provenance flags (rows flagged TRUE, production & name_match samples)")
```

## Name-match source and method

```{r match-source}
matched %>%
  filter(!is.na(name_match_source)) %>%
  count(data_source, entity, sample, name_match_source) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "Name-match source: registry key that matched (official name vs biname) — production & name_match samples")

matched %>%
  filter(!is.na(name_match_method)) %>%
  count(data_source, entity, sample, name_match_method) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "Name-match method: exact vs fuzzy — production & name_match samples")
```

## Name-match quality

```{r quality}
matched %>%
  filter(!is.na(cvr_name_match_quality)) %>%
  group_by(data_source, entity, sample) %>%
  summarise(
    n_scored        = n(),
    mean_quality    = round(mean(cvr_name_match_quality), 1),
    median_quality  = round(median(cvr_name_match_quality), 1),
    pct_perfect_100 = round(100 * mean(cvr_name_match_quality == 100), 1),
    pct_substring   = round(100 * mean(cvr_name_is_substring %in% TRUE), 1),
    .groups = "drop"
  ) %>%
  arrange(data_source, entity, sample) %>%
  kable(caption = "Name-match quality summary (scored rows, production & name_match samples)")

matched %>%
  filter(!is.na(cvr_name_match_quality)) %>%
  mutate(bucket = cut(cvr_name_match_quality, c(-Inf, 50, 80, 99.999, Inf),
                      labels = c("<50", "50-80", "80-<100", "100"))) %>%
  count(data_source, entity, sample, bucket) %>%
  arrange(data_source, entity, sample, bucket) %>%
  kable(caption = "cvr_name_match_quality distribution (scored rows, production & name_match samples)")
```

## Cross-source winner agreement

```{r agreement}
# Do KFST / OpenTender / TED assign the same winner-CVR set to a shared notice (and notice-lot)? From the
# combined PRODUCTION sample, using cvr_final + ted_notice_id + data_source (all kept in the delivery).
prod_win <- cmb %>%
  filter(grepl("production", cvr_method), entity == "winner", flag_awarded %in% TRUE,
         !is.na(ted_notice_id), ted_notice_id != "")

winner_sets <- function(df, keys) {
  df %>%
    mutate(cvr = norm_cvr(cvr_final)) %>%
    filter(!is.na(cvr), if_all(all_of(keys), ~ !is.na(.x) & .x != "")) %>%
    group_by(across(all_of(keys))) %>%
    summarise(cvrs = list(sort(unique(cvr))), .groups = "drop")
}

agree <- function(a, b, keys, label) {
  A <- winner_sets(filter(prod_win, data_source == a), keys)
  B <- winner_sets(filter(prod_win, data_source == b), keys)
  j <- inner_join(A, B, by = keys, suffix = c("_a", "_b"))
  # Per-notice Jaccard share of winner-CVRs: |A intersect B| / |A union B|.
  inter <- map2_int(j$cvrs_a, j$cvrs_b, ~ length(intersect(.x, .y)))
  uni   <- map2_int(j$cvrs_a, j$cvrs_b, ~ length(union(.x, .y)))
  share <- inter / uni
  incomplete <- share < 1                       # notices where the two sources do NOT fully agree
  tibble(
    comparison         = label,
    level              = if (length(keys) > 1) "notice-lot" else "notice",
    comparable         = nrow(j),
    exact_pct          = round(100 * mean(map2_lgl(j$cvrs_a, j$cvrs_b, setequal)), 1),
    any_common_pct     = round(100 * mean(map2_lgl(j$cvrs_a, j$cvrs_b, ~ length(intersect(.x, .y)) > 0)), 1),
    # Share of common CVRs within a notice (Jaccard). Unweighted = mean over notices; weighted = pooled
    # sum(intersection)/sum(union), i.e. each notice weighted by its union size; incomplete = mean over
    # only the notices without complete agreement (share < 1).
    mean_share_pct     = round(100 * mean(share), 1),
    wtd_mean_share_pct = round(100 * sum(inter) / sum(uni), 1),
    n_incomplete       = sum(incomplete),
    incomplete_mean_share_pct = if (any(incomplete)) round(100 * mean(share[incomplete]), 1) else NA_real_
  )
}

# Notice-LEVEL only: cross-source lot-level agreement needs a shared lot key. `lot_id` is not
# comparable across sources (TED "LOT-0001" vs OpenTender UUIDs), and the ordinal `lot_number` that
# made it comparable is dropped from the combined -- so lot-level agreement is not reproducible here.
bind_rows(
  agree("TED", "KFST",       "ted_notice_id", "TED vs KFST"),
  agree("TED", "OpenTender", "ted_notice_id", "TED vs OpenTender"),
  agree("KFST", "OpenTender", "ted_notice_id", "KFST vs OpenTender")
) %>%
  arrange(comparison) %>%
  kable(caption = paste("Winner-CVR agreement across sources at the notice level (production sample).",
                        "share = |A intersect B| / |A union B| per notice:",
                        "mean_share_pct = unweighted mean; wtd_mean_share_pct = union-size-weighted (pooled);",
                        "incomplete_mean_share_pct = unweighted mean over the n_incomplete notices without full agreement."))
```

# Production / extraction / name_match coverage and overlap

All three samples are selected from the delivered combined via `cvr_method`: **production** =
`grepl("production", cvr_method)`, **extraction** = `grepl("extraction", cvr_method)`, **name_match** =
`grepl("name_match", cvr_method)`. A distinct valid `(tender, lot, CVR)` produced by several methods (e.g.
`cvr_method == "production; name_match"`) is counted in **each** of those samples (the intended behaviour when
a lot's methods agree). `name_match_only` is the count of keys found by name matching that appear in **neither**
production nor extraction — the CVRs name-matching contributes on its own. This reproduces the per-source
stacked-file overlap using only `clean_all_samples_combined`, so a server recipient can reproduce it exactly.

```{r method-overlap}
cmb %>%
  filter(is_valid_cvr(cvr_final)) %>%
  mutate(k = paste(tender_id, lot_id, norm_cvr(cvr_final))) %>%
  group_by(data_source, entity) %>%
  summarise(kp = list(unique(k[grepl("production", cvr_method)])),
            ke = list(unique(k[grepl("extraction", cvr_method)])),
            kn = list(unique(k[grepl("name_match", cvr_method)])),
            .groups = "drop") %>%
  transmute(
    data_source, entity,
    production      = lengths(kp),
    extraction      = lengths(ke),
    name_match      = lengths(kn),
    prod_and_extr   = mapply(function(a, b) length(intersect(a, b)), kp, ke),
    prod_and_name   = mapply(function(a, b) length(intersect(a, b)), kp, kn),
    extr_and_name   = mapply(function(a, b) length(intersect(a, b)), ke, kn),
    name_match_only = mapply(function(n, a, b) length(setdiff(n, union(a, b))), kn, kp, ke)
  ) %>%
  arrange(data_source, entity) %>%
  kable(caption = "Production / extraction / name_match (tender, lot, CVR) coverage and pairwise overlap, per source/entity; name_match_only = keys unique to name matching")
```

## Method agreement (within source, lot level)

Within a single source `lot_id` is comparable (unlike across sources), so we can measure how much the
CVR-resolution methods agree per lot, for **all three pairwise comparisons** (production vs extraction,
production vs name_match, extraction vs name_match). For each `(tender, lot)` where **both** methods of a pair
produced a CVR, the share is the Jaccard `|A ∩ B| / |A ∪ B|`; `mean_share_pct` is the unweighted mean over
lots, `wtd_mean_share_pct` weights each lot by its union size (pooled), and `incomplete_mean_share_pct` is the
mean over only the `n_incomplete` lots without complete agreement. (KFST buyers have no extraction variant, so
pairs involving extraction do not appear for them.)

```{r method-agreement}
lot_sets <- cmb %>%
  filter(is_valid_cvr(cvr_final)) %>%
  mutate(cvr = norm_cvr(cvr_final)) %>%
  group_by(data_source, entity, tender_id, lot_id) %>%
  summarise(prod = list(sort(unique(cvr[grepl("production", cvr_method)]))),
            extr = list(sort(unique(cvr[grepl("extraction", cvr_method)]))),
            name = list(sort(unique(cvr[grepl("name_match", cvr_method)]))), .groups = "drop")

pair_agree <- function(df, A, B, label) {
  x <- df %>% filter(lengths(.data[[A]]) > 0 & lengths(.data[[B]]) > 0)   # both methods present in the lot
  if (!nrow(x)) return(NULL)
  a <- x[[A]]; b <- x[[B]]
  inter <- map2_int(a, b, ~ length(intersect(.x, .y)))
  uni   <- map2_int(a, b, ~ length(union(.x, .y)))
  share <- inter / uni
  tibble(data_source = x$data_source, entity = x$entity, pair = label,
         inter, uni, share, exact = map2_lgl(a, b, setequal), anyc = inter > 0) %>%
    group_by(data_source, entity, pair) %>%
    summarise(comparable_lots           = n(),
              exact_pct                 = round(100 * mean(exact), 1),
              any_common_pct            = round(100 * mean(anyc), 1),
              mean_share_pct            = round(100 * mean(share), 1),
              wtd_mean_share_pct        = round(100 * sum(inter) / sum(uni), 1),
              n_incomplete              = sum(share < 1),
              incomplete_mean_share_pct = ifelse(any(share < 1), round(100 * mean(share[share < 1]), 1), NA_real_),
              .groups = "drop")
}

bind_rows(
  pair_agree(lot_sets, "prod", "extr", "production vs extraction"),
  pair_agree(lot_sets, "prod", "name", "production vs name_match"),
  pair_agree(lot_sets, "extr", "name", "extraction vs name_match")
) %>%
  arrange(data_source, entity, pair) %>%
  kable(caption = "Pairwise CVR-method agreement WITHIN each source, at the lot level (lots where both methods of the pair are present)")
```
