---
title: "Winner & Buyer CVR Provenance & Quality Counts"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
    code_folding: hide
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)

report_project_dir <- local({
  d <- normalizePath(getwd(), mustWork = TRUE)
  while (!file.exists(file.path(d, "cvr-cleaning.Rproj")) && dirname(d) != d) d <- dirname(d)
  d
})
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)
source(file.path(report_project_dir, "config.R"))
source(file.path(report_project_dir, "code", "functions.R"))
```

```{r load}
clean_dir <- dirs$clean_data
ted_dir   <- file.path(dirs$intermediates, "ted")

# Canonical 8-digit CVR; "valid" = well-formed 8 digits (format only). Whether the CVR is a *real
# registered firm* is the separate flag `flag_valid_cvr_in_registry` (shown as `in_cvr_registry`).
norm_cvr <- function(x) {
  x <- gsub("[^0-9]", "", as.character(x))
  ifelse(x == "" | nchar(x) > 8, NA_character_, sprintf("%08d", suppressWarnings(as.integer(x))))
}
is_valid_cvr <- function(x) !is.na(norm_cvr(x))

# PRIMARY SOURCE = the delivered combined master table `clean_all_samples_combined` -- exactly what the
# server receives. Every count below is per (data_source, entity, sample), where `sample` is the
# build-flag selection: production = `build_prod`, extraction = `build_extr`. A lot whose two methods
# agree carries BOTH flags, so it appears in both samples (that is the intended selection behaviour).
# read_clean() prefers the parquet, preserving types + leading-zero CVRs.
cmb <- as_tibble(read_clean(file.path(clean_dir, "clean_all_samples_combined.rds")))
smp <- bind_rows(
  cmb %>% filter(build_prod %in% TRUE) %>% mutate(sample = "production"),
  cmb %>% filter(build_extr %in% TRUE) %>% mutate(sample = "extraction")
)
```

# Combined-based counts (server-reproducible)

Everything in this section is computed directly from the de-identified server-delivery table
`clean_all_samples_combined`, so a recipient can reproduce it exactly. The raw source-CVR and firm-name
columns are removed for de-identification, so the old "extracted vs name-matched CVR" split is now the
**sample** (`extraction` = raw field CVRs via `build_extr`; `production` = the resolved final CVR via
`build_prod`), and per-CVR provenance is the `cvr_number_source` string. `cvr_name_match` is the
name-matched CVR that is kept in the delivery.

## Headline

```{r headline}
smp %>%
  group_by(data_source, entity, sample) %>%
  summarise(
    rows                = n(),
    awarded_lots        = n_distinct(paste(tender_id, lot_id)[flag_awarded %in% TRUE]),
    valid_cvr_final     = sum(is_valid_cvr(cvr_final)),
    valid_cvr_namematch = sum(is_valid_cvr(cvr_name_match)),
    in_cvr_registry     = sum(flag_valid_cvr_in_registry %in% TRUE),
    unique_final_cvrs   = n_distinct(norm_cvr(cvr_final)[is_valid_cvr(cvr_final)]),
    pct_final_valid     = round(100 * mean(is_valid_cvr(cvr_final)), 1),
    .groups = "drop"
  ) %>%
  arrange(data_source, entity, sample) %>%
  kable(caption = "Valid CVRs by data source, entity and sample (from the delivered combined)")
```

## `cvr_number_source` — how each final CVR was obtained

```{r cvr-number-source}
smp %>%
  count(data_source, entity, sample, cvr_number_source) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "cvr_number_source row counts, per data source / entity / sample")
```

## `matching_candidate_type` and `name_match_status`

```{r cand-type}
smp %>%
  count(data_source, entity, sample, matching_candidate_type) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "matching_candidate_type row counts")

smp %>%
  count(data_source, entity, sample, name_match_status) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "name_match_status row counts")
```

## Provenance flags (count of TRUE)

```{r flags}
# Entity-agnostic provenance flags (the entity-specific missing-CVR flags differ winner vs buyer, so
# they are excluded from this pooled table).
prov_flags <- c("flag_name_match_found", "flag_name_match_ambiguous", "flag_review_name_match",
                "flag_manual_name_review", "flag_cvr_recovered_from_invalid", "flag_valid_cvr_in_registry")
smp %>%
  group_by(data_source, entity, sample) %>%
  summarise(across(all_of(prov_flags), ~ sum(.x %in% TRUE)), .groups = "drop") %>%
  pivot_longer(-c(data_source, entity, sample), names_to = "flag", values_to = "n_true") %>%
  arrange(data_source, entity, sample, flag) %>%
  kable(caption = "Provenance flags (rows flagged TRUE)")
```

## Name-match source and method

```{r match-source}
smp %>%
  filter(!is.na(name_match_source)) %>%
  count(data_source, entity, sample, name_match_source) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "Name-match source: registry key that matched (official name vs biname)")

smp %>%
  filter(!is.na(name_match_method)) %>%
  count(data_source, entity, sample, name_match_method) %>%
  arrange(data_source, entity, sample, desc(n)) %>%
  kable(caption = "Name-match method: exact vs fuzzy")
```

## Name-match quality

```{r quality}
smp %>%
  filter(!is.na(cvr_name_match_quality)) %>%
  group_by(data_source, entity, sample) %>%
  summarise(
    n_scored        = n(),
    mean_quality    = round(mean(cvr_name_match_quality), 1),
    median_quality  = round(median(cvr_name_match_quality), 1),
    pct_perfect_100 = round(100 * mean(cvr_name_match_quality == 100), 1),
    pct_substring   = round(100 * mean(cvr_name_is_substring %in% TRUE), 1),
    .groups = "drop"
  ) %>%
  arrange(data_source, entity, sample) %>%
  kable(caption = "Name-match quality summary (scored rows only)")

smp %>%
  filter(!is.na(cvr_name_match_quality)) %>%
  mutate(bucket = cut(cvr_name_match_quality, c(-Inf, 50, 80, 99.999, Inf),
                      labels = c("<50", "50-80", "80-<100", "100"))) %>%
  count(data_source, entity, sample, bucket) %>%
  arrange(data_source, entity, sample, bucket) %>%
  kable(caption = "cvr_name_match_quality distribution (scored rows)")
```

## Cross-source winner agreement

```{r agreement}
# Do KFST / OpenTender / TED assign the same winner-CVR set to a shared notice (and notice-lot)? From the
# combined PRODUCTION sample, using cvr_final + ted_notice_id + data_source (all kept in the delivery).
prod_win <- cmb %>%
  filter(build_prod %in% TRUE, entity == "winner", flag_awarded %in% TRUE,
         !is.na(ted_notice_id), ted_notice_id != "")

winner_sets <- function(df, keys) {
  df %>%
    mutate(cvr = norm_cvr(cvr_final)) %>%
    filter(!is.na(cvr), if_all(all_of(keys), ~ !is.na(.x) & .x != "")) %>%
    group_by(across(all_of(keys))) %>%
    summarise(cvrs = list(sort(unique(cvr))), .groups = "drop")
}

agree <- function(a, b, keys, label) {
  A <- winner_sets(filter(prod_win, data_source == a), keys)
  B <- winner_sets(filter(prod_win, data_source == b), keys)
  j <- inner_join(A, B, by = keys, suffix = c("_a", "_b"))
  tibble(
    comparison     = label,
    level          = if (length(keys) > 1) "notice-lot" else "notice",
    comparable     = nrow(j),
    exact_pct      = round(100 * mean(map2_lgl(j$cvrs_a, j$cvrs_b, setequal)), 1),
    any_common_pct = round(100 * mean(map2_lgl(j$cvrs_a, j$cvrs_b, ~ length(intersect(.x, .y)) > 0)), 1)
  )
}

# Notice-LEVEL only: cross-source lot-level agreement needs a shared lot key. `lot_id` is not
# comparable across sources (TED "LOT-0001" vs OpenTender UUIDs), and the ordinal `lot_number` that
# made it comparable is dropped from the combined -- so lot-level agreement is not reproducible here.
bind_rows(
  agree("TED", "KFST",       "ted_notice_id", "TED vs KFST"),
  agree("TED", "OpenTender", "ted_notice_id", "TED vs OpenTender"),
  agree("KFST", "OpenTender", "ted_notice_id", "KFST vs OpenTender")
) %>%
  arrange(comparison) %>%
  kable(caption = "Winner-CVR agreement across sources at the notice level (production sample, from the combined)")
```

# Internal analyses (NOT reproducible from the delivered combined)

The two analyses below need the **raw winner-CVR field** and the **firm names**, which are removed from
`clean_all_samples_combined` for de-identification. They are therefore computed from the internal
per-source matched files and **cannot be reproduced by a server recipient**.

```{r internal-load}
ted_path <- file.path(clean_dir, "clean_winner_data_ted_name_matched.rds")
if (!file.exists(ted_path)) ted_path <- file.path(ted_dir, "ted_winner_data_name_matched.rds")
all_winners <- bind_rows(
  read_clean(file.path(clean_dir, "clean_winner_data_kfst_name_matched.rds")) %>% mutate(dataset = "KFST"),
  read_clean(file.path(clean_dir, "clean_winner_data_ot_name_matched.rds"))   %>% mutate(dataset = "OpenTender"),
  read_clean(ted_path)                                                        %>% mutate(dataset = "TED")
) %>% as_tibble() %>%
  mutate(is_winner = if ("is_winner" %in% names(.)) coalesce(is_winner, TRUE) else TRUE) %>%
  filter(is_winner %in% TRUE)

tedb_path <- file.path(clean_dir, "clean_buyer_data_ted_name_matched.rds")
if (!file.exists(tedb_path)) tedb_path <- file.path(ted_dir, "ted_buyer_data_name_matched.rds")
buyers_all <- bind_rows(
  read_clean(file.path(clean_dir, "clean_buyer_data_kfst_name_matched.rds")) %>% mutate(dataset = "KFST"),
  read_clean(file.path(clean_dir, "clean_buyer_data_ot_name_matched.rds"))   %>% mutate(dataset = "OpenTender"),
  read_clean(tedb_path)                                                      %>% mutate(dataset = "TED")
) %>% as_tibble()
```

## Multiple-CVR record structure (internal)

```{r multiple-cvr}
# How many valid final CVRs came from a raw record whose winner-CVR field listed MULTIPLE CVRs (expanded
# into several winner rows) vs a single-CVR record vs no field CVR (final CVR came from name matching).
tok_count <- function(x) { x <- as.character(x); x[is.na(x)] <- ""
  vapply(strsplit(x, "[^0-9]+"), function(t) { t <- unique(t[t != ""]); sum(nchar(t) == 8L) }, integer(1)) }

all_winners %>%
  filter(is_valid_cvr(winner_cvr_final)) %>%
  mutate(
    n_field_cvr = if_else(dataset == "OpenTender",
                          suppressWarnings(as.integer(n_valid_cvr_raw)),
                          tok_count(winner_cvr_original)),
    cvr_record  = case_when(n_field_cvr >= 2 ~ "multiple-CVR record (expanded)",
                            n_field_cvr == 1 ~ "single-CVR record",
                            TRUE             ~ "no field CVR (name-matched)")
  ) %>%
  count(dataset, cvr_record) %>%
  pivot_wider(names_from = dataset, values_from = n, values_fill = 0) %>%
  kable(caption = "Valid winner CVRs by raw-record CVR structure (INTERNAL: needs the raw winner-CVR field)")
```

## Foreign-language names (internal)

```{r foreign-terms}
swedish_re <- paste(c("ö", "ä", "Köpenhamn", "kopenhamn", "Stockholm", "[Ss]verige", "[Ss]weden", "broderna",
                      "(?<![[:alnum:]])av(?![[:alnum:]])", "(?<![[:alnum:]])[Ss][Ee](?![[:alnum:]])"),
                    collapse = "|")

foreign_terms <- function(df, name_col, country_col, side) {
  ctry <- if (country_col %in% names(df)) df[[country_col]] else NA_character_
  tibble(dataset = df$dataset, nm = df[[name_col]],
         is_dk = is.na(ctry) | toupper(trimws(ctry)) == "DK") %>%
    filter(is_dk, !is.na(nm)) %>%
    distinct(dataset, nm) %>%
    mutate(swedish = str_detect(nm, swedish_re)) %>%
    group_by(dataset) %>%
    summarise(side = side, danish_names = n(), swedish_term_names = sum(swedish),
              pct_swedish = round(100 * mean(swedish), 2), .groups = "drop")
}

bind_rows(
  foreign_terms(all_winners, "winner_name", "winner_country", "winner"),
  foreign_terms(buyers_all,  "buyer_name",  "buyer_country",  "buyer")
) %>%
  arrange(side, dataset) %>%
  kable(caption = "Swedish letters/terms on distinct Danish-registered names (INTERNAL: needs firm names)")
```

# Concat-and-dedup stacks: production vs extraction

Each stack rebuilds the **production** sample with `build_prod == TRUE` and the **extraction** sample with
`build_extr == TRUE`. Counts below are distinct valid `(tender, lot, CVR)`.

```{r stack-load}
win_stacks <- c(KFST = "kfst_winner_datasets_stacked.rds", OpenTender = "ot_winner_datasets_stacked.rds")
stacks <- imap_dfr(win_stacks, function(f, src) {
  p <- file.path(clean_dir, f)
  if (!file.exists(p)) return(tibble())
  as_tibble(read_clean(p)) %>% transmute(
    source = src, build_prod, build_extr,
    k = paste(tender_id, lot_id, norm_cvr(winner_cvr_final)),
    valid = is_valid_cvr(winner_cvr_final))
})
have_stacks <- nrow(stacks) > 0
```

## Sample sizes and method agreement (winner stacks)

```{r stack-agreement}
if (have_stacks) {
  stacks %>% filter(valid) %>% group_by(source) %>%
    summarise(production = n_distinct(k[build_prod == TRUE]),
              extraction = n_distinct(k[build_extr == TRUE]),
              both       = length(intersect(k[build_prod == TRUE], k[build_extr == TRUE])),
              .groups = "drop") %>%
    mutate(production_only = production - both, extraction_only = extraction - both) %>%
    kable(caption = "Winner stacks: production vs extraction (lot, CVR) coverage and overlap")
} else "Stacked files not found — run 3_1 / 3_2 to build them."
```

## OpenTender buyer stack

```{r stack-buyer}
buyer_stack <- file.path(clean_dir, "ot_buyer_datasets_stacked.rds")
if (file.exists(buyer_stack)) {
  as_tibble(read_clean(buyer_stack)) %>%
    transmute(build_prod, build_extr,
              k = paste(tender_id, lot_id, norm_cvr(buyer_cvr_final)),
              valid = is_valid_cvr(buyer_cvr_final)) %>%
    filter(valid) %>%
    summarise(production = n_distinct(k[build_prod == TRUE]),
              extraction = n_distinct(k[build_extr == TRUE]),
              both       = length(intersect(k[build_prod == TRUE], k[build_extr == TRUE]))) %>%
    mutate(production_only = production - both, extraction_only = extraction - both) %>%
    kable(caption = "OpenTender buyer stack: production vs extraction (lot, CVR) coverage and overlap")
} else "OpenTender buyer stack not found — run 3_3 to build it."
```
