---
title: "TWFE event studies by data source x entity x CVR method"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    fig_width: 11
    fig_height: 10
    df_print: kable
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.align = "center", dpi = 110)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table); library(fixest); library(ggplot2)
}))
# knitr::opts_knit$get("output.dir") is NULL when NOT knitting (running chunks interactively), and
# nzchar(NULL) is logical(0), so a bare if() on it errors with "argument is of length zero". Fall back to
# getwd(), then walk up to the .Rproj marker so this works from code/analysis/ as well as the repo root.
project_dir <- local({
  d <- knitr::opts_knit$get("output.dir")
  if (is.null(d) || !nzchar(d)) d <- getwd()
  d <- normalizePath(d, mustWork = TRUE)
  while (!file.exists(file.path(d, "cvr-cleaning.Rproj")) && dirname(d) != d) d <- dirname(d)
  d
})
while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) && dirname(project_dir) != project_dir)
  project_dir <- dirname(project_dir)
knitr::opts_knit$set(root.dir = project_dir)
setwd(project_dir); source("config.R"); source("code/functions.R")
emp_dir <- dirs$employment

H         <- 8L                       # +/- window (quarters)
FREQ      <- "quarterly_spliced"
MIN_FIRMS <- 30L                      # drop cells with fewer firms
MIN_FTE   <- 0
ENTITIES  <- c("winner", "buyer")
```

A firm-fixed-effect event study of (log) quarterly-spliced employment around each firm's **first award**, run
**separately for every `data_source | entity | cvr_method` cell**. This is the naive within-sample design (no
matched controls — biased under staggered timing; the rigorous design is the matched winner-vs-non-winner
study). FE = firm only; balanced panel with strictly positive FTE in each of the +/-`r H` event quarters;
cells with fewer than `r MIN_FIRMS` firms are dropped. Each panel below is one cell; `t = -1` is omitted.

```{r prep}
# --- firm quarterly employment panel -----------------------------------------------------------------
emp <- as.data.table(readRDS(file.path(emp_dir, "firm_employment_panel_all.rds")))
nonwin <- file.path(emp_dir, "cvr_employment_history_nonwinner.rds")
if (file.exists(nonwin)) emp <- rbind(emp, as.data.table(readRDS(nonwin)), use.names = TRUE, fill = TRUE)
emp[, cvr := as.character(cvr)]
firm <- emp[frequency == FREQ & !is.na(year) & !is.na(quarter),
            .(cvr, qidx = year * 4L + quarter, fte = as.numeric(fte))]
firm <- unique(firm, by = c("cvr", "qidx"))

# --- events: first award per firm, within each (data_source, entity, cvr_method) cell ----------------
cmb <- as.data.table(read_clean(file.path(dirs$clean_data, "tender_data_2006_2026")))
cmb <- cmb[entity %chin% ENTITIES & !is.na(cvr_final) & cvr_final != "" & !is.na(award_date)]
cmb[, cvr := sprintf("%08d", suppressWarnings(as.integer(gsub("[^0-9]", "", cvr_final))))]
cmb <- cmb[grepl("^[0-9]{8}$", cvr)]
cmb[, award_date := as.Date(award_date)]
ev <- rbind(
  cmb[grepl("production", cvr_method), .(data_source, entity, method = "production", cvr, award_date)],
  cmb[grepl("extraction", cvr_method), .(data_source, entity, method = "extraction", cvr, award_date)],
  cmb[grepl("name_match", cvr_method), .(data_source, entity, method = "name_match", cvr, award_date)])
ev[, cell := paste(data_source, entity, method, sep = " | ")]
ev <- ev[, .(award_date = min(award_date)), by = .(cell, cvr)]
ev[, event_qidx := year(award_date) * 4L + quarter(award_date)]

# --- balanced +/-H panel with positive FTE, drop small cells -----------------------------------------
panel <- firm[ev, on = "cvr", allow.cartesian = TRUE, nomatch = NULL]
panel[, event_time := qidx - event_qidx]
panel <- panel[event_time %between% c(-H, H) & !is.na(fte) & fte > MIN_FTE]
panel[, n_periods := uniqueN(event_time), by = .(cell, cvr)]
panel <- panel[n_periods == 2L * H + 1L]
panel[, n_firms := uniqueN(cvr), by = cell]
panel <- panel[n_firms >= MIN_FIRMS]

# --- per-cell event-time coefficients (level + log FTE), firm FE, clustered by firm ------------------
cells <- sort(unique(panel$cell))
coefs <- rbindlist(lapply(cells, function(cl) {
  dt <- panel[cell == cl]
  one <- function(m, lab) {
    ct <- as.data.table(coeftable(m), keep.rownames = "term")[grepl("event_time", term)]
    ct[, event_time := as.integer(gsub(".*event_time::(-?[0-9]+).*", "\\1", term))]
    ct <- rbind(ct[, .(event_time, est = Estimate, se = `Std. Error`)], data.table(event_time = -1L, est = 0, se = 0))
    ct[, `:=`(cell = cl, outcome = lab)]; ct[]
  }
  rbind(one(feols(fte      ~ i(event_time, ref = -1) | cvr, dt, cluster = ~cvr), "FTE (level)"),
        one(feols(log(fte) ~ i(event_time, ref = -1) | cvr, dt, cluster = ~cvr), "log FTE"))
}))
coefs[, `:=`(lo = est - 1.96 * se, hi = est + 1.96 * se)]
setorder(coefs, cell, outcome, event_time)

cell_summary <- panel[, .(firms = uniqueN(cvr), firm_quarters = .N), by = cell][order(cell)]
```

Cells estimated (firms per cell): `r nrow(cell_summary)` cells.

```{r cell-table}
knitr::kable(cell_summary, col.names = c("cell (source | entity | method)", "firms", "firm-quarters"))
```

# log FTE event studies (all cells)

```{r plot-log, fig.width=11, fig.height=10}
ggplot(coefs[outcome == "log FTE"], aes(event_time, est)) +
  geom_hline(yintercept = 0, colour = "grey50", linewidth = 0.3) +
  geom_vline(xintercept = -0.5, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#2c7fb8", alpha = 0.15) +
  geom_line(colour = "#2c7fb8", linewidth = 0.5) + geom_point(colour = "#2c7fb8", size = 1.4) +
  facet_wrap(~ cell, scales = "free_y", ncol = 3) +
  scale_x_continuous(breaks = seq(-H, H, 4)) +
  labs(title = sprintf("log FTE around first award, by cell (+/-%d quarters, firm FE)", H),
       x = "Quarters relative to first award (t = -1 omitted)", y = "log FTE coefficient",
       caption = "Shaded = 95% CI, clustered by firm. Naive within-sample (no matched controls).") +
  theme_light(base_size = 10) + theme(plot.title = element_text(face = "bold"),
                                      strip.text = element_text(size = 7.5))
```

# FTE level event studies (all cells)

```{r plot-level, fig.width=11, fig.height=10}
ggplot(coefs[outcome == "FTE (level)"], aes(event_time, est)) +
  geom_hline(yintercept = 0, colour = "grey50", linewidth = 0.3) +
  geom_vline(xintercept = -0.5, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#d95f0e", alpha = 0.15) +
  geom_line(colour = "#d95f0e", linewidth = 0.5) + geom_point(colour = "#d95f0e", size = 1.4) +
  facet_wrap(~ cell, scales = "free_y", ncol = 3) +
  scale_x_continuous(breaks = seq(-H, H, 4)) +
  labs(title = sprintf("FTE (level) around first award, by cell (+/-%d quarters, firm FE)", H),
       x = "Quarters relative to first award (t = -1 omitted)", y = "FTE coefficient",
       caption = "Shaded = 95% CI, clustered by firm. Naive within-sample (no matched controls).") +
  theme_light(base_size = 10) + theme(plot.title = element_text(face = "bold"),
                                      strip.text = element_text(size = 7.5))
```
