---
title: "Matched winner vs non-winner event studies (TED co-bidder controls)"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    fig_width: 11
    fig_height: 5
    df_print: kable
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

<!--
Running this file -- it is standalone; there is no companion .R script.
  1. Knit          : the Knit button (the hook above writes to output/docs/), or
                     Rscript -e 'rmarkdown::render("code/analysis/13_estudy_winner_vs_nonwinner_matched.Rmd",
                                                   output_dir = "output/docs")'
                     A bare render() does not use the hook, so without output_dir the HTML lands in
                     code/analysis/.
  2. Interactively : open it and run chunks. project_dir falls back to getwd() and walks up to the
                     .Rproj marker, so this works from the repo root or from code/analysis/.
  3. As a script   : knitr::purl("code/analysis/13_estudy_winner_vs_nonwinner_matched.Rmd", output = "/tmp/es.R")
                     extracts the code on demand -- generate it, do not hand-maintain a second copy.
Parameters are ESWNW_* environment variables (see the setup chunk); ESWNW_SAVE=0 skips writing .rds.
NOT carried over from the retired .R: the optional Virk pull. A report should not make API calls as a
side effect -- employment pulls now belong to code/matching/1_build_universe.R.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.align = "center", dpi = 110)
suppressWarnings(suppressPackageStartupMessages({
  library(data.table); library(fixest); library(ggplot2)
}))
# knitr::opts_knit$get("output.dir") is NULL when NOT knitting (running chunks interactively), and
# nzchar(NULL) is logical(0), so a bare if() on it errors with "argument is of length zero". Fall back to
# getwd(), then walk up to the .Rproj marker so this works from code/analysis/ as well as the repo root.
project_dir <- local({
  d <- knitr::opts_knit$get("output.dir")
  if (is.null(d) || !nzchar(d)) d <- getwd()
  d <- normalizePath(d, mustWork = TRUE)
  while (!file.exists(file.path(d, "cvr-cleaning.Rproj")) && dirname(d) != d) d <- dirname(d)
  d
})
knitr::opts_knit$set(root.dir = project_dir)
setwd(project_dir); source("config.R"); source("code/functions.R")
emp_dir <- dirs$employment

# Parameters are env-overridable so this file can be driven non-interactively without editing it --
# see the "Running this file" note above. Defaults reproduce the previous hardcoded behaviour.
.envint <- function(k, d) { v <- Sys.getenv(k, ""); if (nzchar(v)) as.integer(v) else as.integer(d) }
.envnum <- function(k, d) { v <- Sys.getenv(k, ""); if (nzchar(v)) as.numeric(v) else as.numeric(d) }
.envvec <- function(k, d) { v <- Sys.getenv(k, ""); x <- if (nzchar(v)) v else d
                            as.integer(strsplit(trimws(x), "[ ,]+")[[1]]) }

MIN_FTE    <- .envnum("ESWNW_MIN_FTE",    0)
MIN_STACKS <- .envint("ESWNW_MIN_STACKS", 20)
IND_DIGITS <- .envint("ESWNW_IND_DIGITS", 2)    # industry FE granularity: 2 = division
QUARTER_WINDOWS <- .envvec("ESWNW_QUARTER_WINDOWS", "8 4")    # +/- quarters
SAVE_RDS   <- Sys.getenv("ESWNW_SAVE", "1") == "1"   # persist models + panel per window

# Build a firm employment panel at a given frequency, keyed by (cvr, tidx). tidx is a quarter index
# (year*4 + quarter) or month index (year*12 + month). Audits duplicate (cvr, tidx) rows: if any disagree
# on FTE or industry we WARN and resolve deterministically (highest-FTE row, via setorder) rather than
# relying on raw row order.
prep_firm <- function(freq, per, subcol) {
  f <- emp[frequency == freq & !is.na(year) & !is.na(get(subcol)),
           .(cvr, tidx = year * per + get(subcol), fte = as.numeric(fte), industry_code = as.character(industry_code),
             registration_date, capital_amount, capital_currency, legal_form_short)]
  disagree <- f[, .(bad = uniqueN(fte[!is.na(fte)]) > 1L |
                          uniqueN(na.omit(substr(industry_code, 1L, IND_DIGITS))) > 1L),
                by = .(cvr, tidx)][bad == TRUE, .N]
  if (disagree) warning(sprintf("%s: %d (cvr, period) cells have DISAGREEING duplicate fte/industry; keeping highest-FTE row.", freq, disagree))
  setorder(f, cvr, tidx, -fte)                          # deterministic tiebreak, not raw row order
  f <- unique(f, by = c("cvr", "tidx"))
  f[, industry_grp := substr(industry_code, 1L, IND_DIGITS)]
  f[]
}

# One matched-control (stacked) event study per window, printed as a tab. Deshpande-Li-style structure:
# i(event_time, treated) with FE = cvr + tidx^industry_grp + treated + event_time (NO stack x event_time or
# stack x cvr FE -- that would change the estimator). `firm` has (cvr, tidx, fte, industry_grp); `matchtab`
# has (stack_id, cvr, entity, event_tidx) in the SAME time unit (quarters or months).
estudy_section <- function(firm, matchtab, windows, unit) {
  for (H in windows) {
    reg <- firm[matchtab, on = "cvr", allow.cartesian = TRUE, nomatch = NULL]
    reg[, event_time := tidx - event_tidx]
    # keep periods in the window with strictly positive FTE AND a present industry_grp: industry enters the
    # FE, so a missing value would be dropped by feols later and silently destroy the balance.
    reg <- reg[event_time %between% c(-H, H) & !is.na(fte) & fte > MIN_FTE &
                 !is.na(industry_grp) & industry_grp != ""]
    # balanced firm: exactly 2H+1 rows AND 2H+1 distinct periods spanning -H..H (catches gaps AND duplicates)
    reg[, `:=`(n_row = .N, n_per = uniqueN(event_time), tmin = min(event_time), tmax = max(event_time)),
        by = .(stack_id, cvr)]
    reg <- reg[n_row == 2L * H + 1L & n_per == 2L * H + 1L & tmin == -H & tmax == H]
    reg[, `:=`(has_w = "winner" %in% entity, has_n = "non-winner" %in% entity), by = stack_id]
    reg <- reg[has_w == TRUE & has_n == TRUE]
    n_stk <- uniqueN(reg$stack_id)

    cat(sprintf("\n\n## +/-%d %s\n\n", H, unit))
    if (n_stk < MIN_STACKS) { cat(sprintf("*Only %d stacks (< %d) at this window - skipped.*\n\n", n_stk, MIN_STACKS)); next }

    # balance audit: every retained firm is exactly balanced on -H..H (belt-and-braces on the filter above)
    aud <- reg[, .(n = .N, u = uniqueN(event_time), lo = min(event_time), hi = max(event_time)), by = .(stack_id, cvr)]
    stopifnot(all(aud$n == 2L * H + 1L), all(aud$u == 2L * H + 1L), all(aud$lo == -H), all(aud$hi == H))

    reg[, treated := as.integer(entity == "winner")]
    reg[, weight  := 1 / uniqueN(cvr), by = .(stack_id, entity)]     # each stack-arm sums to 1
    reg[, event_time := relevel(factor(event_time), ref = "-1")]
    n_w <- reg[treated == 1, uniqueN(cvr)]; n_n <- reg[treated == 0, uniqueN(cvr)]
    cat(sprintf("**%d stacks** | %d winners vs %d non-winners | %d firm-%s.\n\n", n_stk, n_w, n_n, nrow(reg), unit))
    brk <- seq(-H, H, by = max(1L, H %/% 4L))

    # Two-way clustering (tender + firm): allows arbitrary correlation across co-bidders within a tender AND
    # across repeated appearances of the same firm. (stack-only, ~stack_id, is the closest single-way D-L
    # analogue -- swap the `cluster =` line for that as a robustness check.)
    # fixef.rm = "none": keep the full balanced panel -- otherwise fixest drops singleton tidx^industry_grp
    # cells (one obs in a calendar-period x industry cell), which would silently unbalance the sample.
    # i(event_time, treated) gives one interaction per k only if treated is numeric 0/1; a factor gets one
    # per level, collinear with the event_time FE, and fixest may drop the wrong ones.
    stopifnot(is.numeric(reg$treated), all(reg$treated %in% c(0, 1)))
    est <- feols(c(fte, log(fte)) ~ i(event_time, treated, ref = "-1") |
                  treated + event_time, 
                 data = reg, 
                 cluster = ~cvr, weights = ~weight,
                 fixef.rm = "none")
    stopifnot(nobs(est[[1]]) == nrow(reg), nobs(est[[2]]) == nrow(reg))   # fixest kept every observation
    # Persist the fitted models and the estimation panel. Quarterly keeps the filenames the old .R wrote
    # (estudy_wnw_h8.rds / _h4.rds) so anything already reading them keeps working; monthly uses _m.
    if (SAVE_RDS) {
      .f <- file.path(emp_dir, sprintf("estudy_wnw_%s%d.rds",
                                       if (identical(unit, "quarters")) "h" else "m", H))
      saveRDS(list(models = est, panel = reg, window = H, unit = unit,
                   min_fte = MIN_FTE, ind_digits = IND_DIGITS, run_at = Sys.time()), .f)
    }
    # `reg` is local to estudy_section(), so it disappears when the chunk finishes. Stash each window's
    # estimation panel (and its models) in the global env so they are reachable after running chunks
    # interactively: es_panels$h8, es_panels$h4, es_panels$m12, es_panels$m6.
    .nm <- sprintf("%s%d", if (identical(unit, "quarters")) "h" else "m", H)
    if (!exists("es_panels", envir = .GlobalEnv)) assign("es_panels", list(), envir = .GlobalEnv)
    if (!exists("es_models", envir = .GlobalEnv)) assign("es_models", list(), envir = .GlobalEnv)
    .p <- get("es_panels", envir = .GlobalEnv); .p[[.nm]] <- copy(reg)
    .m <- get("es_models", envir = .GlobalEnv); .m[[.nm]] <- est
    assign("es_panels", .p, envir = .GlobalEnv); assign("es_models", .m, envir = .GlobalEnv)

    # graph 1: coefficient event study, FTE level + log FTE, 95% CI
    co <- data.table()
    for (m in c(1L, 2L)) {
      ct <- as.data.table(coeftable(est[[m]]), keep.rownames = "term")[grepl("event_time", term)]
      ct[, event_time := as.integer(gsub(".*event_time::(-?[0-9]+).*", "\\1", term))]
      ct <- rbind(ct[, .(event_time, est = Estimate, se = `Std. Error`)], data.table(event_time = -1L, est = 0, se = 0))
      ct[, outcome := c("FTE (level)", "log FTE")[m]]
      co <- rbind(co, ct)
    }
    co[, `:=`(lo = est - 1.96 * se, hi = est + 1.96 * se)]; setorder(co, outcome, event_time)
    print(ggplot(co, aes(event_time, est)) +
      geom_hline(yintercept = 0, colour = "grey50", linewidth = 0.3) +
      geom_vline(xintercept = -0.5, linetype = "dashed", colour = "grey60") +
      geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#2c7fb8", alpha = 0.15) +
      geom_line(colour = "#2c7fb8", linewidth = 0.5) + geom_point(colour = "#2c7fb8", size = 1.8) +
      facet_wrap(~ outcome, scales = "free_y") + scale_x_continuous(breaks = brk) +
      labs(title = sprintf("Employment response: winner - non-winner co-bidders (+/-%d %s)", H, unit),
           subtitle = sprintf("Matched controls | %d stacks, %d winners vs %d non-winners", n_stk, n_w, n_n),
           x = sprintf("%s relative to award (t = 0 = award %s; t = -1 omitted)", tools::toTitleCase(unit), sub("s$", "", unit)),
           y = "Effect (winner - non-winner)", caption = "Shaded = 95% CI, two-way clustered by tender (stack) + firm.") +
      theme_light(base_size = 11) + theme(plot.title = element_text(face = "bold")))
    cat("\n\n")

    # graph 2: weighted mean FTE levels with OLS pre/post trends, labelled slope [95% CI]
    d <- reg[, .(m_fte = weighted.mean(fte, w = weight)), by = .(event_time, entity)]
    d[, event_time := as.integer(as.character(event_time))]
    d[, period := ifelse(event_time < 0, "pre", "post")]
    lab <- d[, { mm <- lm(m_fte ~ event_time); ci <- confint(mm)["event_time", ]; xx <- mean(event_time)
      .(x = xx, y = predict(mm, data.frame(event_time = xx)),
        txt = sprintf("slope %.2f\n[%.2f, %.2f]", coef(mm)[["event_time"]], ci[[1]], ci[[2]])) }, by = .(entity, period)]
    lab[, ny := fifelse((entity == "winner") == (period == "post"), 26, -26)]
    print(ggplot(d, aes(event_time, m_fte, colour = entity)) +
      geom_point() + geom_line(aes(group = entity), alpha = 0.35) +
      geom_smooth(aes(group = interaction(entity, period)), method = "lm", se = FALSE, linewidth = 0.9) +
      geom_vline(xintercept = -0.5, linetype = "dashed", colour = "grey60") +
      geom_label(data = lab, aes(x, y + ny, label = txt), size = 2.9, show.legend = FALSE) +
      scale_x_continuous(breaks = brk) +
      labs(title = sprintf("Weighted mean FTE with OLS pre/post trends (+/-%d %s)", H, unit),
           x = sprintf("%s relative to award", tools::toTitleCase(unit)), y = "Weighted mean FTE", colour = NULL) +
      theme_minimal(base_size = 11))
    cat("\n\n")
  }
}
```

**Balance restriction:** a firm is retained only if it has strictly positive FTE *and* a non-missing industry
in **every one of the 2H+1 event periods** around its stack's award (`t = 0` = award period, `t = -1`
omitted). Firms with any gap, missing FTE, or missing industry in the window are dropped.

```{r prep}
# --- A. Matched winner/non-winner set from the delivered combined ------------------------------------
cmb <- as.data.table(read_clean(file.path(dirs$clean_data, "tender_data_2006_2026")))
# require valid tender_id AND lot_id so missing ids can't merge distinct lots into one stack.
wn  <- cmb[data_source == "TED" & entity %chin% c("winner", "non-winner") &
             !is.na(cvr_final) & cvr_final != "" &
             !is.na(tender_id) & tender_id != "" & !is.na(lot_id) & lot_id != ""]
wn[, cvr := sprintf("%08d", suppressWarnings(as.integer(gsub("[^0-9]", "", cvr_final))))]
wn <- wn[grepl("^[0-9]{8}$", cvr)]
wn[, award_date := as.Date(award_date)]
# the event date comes from the WINNER, so only winners need a dated award; non-winners are kept regardless
# (they inherit the stack's winner date) -- this keeps more controls.
wn <- wn[entity == "non-winner" | !is.na(award_date)]
wn[, is_dual := ("winner" %in% entity) & ("non-winner" %in% entity), by = .(tender_id, lot_id, cvr)]
wn <- wn[!(entity == "non-winner" & is_dual == TRUE)]                       # a firm can't be its own control
wn[, has_both := ("winner" %in% entity) & ("non-winner" %in% entity), by = .(tender_id, lot_id)]
wn <- wn[has_both == TRUE]
wn[, stack_id := .GRP, by = .(tender_id, lot_id)]
wn[, wdate := min(award_date[entity == "winner"]), by = stack_id]           # winners are all dated -> non-NA
match_q <- unique(wn[, .(stack_id, cvr, entity, event_tidx = year(wdate) * 4L  + quarter(wdate))])

# --- B. Carry the lot's identifiers onto the panel ---------------------------------------------------
# stack_id is a .GRP integer: it names a lot only within this knit, so a reader of estudy_wnw_h8.rds
# cannot tell which procurement a stack is. lot_key is built to the same recipe as the matching
# pipeline's EVENT_META_COLS (0_matching_utils.R) and joins straight onto event_lot_key.
# Built per STACK and merged, not selected alongside cvr in the unique() above: ted_notice_id is only
# ASSUMED constant within a lot, and were it ever to vary, carrying it through that unique() would
# duplicate firm rows and silently unbalance the panel.
if (!"ted_notice_id" %in% names(wn)) wn[, ted_notice_id := NA_character_]
wn[, ted_notice_id := as.character(ted_notice_id)]   # else all-NA groups type-clash with the rest
stack_key <- unique(wn[, .(stack_id, tender_id, lot_id)])                  # 1:1 with stack_id by .GRP
stack_key[, lot_key := paste("TED", tender_id, lot_id, sep = "|")]         # wn is filtered to TED
stack_key <- merge(stack_key,
                   wn[, .(ted_notice_id = { v <- sort(unique(ted_notice_id[!is.na(ted_notice_id)]))
                                            if (length(v)) v[1L] else NA_character_ }), by = stack_id],
                   by = "stack_id")
.n_mq <- nrow(match_q)
match_q <- merge(match_q, stack_key, by = "stack_id")
stopifnot(nrow(stack_key) == uniqueN(wn$stack_id), nrow(match_q) == .n_mq)  # many-to-one, no fan-out

# --- C. Firm employment panel (quarterly-spliced), with duplicate audit ------------------------------
emp <- as.data.table(readRDS(file.path(emp_dir, "firm_employment_panel_all.rds")))
nonwin_out <- file.path(emp_dir, "cvr_employment_history_nonwinner.rds")
if (file.exists(nonwin_out))
  emp <- rbind(emp, as.data.table(readRDS(nonwin_out)), use.names = TRUE, fill = TRUE)
emp[, cvr := as.character(cvr)]
firm_q <- prep_firm("quarterly_spliced", 4L,  "quarter")
```

# Compare winners and non-winners
```{r compare-wnw-data}

# Convert capital up front
firm_q[, capital_amount_dkk := fifelse(capital_currency == "EUR", capital_amount * 7.46038, capital_amount)]
firm_q[, capital_amount_dkk := capital_amount_dkk / 1e6]  # millions of DKK

# Recode legal form to simplify counts
firm_q[, legal_form_short := fifelse(legal_form_short %in% c("A/S", "APS", "ENK"), legal_form_short, "Other")]

# Simplify winner and non-winner panel
wnw_simple <- wn[, .(stack_id, tender_id, lot_id,
                     entity, cvr_final, 
       wdate, competition_publication_date,
       qidx_wdate = year(wdate) * 4L + quarter(wdate),
       qidx_cdate = year(competition_publication_date) * 4L + quarter(competition_publication_date))]

# Lag indices off the win date: qidx = year*4 + quarter, so 1 year back = 4 quarters, 2 years = 8
wnw_simple[, qidx_wdate_l1 := qidx_wdate - 4L]
wnw_simple[, qidx_wdate_l2 := qidx_wdate - 8L]

# Join on employment at win date and publication of competition notice
# at the win date
wnw_simple[firm_q, on = .(cvr_final = cvr, qidx_wdate = tidx),
           `:=`(fte_at_win           = i.fte,
                industry_code_at_win = i.industry_code,
                industry_grp_at_win  = i.industry_grp,
                capital_at_win = i.capital_amount_dkk,
                legal_form_at_win = i.legal_form_short)]

# at the competition-notice date
wnw_simple[firm_q, on = .(cvr_final = cvr, qidx_cdate = tidx),
           `:=`(fte_at_comp           = i.fte,
                industry_code_at_comp = i.industry_code,
                industry_grp_at_comp  = i.industry_grp,
                capital_at_comp = i.capital_amount_dkk,
                legal_form_at_comp = i.legal_form_short)]

# 1 year before the win date
wnw_simple[firm_q, on = .(cvr_final = cvr, qidx_wdate_l1 = tidx),
           `:=`(fte_l1y           = i.fte,
                industry_code_l1y = i.industry_code,
                industry_grp_l1y  = i.industry_grp,
                capital_l1y = i.capital_amount_dkk,
                legal_form_l1y = i.legal_form_short)]

# 2 years before the win date
wnw_simple[firm_q, on = .(cvr_final = cvr, qidx_wdate_l2 = tidx),
           `:=`(fte_l2y           = i.fte,
                industry_code_l2y = i.industry_code,
                industry_grp_l2y  = i.industry_grp,
                capital_l2y = i.capital_amount_dkk,
                legal_form_l2y = i.legal_form_short)]

# Join one registration date
wnw_simple[firm_q, on = .(cvr_final = cvr, qidx_wdate = tidx),
           `:=`(registration_date = i.registration_date)]

# Create age
wnw_simple[, age_at_win := as.integer(wdate - registration_date) / 365.25]
wnw_simple[, age_at_comp := as.integer(competition_publication_date - registration_date) / 365.25]
wnw_simple[, age_l1y := age_at_win - 1]
wnw_simple[, age_l2y := age_at_win - 2]

# Treated and non-treated weights for each variable
vars <- c("fte_at_win", "fte_at_comp", "fte_l1y", "fte_l2y",
          "capital_at_win", "capital_at_comp", "capital_l1y", "capital_l2y",
          "age_at_win", "age_at_comp")

wnw_simple[, paste0("w_", vars) := lapply(.SD, function(x) {
    n <- sum(!is.na(x))
    if (n == 0L) rep(NA_real_, length(x)) else as.numeric(!is.na(x)) / n
  }), by = .(stack_id, entity), .SDcols = vars]


# Set order
setorder(wnw_simple, stack_id, -entity, cvr_final)

```

```{r compare-wnw-tables}

# Weighted mean / SD of one variable, using that variable's own weight column
wstats <- function(x, w) {
  sw <- sum(w, na.rm = TRUE)                      
  mu <- sum(x * w, na.rm = TRUE) / sw
  list(n = sum(!is.na(x)), mean = mu,
       sd = sqrt(sum(w * (x - mu)^2, na.rm = TRUE) / sw))
}

# One row per variable x entity
balance <- rbindlist(lapply(vars, function(v)
  wnw_simple[, c(list(variable = v), wstats(get(v), get(paste0("w_", v)))), by = entity]))

# Winners and non-winners side by side, plus the normalised difference
balance[, entity := fifelse(entity == "winner", "win", "nonwin")]
tab <- dcast(balance, variable ~ entity, value.var = c("n", "mean", "sd"))
tab[, norm_diff := (mean_win - mean_nonwin) / sqrt((sd_win^2 + sd_nonwin^2) / 2)]

knitr::kable(tab, digits = 2,
             caption = "Weighted balance: winners vs non-winning bidders on the same lot")

```

```{r compare-wnw-legal-form, fig.width = 10, fig.height = 7, fig.align='center'}
lf_vars <- c(at_win = "legal_form_at_win", at_comp = "legal_form_at_comp",
             l1y    = "legal_form_l1y",    l2y     = "legal_form_l2y")

# Weights that respect each legal-form column's own missingness (same rule as the numeric vars)
wnw_simple[, paste0("w_", lf_vars) := lapply(.SD, function(x) {
    n <- sum(!is.na(x)); if (n == 0L) rep(NA_real_, length(x)) else as.numeric(!is.na(x)) / n
  }), by = .(stack_id, entity), .SDcols = unname(lf_vars)]

# Long: one row per (firm-lot x time point), carrying the form and its matching weight
lf <- melt(wnw_simple, id.vars = c("stack_id", "entity"),
           measure.vars = list(form = unname(lf_vars), w = paste0("w_", unname(lf_vars))),
           variable.name = "when")
lf[, when := factor(when, labels = names(lf_vars))]

# Weighted share of each legal form within (time point, entity)
shares <- lf[!is.na(form), .(w = sum(w, na.rm = TRUE)), by = .(when, entity, form)]
shares[, share := w / sum(w), by = .(when, entity)]
setorder(shares, -share)
shares[, form := factor(form, levels = unique(shares[when == "at_win", form]))]

ggplot(shares, aes(x = form, y = share, fill = entity)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  facet_wrap(~ when, nrow = 2) +
  scale_fill_manual(values = c("winner" = "#2a78d6", "non-winner" = "#eb6834"), name = NULL) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = expansion(c(0, 0.05))) +
  labs(title = "Legal form of winners vs non-winning bidders on the same lot",
       subtitle = "Weighted shares; each stack-arm contributes equally",
       x = NULL, y = "Share of firms") +
  theme_light(base_size = 11) +
  theme(plot.title = element_text(face = "bold"), legend.position = "top",
        panel.grid.major.x = element_blank(), panel.grid.minor = element_blank())
```

# Quarterly event studies {.tabset}

```{r quarterly, results='asis', fig.width=11, fig.height=5}
estudy_section(firm_q, match_q, QUARTER_WINDOWS, "quarters")
```

# What predicts winning?
This section tries to use the winner and non-winner panel to understand the predictors between winning and non-winning.

```{r basics}
# Filter to pre-award, including award
win_pred_data <- lf_es[event_time <= 0, ]

# Code a win indicator
win_pred_data[, win := as.integer(entity == "winner" & event_time == 0)]

# Order 
setorder(win_pred_data, stack_id, -entity, cvr, event_time)

# Create FTE/capital growth from 1 year/2 year ago
win_pred_data[, `:=`(
  fte_growth_21 = shift(fte, n = 4, type = "lag") / shift(fte, n = 8, type = "lag"),
  fte_growth_10 = fte / shift(fte, n = 4, type = "lag"),
  k_growth_21 = shift(capital_amount_dkk, n = 4, type = "lag") / shift(capital_amount_dkk, n = 8, type = "lag"),
  k_growth_10 = capital_amount_dkk / shift(capital_amount_dkk, n = 4, type = "lag")
), by = .(stack_id, entity, cvr)]

# Run regression
feols(win ~ fte_growth_21 + fte_growth_10 + k_growth_21 + k_growth_10 | stack_id, 
      data = win_pred_data[event_time == 0, ],
      cluster = ~stack_id + cvr)

```

# What predicts bidding?
This section tries to use the winner and non-winner panel to understand the predictors between bidding and non-bidding. Here I define a non-bidder as a firm who is the same industry set as the known bidders and with positive employment, over the whole pre-period.

```{r join-non-bid}

# Horizon
H <- 8

# Filter firm employment a bit more so things are faster
bidder_cvrs <- unique(wnw_simple$cvr_final)
winning_periods <- sort(unique(lf_es$event_tidx))
min_period <- min(winning_periods) - H
max_period <- max(winning_periods) + H

# Filter
firm_q_bidders <- firm_q[cvr %in% bidder_cvrs, ]
firm_q_bidders <- firm_q_bidders[tidx %in% min_period:max_period & !is.na(industry_grp) & industry_grp != "" & fte > 0, ]
firm_q_sample_frame <- firm_q[tidx %in% min_period:max_period & !is.na(industry_grp) & industry_grp != "" & fte > 0, ]

# Make lags of FTE and employment
firm_q_sample_frame[, k_l2y := shift(capital_amount_dkk, n = 8, type = "lag"), by = cvr]
firm_q_sample_frame[, fte_l2y := shift(fte, n = 8, type = "lag"), by = cvr]
firm_q_sample_frame[, k_l1y := shift(capital_amount_dkk, n = 4, type = "lag"), by = cvr]
firm_q_sample_frame[, fte_l1y := shift(fte, n = 4, type = "lag"), by = cvr]

# Filter out observations that don't have the lagged amounts available
firm_q_sample_frame <- firm_q_sample_frame[!is.na(k_l2y) & !is.na(k_l1y) & !is.na(fte_l2y) & !is.na(fte_l1y), ]
  
# Create filtering meta data at event level.
contract_meta <- lapply(unique(wnw_simple$tender_id), function(sid) {
  
  # Bidder CVRs (includes winners and non-winng bidders)
  bidder_cvrs <- wnw_simple[entity %in% c("winner", "non-winner") & tender_id == sid, unique(cvr_final)]
  
  # Get dates
  award_qidx <- unique(wnw_simple[tender_id == sid & entity == "winner", qidx_wdate])
  comp_qidx <- unique(wnw_simple[tender_id == sid & entity == "winner", qidx_cdate])
  
  # Get industry groups observed in periods before publication of competition notice
  pre_comp_industries <- unique(firm_q_bidders[(tidx <= comp_qidx & tidx >= comp_qidx - H) &
                                                 cvr %in% bidder_cvrs, 
                                               industry_grp])
  
  # Report metadata
  list(stack_id = sid, bidder_cvrs = bidder_cvrs,
       award_tidx = award_qidx, comp_tidx = comp_qidx, industry_groups = pre_comp_industries)
  
}) 

# Use contract meta-data to find plausible non-bidders (same industry groups as the bidders)
nonbidder_dt <- lapply(contract_meta, function(contract){
  
  # Extract contract data
  bidder_industry_groups <- contract$industry_groups
  comp_qidx <- contract$comp_tidx
  
  # Get possible bidders
  possible_bidders_emp <- firm_q_sample_frame[(tidx <= comp_qidx & tidx >= comp_qidx - H), ]
  possible_bidders_emp[, possible_bidder := any(industry_grp %chin% bidder_industry_groups), by = cvr]
  possible_bidders_emp <- possible_bidders_emp[possible_bidder == TRUE, ]
  possible_bidders_emp <- possible_bidders_emp[tidx == comp_qidx, ]
  possible_bidders_emp$stack_id <- contract$stack_id
  possible_bidders_emp[, bid := 0]
  
  # Get equivalent bidders info
  bidders_emp <- firm_q_sample_frame[cvr %chin% contract$bidder_cvrs, ]
  bidders_emp <- bidders_emp[tidx == comp_qidx, ]
  bidders_emp[, bid := 1]
  bidders_emp$stack_id <- contract$stack_id
  
  # Bind
  out <- rbindlist(list(bidders_emp, possible_bidders_emp), fill = TRUE)
  
  # Return
  return(out)
  
})

nonbidder_dt <- rbindlist(nonbidder_dt)
setorder(nonbidder_dt, stack_id, -bid, cvr)

# Create firm age as another variable
nonbidder_dt[, by_tidx := year(registration_date)*4 + quarter(registration_date)] # Firm birth year as a quarter
nonbidder_dt[, age_q := tidx - by_tidx]
```


```{r run-models}
library(fixest)

# Basic levels
m1 <- feols(bid ~ log(fte) + log(fte_l2y) + log(fte_l1y) + legal_form_short | stack_id,
           family = binomial(), data = nonbidder_dt, cluster = ~cvr)
summary(m1)

# FTE gaps
nonbidder_dt[, fte_gap_2y := (log(fte_l1y) - log(fte_l2y))/10] # rescale
nonbidder_dt[, fte_gap_1y := (log(fte) - log(fte_l1y))/10] # rescale
m2 <- feols(bid ~ fte_gap_2y + fte_gap_1y + legal_form_short | stack_id,
           data = nonbidder_dt, cluster = ~cvr)
summary(m2)

# All csw() 
m3 <- feols(bid ~ csw(legal_form_short, log(fte), log(fte_l2y), log(fte_l1y), age_q)  | stack_id, 
            data = nonbidder_dt, cluster = ~cvr)
summary(m3)

## CLogit
library(survival)

# ApS as reference, so the A/S coefficient reads in the direction your summary stats suggest
nonbidder_dt[, legal_form_short := relevel(factor(legal_form_short), ref = "APS")]
nonbidder_dt[, fte_x := fte / 10]
c1 <- clogit(bid ~ fte_x + fte_gap_1y + fte_gap_2y + legal_form_short + strata(stack_id),
             data = nonbidder_dt, cluster = cvr, method = "efron")

summary(c1)

# Growth
nonbidder_dt[, fte_growth_1y := log(fte / fte_l1y)]
nonbidder_dt[, fte_growth_2y := log(fte_l1y / fte_l2y)]

c2 <- clogit(bid ~ fte_x + fte_growth_1y + fte_growth_2y + legal_form_short + strata(stack_id),
             data = nonbidder_dt, cluster = cvr, method = "efron")

summary(c2)

```

# Legal forms in the data
Each firm in Denmark registers with the business authority under a specific legal form. There are `r emp[legal_form_short != "" & !is.na(legal_form_short), uniqueN(legal_form_short)]` different firm types. Most firms are ENK (sole proprietorship), ApS (a SME) or A/S (a larger firm). In our employment data, most currently active firms are ApS while most currently active TENDER WINNERS are A/S. 

```{r bidding-sum-stats, fig.align='center'}

# Just use annual panel for this:
ann_emp <- emp[!is.na(legal_form_short) & 
                 legal_form_short != "" & 
                 legal_form_short != "NA" & 
                 frequency == "annual_spliced", ]

# 1 What is the most common form among ALL CURRENTLY ACTIVE firms?
now <- year(Sys.Date())
common_forms_active_firms <- ann_emp[year == now & exists_during_period == TRUE & fte > 0, .(n = .N), by = legal_form_short][order(-n)][, `:=`(p = round(n / sum(n), 4), cp = round(cumsum(n) / sum(n), 4))][, head(.SD, 6)]
knitr::kable(common_forms_active_firms, 
      caption = "Top 6 Legal Forms Among ALL CURRENTLY Active Firms")

# 2 What is the most common form among ALL TENDER WINNERS?
winner_cvr_set <- cmb[entity == "winner", unique(cvr_final)]
common_forms_winning_firms <- ann_emp[year == now & exists_during_period == TRUE & fte > 0 & cvr %chin% winner_cvr_set, .(n = .N), by = legal_form_short][order(-n)][, `:=`(p = round(n / sum(n), 4), cp = round(cumsum(n) / sum(n), 4))][, head(.SD, 6)]
knitr::kable(common_forms_winning_firms, 
      caption = "Top 6 Legal Forms Among ALL CURRENTLY Active WINNING Firms")

# 3 How many firms overall ever change legal form?
n_lforms <- ann_emp[, .(n_forms = uniqueN(legal_form_short),
                        forms_used = paste(sort(unique(legal_form_short)), 
                                           collapse = "; ")), by = cvr]

# Counts of number of forms over firm's employment history
n_forms_used <- n_lforms[, .(count = .N), by = n_forms]

# Top 3 forms per number of forms used in employment history
forms_used_dist <- n_lforms[, .(count = .N), by = .(n_forms, forms_used)][order(n_forms, -count)]
forms_used_top3 <- forms_used_dist[, head(.SD, 5), by = n_forms]
knitr::kable(forms_used_top3, caption = "Common forms used")

# Common transitions
setorder(ann_emp, cvr, year)
ann_emp[, max_year := max(year), by = cvr]
ann_emp[, firm_age_yr := year - year(registration_date)]
ann_emp[, legal_form_short_f1 := shift(legal_form_short, n = 1, type = "lead"), by = cvr]
ann_emp[, trans_hit := legal_form_short_f1 != legal_form_short]
ann_emp[trans_hit %in% TRUE, 
        form_trans := paste0(legal_form_short, "->", legal_form_short_f1)]
ann_emp[year == max_year, form_trans := NA, by = cvr]
ann_emp[, n_trans_per_firm := sum(trans_hit, na.rm = T), by = cvr]

# Common transitions
common_trans <- ann_emp[trans_hit == TRUE, .(n = .N), by = form_trans][order(-n)][, `:=`(p = round(n / sum(n), 4), cp = round(cumsum(n) / sum(n), 4))][, head(.SD, 6)]
knitr::kable(common_trans, 
             caption = "Legal Form Changes in Annual Employment Data")
```


## Does winning correlate with ApS->A/S transitions?

```{r estudy-legal-form, fig.width = 9, fig.height = 4.5}
# Horizon
H <- 8

# Define transitions
setorder(firm_q, cvr, tidx)
firm_q[, legal_form_short_f1 := shift(legal_form_short, 1, type = "lead"), by = cvr]
firm_q[, max_tidx := max(tidx), by = cvr]
firm_q[, trans_hit := as.integer(legal_form_short != legal_form_short_f1)]
firm_q[, form_trans := paste0(legal_form_short, "->", legal_form_short_f1)]
firm_q[max_tidx == tidx, form_trans := NA]

# Winning periods
events <- cmb[entity == "winner" & direct_award %in% FALSE, .(cvr_final, award_date)]
setorder(events, cvr_final, award_date)
events <- distinct(events, cvr_final, award_date)
events[, award_qidx := quarter(award_date) + year(award_date) * 4]
events <- events[, head(.SD, 1), by = .(cvr_final, award_qidx)] # keep first occurrence per (cvr, event_qidx)
events <- events[!is.na(award_qidx), ]

# Filter to only necessary obs periods
obs_period <- seq(min(unique(events$award_qidx)) - H,
                  max(unique(events$award_qidx)) + H)
firm_q_obs <- firm_q[tidx %in% obs_period, ]

# Create event study panel
# one id per event -- this is your stack id
events[, ev := .I]

# expand to the full -H:H grid first
es <- events[, .(tau = -H:H),
             by = .(ev, cvr = cvr_final, award_qidx)]
es[, tidx := award_qidx + tau]

# then attach firm state (keeps every grid row, NA where unobserved)
es <- firm_q_obs[es, on = .(cvr, tidx)]

# Keep only ev's where every period has a legal form
es[, all_forms_present := all(!is.na(legal_form_short)), by = .(cvr, ev)]
es <- es[all_forms_present == TRUE, ]
es <- es[!is.na(trans_hit), ] # Remove NA transition hits (occur at the end of the sample)
es[, all_periods := as.logical(.N == 2 * H + 1), by = ev]
es <- es[all_periods == TRUE, ]

# Remove singletons
es[, cvr_single := .N == 1, by = cvr]
es[, tidx_single := .N == 1, by = tidx]
es <- es[cvr_single == FALSE & tidx_single == FALSE, ]
es[, all_periods := as.logical(.N == 2 * H + 1), by = ev]
es <- es[all_periods == TRUE, ]

# Run TWFE event study
simple_lform_transition_mod <- feols(trans_hit ~ i(tau, ref = -1) | cvr + tidx, data = es, cluster = ~cvr)



```
