---
title: "Employment Data Quality"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

# Clean up environment
rm(list = ls())

# Packages
library(here)
library(data.table)
library(tidyverse)
library(knitr)
library(fixest)
library(lubridate)
library(kableExtra)

# Paths
report_project_dir <- local({
  d <- normalizePath(getwd(), mustWork = TRUE)
  while (!file.exists(file.path(d, "cvr-cleaning.Rproj")) && dirname(d) != d) {
    d <- dirname(d)
  }
  d
})
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)

source(file.path(report_project_dir, "config.R"))
clean_data_dir <- dirs$clean_data
key_dir <- dirs$cvr_key

valid_cvrs <- function(x) {
  x <- trimws(as.character(x))
  x <- gsub("[^0-9]", "", x)
  x <- x[grepl("^[0-9]{1,8}$", x)]
  unique(sprintf("%08d", as.integer(x)))
}

# 1 Load data
## 1.1 Firm data
firm_data_raw <- fread(file.path(clean_data_dir, "cvr_employment_history_virk.csv"))
setDT(firm_data_raw)

firm_data <- copy(firm_data_raw)
setDT(firm_data)
firm_data[, firm_by := year(lifecycle_start)]
firm_data[, firm_dy := year(lifecycle_end)]
firm_data[, firm_age := as.integer(floor(as.numeric(period_end - lifecycle_start) / 365.25))]
firm_data_ls <- firm_data %>% 
  split(.$frequency)

## 1.2 Tender data
data_ot <- readRDS(file.path(clean_data_dir, "clean_winner_data_ot_name_matched.rds")) %>% 
  mutate(data_source = "OpenTender")
data_kfst <- readRDS(file.path(clean_data_dir, "clean_winner_data_kfst_name_matched.rds")) %>% 
  mutate(data_source = "KFST")
data_ot_buyers <- readRDS(file.path(clean_data_dir, "clean_buyer_data_ot_name_matched.rds")) %>% 
  mutate(data_source = "OpenTender")
data_kfst_buyers <- readRDS(file.path(clean_data_dir, "clean_buyer_data_kfst_name_matched.rds")) %>% 
  mutate(data_source = "KFST")
data_tender <- rbindlist(list(data_ot, data_kfst), fill = TRUE, ignore.attr = TRUE) %>% 
  select(data_source, tender_id, lot_id, award_date, winner_cvr_final, tender_amount, lot_amount, contract_type, cpv_category, cpv_sector, flag_awarded)
unique_cvrs <- unique(data_tender$winner_cvr_final)


## 1.3 CVR key (includes firm registration and death dates)
virk_data <- fread(file.path(key_dir, "cvr_names_virk_20260710_182823.csv"))
virk_data[, tender_firm := FALSE]
virk_data[cvr %in% unique_cvrs, tender_firm := TRUE]
```

# Introduction
The `virk.dk` API contains has employment data on a monthly, quarterly, and annual frequency. I pulled these data for every firm in the tender datasets. This note describes the quality of these data.

# Availability/coverage
```{r availability, fig.align='center'}

# How many CVRs actually appear in the employment data?

emp_cvrs <- valid_cvrs(firm_data_raw$cvr)

coverage_cvrs <- rbindlist(list(
  data.table(
    data_source = "OpenTender",
    firm_role = "Winner",
    cvr = valid_cvrs(data_ot$winner_cvr_final)
  ),
  data.table(
    data_source = "OpenTender",
    firm_role = "Buyer",
    cvr = valid_cvrs(data_ot_buyers$buyer_cvr_final)
  ),
  data.table(
    data_source = "KFST",
    firm_role = "Winner",
    cvr = valid_cvrs(data_kfst$winner_cvr_final)
  ),
  data.table(
    data_source = "KFST",
    firm_role = "Buyer",
    cvr = valid_cvrs(data_kfst_buyers$buyer_cvr_final)
  )
))

coverage_table <- coverage_cvrs[, .(
  n_cvrs = uniqueN(cvr),
  n_in_employment_data = uniqueN(cvr[cvr %in% emp_cvrs]),
  share_in_employment_data = round(uniqueN(cvr[cvr %in% emp_cvrs]) / uniqueN(cvr), 5)
), by = .(data_source, firm_role)]

kable(
  coverage_table,
  caption = "Share of valid firm CVRs in the tender data that appear in the pulled employment data"
)

# How many rows have non-missing data
missingness_table <- firm_data_raw[, .(
  # Counts
  n = .N, 
  n_nonmissing_fte = sum(!is.na(fte)),
  n_nonmissing_emp = sum(!is.na(employees)),
  n_nonmissing_emp_with_owner = sum(!is.na(employees_including_owners)),
  
  # Shares
  share_nonmissing_fte = round(sum(!is.na(fte)) / .N, 5),
  share_nonmissing_emp = round(sum(!is.na(employees)) / .N, 5),
  share_nonmissing_emp_with_owner = round(sum(!is.na(employees_including_owners)) / .N, 5)


), by = frequency]

kable(missingness_table,
      caption = "Employment data availability for firms that appear in the employment data")

```

# Balance
Below is a balance table of age for firms in our tender dataset compared to those not in the tender dataset. Firms appearing in our tender dataset tend are older than firms not in the tender dataset. This could be because firms who win tenders are usually more productive/cost competitive than firms who do not win them (especially if price is heavily weighted in deciding which firm to award a tender to).

```{r age-balance}

# Calculate firm age
anchor_date <- lubridate::floor_date(Sys.Date(), unit = "year") # Beginning of this year
virk_data[!is.na(lifecycle_end), firm_age := lifecycle_end - registration_date] # If firm ended, calculate total age
virk_data[is.na(lifecycle_end), firm_age := anchor_date - registration_date] # Otherwise, calculate from today's date
virk_data[, firm_age_yrs := as.numeric(firm_age) / 365.25]
virk_data[, firm_dissolved := fifelse(is.na(lifecycle_end), "Still registered", "Dissolved")]
age_regs <- feols(firm_age_yrs ~ i(tender_firm) - 1, fsplit = ~firm_dissolved, data = virk_data)

# Make table
age_table <- coeftable(age_regs) %>% 
  mutate(
    group = ifelse(str_detect(coefficient, "TRUE"), "Won tender", "No tender")
  ) %>% 
  select(sample, group, Estimate) %>% 
  pivot_wider(id_cols = group, names_from = sample, values_from = Estimate)

kable(
  age_table,
  caption = "Firm Age by Tender Winning Status",
  escape = FALSE,
  align = "lcc"
) %>%
  kable_styling(full_width = FALSE)
```

# Employment by firm age
```{r emp-by-firm-age, fig.align='center'}

# Regression data
reg_data <- firm_data[
  frequency == "annual" &
    exists_during_period == TRUE &
    !is.na(fte) &
    fte > 0 &
    !is.na(firm_age) &
    firm_age >= 0 &
    firm_age <= 100
]

regression_sample_table <- reg_data[, .(
  n = .N,
  n_firms = uniqueN(cvr),
  min_firm_age = min(firm_age),
  max_firm_age = max(firm_age)
)]

kable(
  regression_sample_table,
  caption = "Annual employment observations used in the firm-age regression"
)

# Regression
fte_reg <- feols(log(fte) ~ i(firm_age) - 1 | cvr, 
                 data = reg_data, 
                 cluster = ~cvr)
iplot(fte_reg)
```

# Event study around tender award

```{r es-plot-helper, include=FALSE}
# Helper: plot a pair of fixest models as one event-study figure
# (models[[1]] = FTE, models[[2]] = employees).
plot_es <- function(models, main, xlab = "Quarters relative to contract win") {
  iplot(list(models[[1]], models[[2]]),
        main   = main,
        xlab   = xlab,
        col    = c("steelblue", "darkred"),
        pt.pch = c(16, 17),
        ci.lty = c(1, 1))
  legend("bottomleft",
         legend = c("FTE", "Employees"),
         col    = c("steelblue", "darkred"),
         pch    = c(16, 17),
         lty    = c(1, 1),
         bty    = "n")
}
```

## Annual (unbalanced) {.tabset}

Event studies around the **first** tender award (employment relative to the award year). Click through the tabs for each sample. These use an **unbalanced** panel — the set of firms identifying each event-year coefficient shrinks as you move away from the award, which widens the confidence intervals at the window edges.

```{r tender-award-estudy-data, include=FALSE}

# Build universe of events
## Get unique events
setDT(data_tender)
setorder(data_tender, winner_cvr_final, data_source, award_date)
## Awarded contracts only: drop tenders that were annulled / never awarded
## (flag_awarded is a tender/lot-level flag from the processing scripts). Applied
## to the event universe here, so it propagates to every event study below
## (annual estudy_data and quarterly estudy_all_events).
valid_winner_events <- data_tender[winner_cvr_final %in% coverage_cvrs[firm_role == "Winner"]$cvr &
                                     flag_awarded == TRUE, ]
valid_winner_events <- unique(valid_winner_events, by = c("winner_cvr_final", "award_date"))

## Create event identifier (chronological: event_id == 1 is the earliest award).
## Sort by award_date within firm *before* numbering. The earlier setorder puts
## data_source ahead of award_date, so numbering off that order would not be
## chronological for firms appearing in more than one source.
setorder(valid_winner_events, winner_cvr_final, award_date)
valid_winner_events[, event_id := seq_len(.N), by = winner_cvr_final]

## Flag "isolated" events: no other award by the same firm within 4 quarters on
## either side. Used by the all-events quarterly event study so the +/-4 quarter
## window around each event is not polluted by another award.
valid_winner_events[, award_qidx := year(award_date) * 4 + quarter(award_date)]
valid_winner_events[, gap_prev := award_qidx - shift(award_qidx), by = winner_cvr_final]
valid_winner_events[, gap_next := shift(award_qidx, type = "lead") - award_qidx, by = winner_cvr_final]
valid_winner_events[, isolated_event := (is.na(gap_prev) | gap_prev > 4) &
                                        (is.na(gap_next) | gap_next > 4)]

## Coerce firm data CVR to a zero-padded 8-digit string.
## fread reads the all-numeric cvr column as integer and drops leading zeros,
## whereas the tender CVRs are 8-digit strings. Pad here so the join matches.
firm_data[, winner_cvr_final := sprintf("%08d", as.integer(cvr))]

## Join every event to each firms employment history
## Use the spliced annual series (official native <=2018, monthly-derived after),
## so post-award coverage runs to ~2026 instead of dying at 2018.
firm_data_annual <- firm_data[frequency == "annual_spliced", ]
estudy_data <- firm_data_annual[valid_winner_events, on = "winner_cvr_final", allow.cartesian = TRUE]

## Create event time
estudy_data[, award_year := year(award_date)]
estudy_data[, event_year := year - award_year]
estudy_data[, event_year_binned := fcase(
  event_year <= -5, -5L,
  event_year >= 5, 5L,
  default = as.integer(event_year)
)]

## Order more nicely
setorder(estudy_data, winner_cvr_final, event_id, year)

## Remove join failures
estudy_data <- estudy_data[!is.na(year), ]

## Balanced sample
# Get firms observed in the full -3 to 3 window around each event
# A firm-event is "balanced" if it has an observation in every year from -3 to 3
required_years <- -3:3

balanced_events <- estudy_data[
  event_year %in% required_years,
  .(n_years = uniqueN(event_year)),
  by = .(winner_cvr_final, event_id)
][n_years == length(required_years)]

# Filter estudy_data to only those firm-events
estudy_data_balanced <- estudy_data[
  balanced_events, 
  on = .(winner_cvr_final, event_id)
]
```

### All firms

Employment tends to fall after the first tender award. This is likely biased by firms dying as time passes.

```{r estudy-reg-all, fig.align='center'}

models <- feols(c(fte, employees) ~ i(event_year_binned, ref = -1) | year + winner_cvr_final, 
      cluster = ~winner_cvr_final, 
      data = estudy_data[event_id == 1 & 
                           year >= firm_by & 
                           (year <= firm_dy | is.na(lifecycle_end)), ])

# Plot
iplot(list(models[[1]], models[[2]]),
      main   = "Effect on employment",
      xlab   = "Years relative to first contract win",
      col    = c("steelblue", "darkred"),
      pt.pch = c(16, 17),
      ci.lty = c(1, 1))

legend("bottomleft",
       legend = c("FTE", "Employees"),
       col    = c("steelblue", "darkred"),
       pch    = c(16, 17),
       lty    = c(1, 1),
       bty    = "n")
```

### Current firms only

Restricting to firms currently still registered. This doesn't correct the issue.

```{r estudy-regs-alive-firms, fig.align='center'}
models <- feols(c(fte, employees) ~ i(event_year_binned, ref = -1) |
                  year + winner_cvr_final,
                cluster = ~winner_cvr_final,
                data = estudy_data[event_id == 1 &
                                     year >= firm_by &
                                     is.na(lifecycle_end), ])

plot_es(models, "Effect on employment; only current firms",
        xlab = "Years relative to first contract win")
```

```{r estudy-regs-1-tender-models, include=FALSE}
# Number of tenders won per firm, then split the first-award event study by it.
estudy_data[, total_tenders_won   := max(event_id, na.rm = TRUE), by = winner_cvr_final]
estudy_data[, total_tenders_group := fifelse(total_tenders_won > 1, "more than 1", "only 1")]

models_by_tenders <- feols(c(fte, employees) ~ i(event_year_binned, ref = -1) |
                             year + winner_cvr_final,
                           cluster = ~winner_cvr_final,
                           split  = ~total_tenders_group,
                           data   = estudy_data[event_id == 1 &
                                                  year >= firm_by &
                                                  (year <= firm_dy | is.na(lifecycle_end))])
```

### More than 1 tender

Firms that go on to win more than one tender.

```{r estudy-regs-multi-tender, fig.align='center'}
plot_es(models_by_tenders[sample = "more than 1"],
        "Effect on employment; more than 1 tender won",
        xlab = "Years relative to first contract win")
```

### Only 1 tender

Firms that win exactly one tender.

```{r estudy-regs-single-tender, fig.align='center'}
plot_es(models_by_tenders[sample = "only 1"],
        "Effect on employment; only 1 tender won",
        xlab = "Years relative to first contract win")
```

### By agreement type
Compares across framework agreements and public contracts. I hypothesise that Services behaves more like a demand shock that Works or Supplies, since it is likely more labour intensive.

```{r contract-type-estudy}

# Run models
models_by_type <- feols(c(fte, employees) ~ i(event_year_binned, ref = -1) |
                             year + winner_cvr_final,
                           cluster = ~winner_cvr_final,
                           split  = ~contract_type,
                           data   = estudy_data[event_id == 1 &
                                                  year >= firm_by &
                                                  (year <= firm_dy | is.na(lifecycle_end))])

# Framework agreement
plot_es(models_by_type[sample = "Framework agreement"],
        "Effect on employment; Framework agreement",
        xlab = "Years relative to first contract win")

# Public contract
plot_es(models_by_type[sample = "Public contract"],
        "Effect on employment; Public contracts",
        xlab = "Years relative to first contract win")


```

### By work category
Compares across tenders for 'Works', 'Services' and 'Supplies'. I hypothesise that Services behaves more like a demand shock that Works or Supplies, since it is likely more labour intensive.

```{r work-category-estudy}

# Run models
models_by_work_cat <- feols(c(fte, employees) ~ i(event_year_binned, ref = -1) |
                             year + winner_cvr_final,
                           cluster = ~winner_cvr_final,
                           split  = ~cpv_category,
                           data   = estudy_data[event_id == 1 &
                                                  year >= firm_by &
                                                  (year <= firm_dy | is.na(lifecycle_end))])

# Works
plot_es(models_by_work_cat[sample = "Works"],
        "Effect on employment; Works",
        xlab = "Years relative to first contract win")

# Services
plot_es(models_by_work_cat[sample = "Services"],
        "Effect on employment; Services",
        xlab = "Years relative to first contract win")

# Supplies
plot_es(models_by_work_cat[sample = "Supplies"],
        "Effect on employment; Supplies",
        xlab = "Years relative to first contract win")

```

## Quarterly {.tabset}

Quarterly event studies. The **First award** tab uses the first award per firm; the remaining tabs use *all isolated events* (firms with no other award within four quarters on either side), with a balanced ±4-quarter window and firm + calendar-year + season fixed effects, shown in three functional forms.

```{r qtr-estudy_data, include=FALSE}

## Join every event to each firms employment history
## Spliced quarterly series (native <=2019, monthly-derived after). NB: native
## quarterly rarely reports headcount, so quarterly_spliced FTE is continuous but
## headcount is sparse before 2020 (see report).
firm_data_qtr <- firm_data[frequency == "quarterly_spliced", ]
estudy_data <- firm_data_qtr[valid_winner_events,
                                on = "winner_cvr_final",
                                allow.cartesian = TRUE]

# Extract award year and quarter
estudy_data[, award_year    := year(award_date)]
estudy_data[, award_quarter := quarter(award_date)]

# Define event_quarter as number of quarters after event quarter
# First create a unique quarter index for both the observation and award date
estudy_data[, obs_quarter_index   := year * 4 + quarter]
estudy_data[, award_quarter_index := award_year * 4 + award_quarter]
estudy_data[, event_quarter       := obs_quarter_index - award_quarter_index]

# Bin
estudy_data[, event_quarter_binned := fcase(
  event_quarter >= 8, 8L,
  event_quarter <= -8, -8L,
  default = as.integer(event_quarter)
)]

```

```{r estudy-reg-all-events-models, include=FALSE}
# All isolated events, in the clean +/-4 quarter window, within the firm's life.
window_quarters <- -4:4
estudy_all_events <- estudy_data[
  isolated_event == TRUE &
    event_quarter %in% window_quarters &
    year >= firm_by &
    (year <= firm_dy | is.na(lifecycle_end))
]

# Unique identifier for each stacked event (firm x event)
estudy_all_events[, event_uid := paste(winner_cvr_final, event_id, sep = "_")]

# Balanced window: keep only events observed in every event-quarter from -4 to +4,
# so each coefficient is estimated off the same composition of events.
balanced_q_events <- estudy_all_events[
  , .(n_q = uniqueN(event_quarter)), by = event_uid
][n_q == length(window_quarters)]
estudy_all_events <- estudy_all_events[balanced_q_events, on = "event_uid"]

# Employment outcomes in three functional forms. log() is NA for non-positive
# values; asinh() (inverse hyperbolic sine) keeps zeros while giving ~% effects.
estudy_all_events[, `:=`(
  log_fte   = fifelse(fte > 0, log(fte), NA_real_),
  log_emp   = fifelse(employees > 0, log(employees), NA_real_),
  asinh_fte = asinh(fte),
  asinh_emp = asinh(employees)
)]

# firm + year + quarter FE: firm and calendar-year as before, plus quarter-of-year
# to absorb employment seasonality. (event_quarter dummies stay identified because
# year/quarter enter additively, not as the full calendar-quarter interaction.)
models_levels <- feols(c(fte, employees) ~ i(event_quarter, ref = -1) |
                         winner_cvr_final + year + quarter,
                       cluster = ~winner_cvr_final, data = estudy_all_events)
models_log    <- feols(c(log_fte, log_emp) ~ i(event_quarter, ref = -1) |
                         winner_cvr_final + year + quarter,
                       cluster = ~winner_cvr_final, data = estudy_all_events)
models_asinh  <- feols(c(asinh_fte, asinh_emp) ~ i(event_quarter, ref = -1) |
                         winner_cvr_final + year + quarter,
                       cluster = ~winner_cvr_final, data = estudy_all_events)
```

### First award (unbalanced)

Employment tends to fall after the first tender award. This is likely biased by firms dying as time passes.

```{r estudy-reg-all-qtr, fig.align='center'}
models <- feols(c(fte, employees) ~ i(event_quarter_binned, ref = -1) |
                  year + winner_cvr_final,
                cluster = ~winner_cvr_final,
                data = estudy_data[event_id == 1 &
                                     year >= firm_by &
                                     (year <= firm_dy | is.na(lifecycle_end)), ])

plot_es(models, "Effect on employment",
        xlab = "Quarters relative to first contract win")
```

### By agreement type (unbalanced)
Compares across framework agreements and public contracts. I hypothesise that Services behaves more like a demand shock that Works or Supplies, since it is likely more labour intensive.

```{r contract-type-estudy-qtr}

# Run models
models_by_type <- feols(c(fte, employees) ~ i(event_quarter_binned, ref = -1) |
                             year + winner_cvr_final,
                           cluster = ~winner_cvr_final,
                           split  = ~contract_type,
                           data   = estudy_data[event_id == 1 &
                                                  year >= firm_by &
                                                  (year <= firm_dy | is.na(lifecycle_end))])

# Framework agreement
plot_es(models_by_type[sample = "Framework agreement"],
        "Effect on employment; Framework agreement",
        xlab = "Quarters relative to first contract win")

# Public contract
plot_es(models_by_type[sample = "Public contract"],
        "Effect on employment; Public contracts",
        xlab = "Quarters relative to first contract win")


```

### By work category (unbalanced)
Compares across tenders for 'Works', 'Services' and 'Supplies'. I hypothesise that Services and Works behaves more like a demand shock than Supplies, since they are likely more labour intensive.

```{r work-category-estudy-qtr}

# Run models
models_by_work_cat <- feols(c(fte, employees) ~ i(event_quarter_binned, ref = -1) |
                             year + winner_cvr_final,
                           cluster = ~winner_cvr_final,
                           split  = ~cpv_category,
                           data   = estudy_data[event_id == 1 &
                                                  year >= firm_by &
                                                  (year <= firm_dy | is.na(lifecycle_end))])

# Works
plot_es(models_by_work_cat[sample = "Works"],
        "Effect on employment; Works",
        xlab = "Quarters relative to first contract win")

# Services
plot_es(models_by_work_cat[sample = "Services"],
        "Effect on employment; Services",
        xlab = "Quarters relative to first contract win")

# Supplies
plot_es(models_by_work_cat[sample = "Supplies"],
        "Effect on employment; Supplies",
        xlab = "Quarters relative to first contract win")

```


### All isolated events — levels (balanced)

```{r qtr-es-levels, fig.align='center'}
plot_es(models_levels, "Effect on employment (levels); all isolated events")
```

### All isolated events — log (balanced)

```{r qtr-es-log, fig.align='center'}
plot_es(models_log, "Effect on log employment; all isolated events")
```

### All isolated events — asinh (balanced)

```{r qtr-es-asinh, fig.align='center'}
plot_es(models_asinh, "Effect on asinh(employment); all isolated events")
```

## Balanced — isolated events, all awards {.tabset}

These event studies use **all** tender awards (every award per firm, not only the
first). An award enters only if it satisfies all three
conditions:

1. **Isolated** — the firm has no *other* award inside the event window on either
   side (annual: no other award within 1 year; quarterly: within 4 quarters), so
   the window reflects this one award rather than a pile-up of nearby awards.
2. **Fully in-sample** — the award's entire window falls inside the observed
   employment panel, dropping events near the start or end of the sample where the
   window would be truncated.
3. **Balanced with positive employment** — the firm is observed with **FTE > 0 and
   headcount > 0 in every period** of the window. This delivers a truly balanced
   panel and, by construction, drops any event with a zero-employment period.

The annual study uses a short ±1-year window (event years −1, 0, +1 only), so the
coefficients come from a simple, well-populated regression; the quarterly study
uses a ±4-quarter window. Firm and calendar fixed effects match the corresponding unbalanced studies
above (annual: firm + year; quarterly: firm + year + quarter-of-year), with
standard errors clustered by firm.

```{r balanced-isolated-setup, include=FALSE}
## Rebuild the annual and quarterly firm-data splits (the shared `estudy_data`
## object was repurposed by the quarterly chunk above).
firm_data_annual <- firm_data[frequency == "annual_spliced", ]
firm_data_qtr    <- firm_data[frequency == "quarterly_spliced", ]

## Award year on the event universe. award_qidx / gap_* were computed when the
## universe was built; here we add a year-based spacing for the annual window.
valid_winner_events[, award_year := year(award_date)]
setorder(valid_winner_events, winner_cvr_final, award_year, award_date)
valid_winner_events[, ygap_prev := award_year - shift(award_year), by = winner_cvr_final]
valid_winner_events[, ygap_next := shift(award_year, type = "lead") - award_year, by = winner_cvr_final]

## Isolated for the annual (+/-1y) window: no other award by the same firm within
## 1 year on either side (an award exactly 1 year away lands on the window edge,
## so isolation requires a gap strictly greater than 1 year).
valid_winner_events[, isolated_event_annual :=
                      (is.na(ygap_prev) | ygap_prev > 1) &
                      (is.na(ygap_next) | ygap_next > 1)]

## Helper: from a stacked (firm x event x period) table, keep only events observed
## with strictly positive employment in EVERY period of `window`, and return the
## balanced rows. This enforces balance and the "no zero-employment period" rule
## in one step (a zero/NA period is dropped, so the event then fails the count).
balance_positive <- function(dt, period_col, window) {
  d <- dt[get(period_col) %in% window]
  d[, ok := !is.na(fte) & !is.na(employees) & fte > 0 & employees > 0]
  keep <- d[ok == TRUE, .(n = uniqueN(get(period_col))), by = event_uid][n == length(window)]
  d[ok == TRUE][event_uid %in% keep$event_uid]
}

# ---- Annual, isolated, balanced, +/-1 year ---------------------------------
window_years <- -2:2
ann_bounds   <- range(firm_data_annual$year, na.rm = TRUE)

ann <- firm_data_annual[valid_winner_events, on = "winner_cvr_final", allow.cartesian = TRUE]
ann <- ann[!is.na(year)]
ann[, event_year := year - award_year]
ann[, event_uid  := paste(winner_cvr_final, event_id, sep = "_")]

## (1) isolated + (2) full window inside the observed panel
ann <- ann[isolated_event_annual == TRUE &
             award_year - max(window_years) >= ann_bounds[1] &
             award_year + max(window_years) <= ann_bounds[2]]

## (3) balanced with positive employment in every window year
ann_balanced <- balance_positive(ann, "event_year", window_years)

m_ann_balanced <- feols(c(log(fte), log(employees)) ~ i(event_year, ref = -1) |
                          year + winner_cvr_final,
                        cluster = ~winner_cvr_final, data = ann_balanced)

# ---- Quarterly, isolated, balanced, +/-4 quarters --------------------------
window_quarters <- -4:4
qtr_bounds <- range(firm_data_qtr$year * 4 + firm_data_qtr$quarter, na.rm = TRUE)

qtr <- firm_data_qtr[valid_winner_events, on = "winner_cvr_final", allow.cartesian = TRUE]
qtr <- qtr[!is.na(year)]
qtr[, obs_qidx      := year * 4 + quarter]
qtr[, award_qidx_e  := award_year * 4 + quarter(award_date)]
qtr[, event_quarter := obs_qidx - award_qidx_e]
qtr[, event_uid     := paste(winner_cvr_final, event_id, sep = "_")]

## (1) isolated (reuse the +/-4 quarter isolated_event) + (2) window in-sample
qtr <- qtr[isolated_event == TRUE &
             award_qidx_e - max(window_quarters) >= qtr_bounds[1] &
             award_qidx_e + max(window_quarters) <= qtr_bounds[2]]

## (3) balanced with positive employment in every window quarter
qtr_balanced <- balance_positive(qtr, "event_quarter", window_quarters)

m_qtr_balanced <- feols(c(log(fte), log(employees)) ~ i(event_quarter, ref = -1) |
                          winner_cvr_final + year + quarter,
                        cluster = ~winner_cvr_final, data = qtr_balanced)

## Retained sample sizes for the two balanced, isolated-event panels
balanced_sizes <- data.table(
  Sample = c("Annual (+/-1 year)", "Quarterly (+/-4 quarters)"),
  Events = c(uniqueN(ann_balanced$event_uid),        uniqueN(qtr_balanced$event_uid)),
  Firms  = c(uniqueN(ann_balanced$winner_cvr_final), uniqueN(qtr_balanced$winner_cvr_final)),
  Obs    = c(nrow(ann_balanced),                     nrow(qtr_balanced))
)
```

```{r balanced-isolated-sizes}
kable(balanced_sizes,
      caption = "Balanced, isolated-event samples (all awards, positive employment throughout the window)")
```


### Annual (±1 year)

Balanced only on event years −1, 0, +1 (positive employment in all three), so the coefficients on years 0 and +1 (relative to −1) come from a simple, fixed-composition regression.

```{r balanced-annual-es, fig.align='center'}
plot_es(m_ann_balanced,
        "Effect on employment; balanced isolated events (all awards)",
        xlab = "Years relative to contract win")
```

### Quarterly (±4 quarters)

```{r balanced-qtr-es, fig.align='center'}
plot_es(m_qtr_balanced,
        "Effect on employment; balanced isolated events (all awards)",
        xlab = "Quarters relative to contract win")
```

## Balanced — all awards, overlaps allowed {.tabset}

Same balanced construction as the section above — all awards; **FTE > 0 and headcount > 0 in every window period**; events whose window would run past the sample edges are dropped — **but without the isolation requirement**. An award is kept even if the same firm won other tenders inside the window. This substantially expands the sample; the trade-off is that a given window can be contaminated by the firm's other awards. The annual window is **±2 years**; the quarterly window stays at ±4 quarters. Fixed effects and clustering are unchanged (annual: firm + year; quarterly: firm + year + quarter-of-year; clustered by firm).(A wider annual window is not viable here: the annual employment series ends in 2018 while awards are concentrated in 2016 and later, so requiring several years of *post*-award annual data leaves almost no balanced events beyond ±2.)

```{r balanced-nonisolated-setup, include=FALSE}
## Non-isolated counterpart of the section above: same balance + in-sample
## screens, but no isolation filter, so overlapping award windows are allowed.
## Reuses balance_positive(), firm_data_annual/qtr, valid_winner_events (with
## award_year) and the panel bounds computed in the isolated setup chunk.

# ---- Annual, all awards (overlaps allowed), balanced, +/-2 years -----------
window_years_all <- -2:2

ann_all <- firm_data_annual[valid_winner_events, on = "winner_cvr_final", allow.cartesian = TRUE]
ann_all <- ann_all[!is.na(year)]
ann_all[, event_year := year - award_year]
ann_all[, event_uid  := paste(winner_cvr_final, event_id, sep = "_")]

## full window inside the observed panel (no isolation filter)
ann_all <- ann_all[award_year - max(window_years_all) >= ann_bounds[1] &
                     award_year + max(window_years_all) <= ann_bounds[2]]

ann_balanced_all <- balance_positive(ann_all, "event_year", window_years_all)

m_ann_balanced_all <- feols(c(log(fte), log(employees)) ~ i(event_year, ref = -1) |
                              year + winner_cvr_final,
                            cluster = ~winner_cvr_final, data = ann_balanced_all)

# ---- Quarterly, all awards (overlaps allowed), balanced, +/-4 quarters -----
window_quarters_all <- -4:4

qtr_all <- firm_data_qtr[valid_winner_events, on = "winner_cvr_final", allow.cartesian = TRUE]
qtr_all <- qtr_all[!is.na(year)]
qtr_all[, obs_qidx      := year * 4 + quarter]
qtr_all[, award_qidx_e  := award_year * 4 + quarter(award_date)]
qtr_all[, event_quarter := obs_qidx - award_qidx_e]
qtr_all[, event_uid     := paste(winner_cvr_final, event_id, sep = "_")]

qtr_all <- qtr_all[award_qidx_e - max(window_quarters_all) >= qtr_bounds[1] &
                    award_qidx_e + max(window_quarters_all) <= qtr_bounds[2]]

qtr_balanced_all <- balance_positive(qtr_all, "event_quarter", window_quarters_all)

m_qtr_balanced_all <- feols(c(log(fte), log(employees)) ~ i(event_quarter, ref = -1) |
                             winner_cvr_final + year + quarter,
                           cluster = ~winner_cvr_final, data = qtr_balanced_all)

## Retained sample sizes for the two balanced, all-award panels
balanced_all_sizes <- data.table(
  Sample = c("Annual (+/-2 years)", "Quarterly (+/-4 quarters)"),
  Events = c(uniqueN(ann_balanced_all$event_uid),        uniqueN(qtr_balanced_all$event_uid)),
  Firms  = c(uniqueN(ann_balanced_all$winner_cvr_final), uniqueN(qtr_balanced_all$winner_cvr_final)),
  Obs    = c(nrow(ann_balanced_all),                     nrow(qtr_balanced_all))
)
```

```{r balanced-nonisolated-sizes}
kable(balanced_all_sizes,
      caption = "Balanced samples, all awards (overlaps allowed, positive employment throughout the window)")
```

### Annual (±2 years)

Balanced on event years −2…+2 (positive employment in all five), all awards, overlaps allowed.

```{r balanced-annual-all-es, fig.align='center'}
plot_es(m_ann_balanced_all,
        "Effect on log(e); balanced, all awards (overlaps allowed)",
        xlab = "Years relative to contract win")
```

### Quarterly (±4 quarters)

```{r balanced-qtr-all-es, fig.align='center'}
plot_es(m_qtr_balanced_all,
        "Effect on log(e); balanced, all awards (overlaps allowed)",
        xlab = "Quarters relative to contract win")
```

