---
title: "Control Event Studies"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

# Clean up environment
rm(list = ls())

# Packages
library(here)
library(data.table)
library(tidyverse)
library(knitr)
library(fixest)
library(lubridate)
library(kableExtra)

# Paths
report_project_dir <- local({
  d <- normalizePath(getwd(), mustWork = TRUE)
  while (!file.exists(file.path(d, "cvr-cleaning.Rproj")) && dirname(d) != d) {
    d <- dirname(d)
  }
  d
})
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)

source(file.path(report_project_dir, "config.R"))
clean_data_dir <- dirs$clean_data
key_dir <- dirs$cvr_key

valid_cvrs <- function(x) {
  x <- trimws(as.character(x))
  x <- gsub("[^0-9]", "", x)
  x <- x[grepl("^[0-9]{1,8}$", x)]
  unique(sprintf("%08d", as.integer(x)))
}

# 1 Load data
## 1.1 Firm data
firm_data_raw <- fread(file.path(clean_data_dir, "cvr_employment_history_virk.csv"))
setDT(firm_data_raw)

firm_data <- copy(firm_data_raw)
setDT(firm_data)
firm_data[, firm_by := year(lifecycle_start)]
firm_data[, firm_dy := year(lifecycle_end)]
firm_data[, firm_age := as.integer(floor(as.numeric(period_end - lifecycle_start) / 365.25))]
firm_data_ls <- firm_data %>% 
  split(.$frequency)

## 1.2 Tender data
data_ot <- readRDS(file.path(clean_data_dir, "clean_winner_data_ot_name_matched.rds")) %>% 
  mutate(data_source = "OpenTender")
data_kfst <- readRDS(file.path(clean_data_dir, "clean_winner_data_kfst_name_matched.rds")) %>% 
  mutate(data_source = "KFST")
data_ot_buyers <- readRDS(file.path(clean_data_dir, "clean_buyer_data_ot_name_matched.rds")) %>% 
  mutate(data_source = "OpenTender")
data_kfst_buyers <- readRDS(file.path(clean_data_dir, "clean_buyer_data_kfst_name_matched.rds")) %>% 
  mutate(data_source = "KFST")
data_tender <- rbindlist(list(data_ot, data_kfst), fill = TRUE, ignore.attr = TRUE) %>% 
  select(data_source, tender_id, lot_id, award_date, winner_cvr_final, tender_amount, lot_amount, contract_type, cpv_category, cpv_sector, flag_awarded)
unique_cvrs <- unique(data_tender$winner_cvr_final)


## 1.3 CVR key (includes firm registration and death dates)
virk_data <- fread(file.path(key_dir, "cvr_names_virk_20260710_182823.csv"))
virk_data[, tender_firm := FALSE]
virk_data[cvr %in% unique_cvrs, tender_firm := TRUE]
```

```{r run-toggles}
construct_control_data <- 0 # 1 = find and construct control data for each event. 0 = read in pre-constructed control data.
```

# Introduction
The `virk.dk` API contains has employment data on a monthly, quarterly, and annual frequency. I pulled these data for every firm in the tender datasets. This note describes the quality of these data.

# Availability/coverage
```{r availability, fig.align='center'}

# How many CVRs actually appear in the employment data?

emp_cvrs <- valid_cvrs(firm_data_raw$cvr)

coverage_cvrs <- rbindlist(list(
  data.table(
    data_source = "OpenTender",
    firm_role = "Winner",
    cvr = valid_cvrs(data_ot$winner_cvr_final)
  ),
  data.table(
    data_source = "OpenTender",
    firm_role = "Buyer",
    cvr = valid_cvrs(data_ot_buyers$buyer_cvr_final)
  ),
  data.table(
    data_source = "KFST",
    firm_role = "Winner",
    cvr = valid_cvrs(data_kfst$winner_cvr_final)
  ),
  data.table(
    data_source = "KFST",
    firm_role = "Buyer",
    cvr = valid_cvrs(data_kfst_buyers$buyer_cvr_final)
  )
))

coverage_table <- coverage_cvrs[, .(
  n_cvrs = uniqueN(cvr),
  n_in_employment_data = uniqueN(cvr[cvr %in% emp_cvrs]),
  share_in_employment_data = round(uniqueN(cvr[cvr %in% emp_cvrs]) / uniqueN(cvr), 5)
), by = .(data_source, firm_role)]

kable(
  coverage_table,
  caption = "Share of valid firm CVRs in the tender data that appear in the pulled employment data"
)

# How many rows have non-missing data
missingness_table <- firm_data_raw[, .(
  # Counts
  n = .N, 
  n_nonmissing_fte = sum(!is.na(fte)),
  n_nonmissing_emp = sum(!is.na(employees)),
  n_nonmissing_emp_with_owner = sum(!is.na(employees_including_owners)),
  
  # Shares
  share_nonmissing_fte = round(sum(!is.na(fte)) / .N, 5),
  share_nonmissing_emp = round(sum(!is.na(employees)) / .N, 5),
  share_nonmissing_emp_with_owner = round(sum(!is.na(employees_including_owners)) / .N, 5)


), by = frequency]

kable(missingness_table,
      caption = "Employment data availability for firms that appear in the employment data")

```

# Balance
Below is a balance table of age for firms in our tender dataset compared to those not in the tender dataset. Firms appearing in our tender dataset tend are older than firms not in the tender dataset. This could be because firms who win tenders are usually more productive/cost competitive than firms who do not win them (especially if price is heavily weighted in deciding which firm to award a tender to).

```{r age-balance}

# Calculate firm age
anchor_date <- lubridate::floor_date(Sys.Date(), unit = "year") # Beginning of this year
virk_data[!is.na(lifecycle_end), firm_age := lifecycle_end - registration_date] # If firm ended, calculate total age
virk_data[is.na(lifecycle_end), firm_age := anchor_date - registration_date] # Otherwise, calculate from today's date
virk_data[, firm_age_yrs := as.numeric(firm_age) / 365.25]
virk_data[, firm_dissolved := fifelse(is.na(lifecycle_end), "Still registered", "Dissolved")]
age_regs <- feols(firm_age_yrs ~ i(tender_firm) - 1, fsplit = ~firm_dissolved, data = virk_data)

# Make table
age_table <- coeftable(age_regs) %>% 
  mutate(
    group = ifelse(str_detect(coefficient, "TRUE"), "Won tender", "No tender")
  ) %>% 
  select(sample, group, Estimate) %>% 
  pivot_wider(id_cols = group, names_from = sample, values_from = Estimate)

kable(
  age_table,
  caption = "Firm Age by Tender Winning Status",
  escape = FALSE,
  align = "lcc"
) %>%
  kable_styling(full_width = FALSE)
```

# Employment by firm age
```{r emp-by-firm-age, fig.align='center'}

# Regression data
reg_data <- firm_data[
  frequency == "annual" &
    exists_during_period == TRUE &
    !is.na(fte) &
    fte > 0 &
    !is.na(firm_age) &
    firm_age >= 0 &
    firm_age <= 100
]

regression_sample_table <- reg_data[, .(
  n = .N,
  n_firms = uniqueN(cvr),
  min_firm_age = min(firm_age),
  max_firm_age = max(firm_age)
)]

kable(
  regression_sample_table,
  caption = "Annual employment observations used in the firm-age regression"
)

# Regression
fte_reg <- feols(log(fte) ~ i(firm_age) - 1 | cvr, 
                 data = reg_data, 
                 cluster = ~cvr)
iplot(fte_reg)
```

# Set up control group

```{r es-plot-helper, include=FALSE}
# Helper: plot a pair of fixest models as one event-study figure
# (models[[1]] = FTE, models[[2]] = employees).
plot_es <- function(models, main, xlab = "Quarters relative to contract win") {
  iplot(list(models[[1]], models[[2]]),
        main   = main,
        xlab   = xlab,
        col    = c("steelblue", "darkred"),
        pt.pch = c(16, 17),
        ci.lty = c(1, 1))
  legend("bottomleft",
         legend = c("FTE", "Employees"),
         col    = c("steelblue", "darkred"),
         pch    = c(16, 17),
         lty    = c(1, 1),
         bty    = "n")
}
```

## Define universe of events

This section of code defines the universe of events for the annual event study.

```{r tender-award-estudy-data, include=FALSE}

# Build universe of events
## Get unique events
setDT(data_tender)
setorder(data_tender, winner_cvr_final, data_source, award_date)
## Awarded contracts only: drop tenders that were annulled / never awarded
## (flag_awarded is a tender/lot-level flag from the processing scripts). Applied
## to the event universe here, so it propagates to every event study below
## (annual estudy_data and quarterly estudy_all_events).
valid_winner_events <- data_tender[winner_cvr_final %in% coverage_cvrs[firm_role == "Winner"]$cvr &
                                     flag_awarded == TRUE, ]
valid_winner_events <- unique(valid_winner_events, by = c("winner_cvr_final", "award_date"))

## Create event identifier (chronological: event_id == 1 is the earliest award).
## Sort by award_date within firm *before* numbering. The earlier setorder puts
## data_source ahead of award_date, so numbering off that order would not be
## chronological for firms appearing in more than one source.
setorder(valid_winner_events, winner_cvr_final, award_date)
valid_winner_events[, event_id := seq_len(.N), by = winner_cvr_final]

## Flag "isolated" events: no other award by the same firm within 4 quarters on
## either side. Used by the all-events quarterly event study so the +/-4 quarter
## window around each event is not polluted by another award.
valid_winner_events[, award_qidx := year(award_date) * 4 + quarter(award_date)]
valid_winner_events[, gap_prev := award_qidx - shift(award_qidx), by = winner_cvr_final]
valid_winner_events[, gap_next := shift(award_qidx, type = "lead") - award_qidx, by = winner_cvr_final]
valid_winner_events[, isolated_event := (is.na(gap_prev) | gap_prev > 4) &
                                        (is.na(gap_next) | gap_next > 4)]

```

## Find control firm match for each firm-event
A control firm is the firm with:
- closest employment history to the treated firm (winner) in the 4 quarters prior to the award date
- closest age to the treated firm (winner) at the time of the award date
- same sector, and
- same location

```{r create-firm-data-qidx}
firm_data[, qidx := year * 4 + quarter]
# Make sure character to make faster
valid_winner_events[, winner_cvr_final := as.character(winner_cvr_final)] 
firm_data[, cvr := as.character(cvr)]
firm_data[, industry_code := as.character(industry_code)]
```

```{r find-control-firm, include=FALSE}

build_control_firm_data <- function(winning_firm_cvr, 
                              award_year, 
                              award_quarter, 
                              lookback = 4, 
                              freq = "quarterly_spliced",
                              firm_data = firm_data, 
                              event_data = valid_winner_events) {
  
  # Firm qidx at the time of the award
  winning_qidx <- award_year * 4 + award_quarter
  
  # Check firm in firm_data
  if (!(winning_firm_cvr %in% unique(firm_data$cvr))) {
    print(paste0("Winning firm CVR ", winning_firm_cvr, " not found in firm_data."))
    return(NULL)
  }
  
  # Extract firm sector, location and age at the time of the award
  winning_info <- firm_data[
    frequency == freq &
      cvr == winning_firm_cvr & 
      qidx %between% c(winning_qidx - lookback, winning_qidx - 1), 
    .(
      cvr = cvr,
      frequency = frequency,
      year = year, 
      quarter = quarter,
      qidx = qidx,
      firm_sector = industry_code,
      firm_age = firm_age,
      employees = employees,
      fte = fte
    )
  ]
  
  # Find eligible observations
  eligible_obs <- firm_data[
    cvr != winning_firm_cvr &
      frequency == freq &
      qidx %between% c(winning_qidx - lookback, winning_qidx - 1) & # A year before the tender award
      industry_code %chin% unique(winning_info$firm_sector), # A firm might change industry code in the event window
    .(cvr = cvr,
      year = year,
      quarter = quarter,
      qidx = qidx,
      firm_sector = industry_code,
      firm_age = firm_age,
      employees = employees,
      fte = fte)
  ]
  
  ## For these eligible firms, find ones that DIDN'T win a tender in the
  ## in c(award_qidx - lookback, award_qidx + lookback)
  no_tender_controls <- event_data[winner_cvr_final %chin% unique(eligible_obs$cvr) &
                                     !(award_qidx %between% c(winning_qidx - lookback, winning_qidx + 4)), ]
  no_tender_controls_cvrs <- no_tender_controls[, unique(winner_cvr_final)]
  eligible_obs <- eligible_obs[cvr %chin% no_tender_controls_cvrs, ]
  
  ## Create eligible control firm counter
  eligible_obs[, firm_counter_control := .GRP, by = cvr]

  # Cartesian join to find control firm
  eligible_obs <- merge(
    eligible_obs,
    winning_info,
    by = "qidx",
    suffixes = c("_control", "_treatment"),
    allow.cartesian = TRUE
  )

  # Order
  setorder(eligible_obs, firm_counter_control, qidx)

  # Calculate differences
  # for FTE, mean sq. difference in pre-period in fte
  eligible_obs[, `:=`(
    fte_diff_sq = (fte_control - fte_treatment) ^ 2,
    age_diff_sq = (firm_age_control - firm_age_treatment) ^ 2
    )]

  # Find means
  eligible_obs[, `:=`(
    mean_fte_diff_sq = mean(fte_diff_sq),
    mean_age_diff_sq = mean(age_diff_sq)
    ), by = .(firm_counter_control, cvr_control)]

  # Find closest match of sum of differences
  eligible_obs[, sum_diff := mean_fte_diff_sq + mean_age_diff_sq]
  control_firm_data <- eligible_obs[sum_diff == min(sum_diff), ]

  # Create control/treated data
  control_event_data <- firm_data[
    cvr %in% unique(control_firm_data$cvr_control) | cvr == winning_firm_cvr, 
    .(cvr, frequency, year, quarter, qidx, firm_age, employees, fte)
  ]
  control_event_data[, treatment := fifelse(cvr == winning_firm_cvr, "treated", "control")]
  control_event_data$event_year <- award_year
  control_event_data$event_quarter <- award_quarter
  control_event_data$event_qidx <- winning_qidx
  control_event_data$control_quality <- control_firm_data$sum_diff[1]
  control_event_data$flag_found_control <- (nrow(control_firm_data) > 0)
  # Print
  return(list(
    "control_firm_decision_data" = control_firm_data, 
    "all_eligible_controls" = unique(eligible_obs$cvr_control),
    "estudy_data" = control_event_data
    ))
  
}

```

```{r build-full-treatment-control-set}

# Create event year/quarter
valid_winner_events[, event_year := year(award_date)]
valid_winner_events[, event_quarter := quarter(award_date)]

# If toggle on, construct controls
if (construct_control_data == 1) {
  source("R/code/analysis/find_control_firms.R")
  control_event_data <- readRDS(file.path(clean_data_dir, "control_event_list.rds"))
} else {
  control_event_data <- readRDS(file.path(clean_data_dir, "control_event_list.rds"))
}

```

```{r run-controlled-estudy}

# Event window
window <- c(-8, 8) 

# Filter to events we found controls for
found_control_data <- control_event_data[flag_found_control == TRUE, ]

# Create event time
found_control_data[, event_time := qidx - event_qidx]

# Filter to window
found_control_data[, event_time_window := fifelse(event_time >= window[1] & event_time <= window[2], TRUE, FALSE)]
estudy_control_data <- found_control_data[event_time_window == TRUE, ]

# Create balanced dataset with all positive FTE observations
estudy_control_data[, fte_pos := fifelse(fte > 0, TRUE, FALSE)]
estudy_control_data[, all_fte_pos := all(fte_pos), by = .(cvr, event_qidx)]
estudy_control_data[, all_in_window := sum(event_time_window) == length(window[1]:window[2]),
                    by = .(cvr, stack_id, treatment)]
estudy_control_balanced_data <- estudy_control_data[all_in_window == TRUE, ]

# Ensure at least one treatment per stack_id
estudy_control_balanced_data[, n_treatment := sum(treatment == "treated"), by = stack_id]
estudy_control_balanced_data <- estudy_control_balanced_data[n_treatment > 0, ]

# Coerce event_time to factor
estudy_control_balanced_data[, event_time := factor(event_time)]

# Weightings
estudy_control_balanced_data[treatment == "treated", weight := 1]
estudy_control_balanced_data[, n_control := uniqueN(cvr[treatment == "control"]), by = .(stack_id)]
estudy_control_balanced_data[treatment == "control", weight := 1 / n_control, by = .(stack_id)]

# Filter to where I have at least one control
estudy_control_balanced_data <- estudy_control_balanced_data[n_control >= 1, ]

# Join sector
sector_codes <- firm_data[cvr %chin% unique(estudy_control_balanced_data$cvr), .(cvr, qidx, industry_code)]
estudy_control_balanced_data[sector_codes, on = .(cvr, qidx), industry_code := i.industry_code]

# treatment must be numeric 0/1
estudy_control_balanced_data[, treated := as.integer(treatment == "treated")]

# Check balanced of fine tuned regression data
control_quality_bounds <- c(0, 100)
reg_data <- estudy_control_balanced_data[control_quality %between% control_quality_bounds, ]
check <- all(reg_data[, .N, by = event_time]$N == unique(reg_data[, .N, by = event_time]$N))

if (!check) {
  stop("event study is not balanced.")
}

```

Below are the weighted mean employment levels for treated and control firms by event time. The weights are constructed such that each treated firm has a weight of 1, and the controls are weighted inversely by the number of controls in each stack.
```{r weighted-diff-in-means}

# Get regression metadata
n_per_period <- reg_data[, .(n = sum(weight)), by = .(event_time, treatment)]
n_firms <- reg_data[, uniqueN(cvr), by = treatment]
n_stacks <- reg_data[, uniqueN(stack_id)]

# Calculate weighted mean FTE
weighted_mean_fte <- reg_data[,
                              .(
                               mean_fte = sum(weight * fte) / sum(weight)
                               ), 
                             by = .(event_time, treatment, control_protocol)]

# Make graph
ggplot(data = weighted_mean_fte,
       aes(x = event_time, group = treatment, y = mean_fte, colour = treatment)) +
  geom_line() +
  labs(title = "FTE by Treatment Status",
       y = "FTE (level)", x = "Event time (t = 0 is award quarter)",
       caption = sprintf(
         "Control match quality in [%.2f, %.2f]; %s matched stacks.",
         control_quality_bounds[1], control_quality_bounds[2],
         format(n_stacks, big.mark = ","))) +
  theme(plot.caption = element_text(hjust = 0))
  

```

Below is the stacked DiD event study. The specification is:

$$

y = \sum_{k=-8}^{8} \beta_k \cdot 1\{eventTime = k\} \cdot 1[treated] + \gamma_{cvr} + \gamma_{quarter:industry} + \gamma_{treated} + \gamma_{eventTime} + \epsilon

$$
I think this is the right specification based on Deshpande and Li (2019). Standard errors are clustered at the stack-CVR level.
```{r run-estudy-regs}

# Run regression
est <- feols(c(fte, log(fte)) ~ i(event_time, treated, ref = -1) | 
               cvr + quarter^industry_code + treated + event_time,
      data = reg_data, 
      cluster = ~stack_id^cvr, 
      weights = ~weight)

# Graph
iplot(est[1])       
iplot(est[2]) 

```