---
title: "Reconcile Processed Data: KFST vs OpenTender"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(inputFile, encoding = encoding,
                      knit_root_dir = project_dir, output_dir = output_dir)
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
rm(list = ls())

library(tidyverse)
library(lubridate)
library(knitr)
library(kableExtra)
library(scales)

theme_set(theme_light())
theme_update(plot.title = element_text(hjust = 0.5, face = "bold"),
             plot.subtitle = element_text(hjust = 0.5))
source_pal <- c(KFST = "#4E79A7", OpenTender = "#F28E2B")

report_project_dir <- local({
  d <- normalizePath(getwd(), mustWork = TRUE)
  while (!file.exists(file.path(d, "cvr-cleaning.Rproj")) && dirname(d) != d) d <- dirname(d)
  d
})
setwd(report_project_dir)
knitr::opts_knit$set(root.dir = report_project_dir)
source(file.path(report_project_dir, "config.R"))

# TED notice id in a URL, e.g. ".../TED:NOTICE:303670-2017:..." -> "303670-2017".
# Like scraping/ted_1_extract_notices.R::derive_notice_id, but with a LOOSER digit
# count. KFST's raw award URLs carry the notice number UN-padded (e.g. "2521-2022"),
# whereas OpenTender/production URLs zero-pad it to 6 ("094091-2022"), so production's
# strict 6-8 digit rule silently drops KFST's short numbers. Allowing 1-8 leading
# digits recovers them; normalize_id() then re-pads to 6 so "2521-2022" and OT's
# "002521-2022" reconcile. Prefer the token right after "NOTICE:" (classic udl form),
# else fall back to any N-YYYY token (covers the new .../notice/<id> form).
extract_notice_id <- function(url) {
  id <- str_match(url, "NOTICE:([0-9]{1,8}-[0-9]{4})")[, 2]
  if_else(is.na(id), str_extract(url, "[0-9]{1,8}-[0-9]{4}"), id)
}
normalize_id <- function(id) {
  m <- str_match(id, "^0*([0-9]+)-([0-9]{4})$")
  if_else(is.na(m[, 2]), NA_character_,
          paste0(formatC(as.integer(m[, 2]), width = 6, flag = "0"), "-", m[, 3]))
}
```

```{r load-data}
# ---- OpenTender: PROCESSED winner table -------------------------------------
# clean_winner_data_ot.rds keeps only AWARDED/PREAWARDED, non-cancelled lots. The
# award-notice URL + award date are tender-level, so a distinct (tender_id, url,
# date) frame is one row per tender.
ot <- readRDS(file.path(dirs$clean_data, "clean_winner_data_ot.rds")) %>%
  transmute(source     = "OpenTender",
            tender_id  = as.character(tender_id),
            award_url  = tender_publications_lastContractAwardUrl,
            award_date) %>%
  distinct() %>%
  filter(!is.na(award_url) & award_url != "")

# ---- KFST: PROCESSED winner table -------------------------------------------
# clean_winner_data_kfst.rds now carries the award-notice URL directly (added in
# 1_1_process_kfst.R, renamed there from "Link til bekendtgørelse om indgået
# kontrakt"), so no join to the raw source is needed -- same shape as OpenTender.
kf <- readRDS(file.path(dirs$clean_data, "clean_winner_data_kfst.rds")) %>%
  transmute(source     = "KFST",
            tender_id  = as.character(tender_id),
            award_url,
            award_date) %>%
  distinct() %>%
  filter(!is.na(award_url) & award_url != "")

# ---- combine + extract notice ids -------------------------------------------
dat <- bind_rows(ot, kf) %>%
  mutate(notice_id  = normalize_id(extract_notice_id(award_url)),
         award_year = year(award_date))
```

# Overview

This note reconciles the two processed tender datasets by using the notice IDs. We can extract the notice IDs from the award notice URLs which are present in both datasets.

**Universe note.** These are the *cleaned* winner tables, which keep only `AWARDED`/`PREAWARDED` lots and drop cancelled tenders. So this universe is **awarded-only**.

```{r coverage}
coverage <- dat %>%
  group_by(Source = source) %>%
  summarise(`Tenders with award URL` = n_distinct(tender_id),
            `With notice ID`         = n_distinct(tender_id[!is.na(notice_id)]),
            `Distinct notice IDs`    = n_distinct(notice_id[!is.na(notice_id)]),
            .groups = "drop")
kable(coverage, format.args = list(big.mark = ","),
      caption = "Processed tenders with an award URL, and notice-ID coverage by source") %>%
  kable_styling(full_width = FALSE)
```

## KFST notice-ID extraction

KFST's raw award URLs carry the notice number **un-padded**, so the strict 6–8 digit
rule that production (`derive_notice_id`) applies to OpenTender's zero-padded URLs
silently drops any short KFST number (e.g. `2521-2022`). The looser rule used here
recovers them all — and most turn out to be notices OpenTender already has, so they
move from "KFST only" into "shared" once extracted.

```{r kfst-extraction-diagnostic}
# Re-derive with the STRICT production rule to size what it misses, on the distinct
# set of KFST award URLs (so the three tiers partition cleanly).
strict_id <- function(url) normalize_id(str_extract(url, "[0-9]{6,8}-[0-9]{4}"))
kfst_diag <- dat %>%
  filter(source == "KFST") %>%
  distinct(award_url) %>%
  mutate(id_loose  = normalize_id(extract_notice_id(award_url)),
         id_strict = strict_id(award_url))

diag_tbl <- tibble(
  metric = c("Distinct KFST award URLs",
             "extracted by the strict 6-8 digit rule (production)",
             "recovered by the looser 1-8 digit rule (un-padded short numbers)",
             "still unextractable"),
  n = c(nrow(kfst_diag),
        sum(!is.na(kfst_diag$id_strict)),
        sum(is.na(kfst_diag$id_strict) & !is.na(kfst_diag$id_loose)),
        sum(is.na(kfst_diag$id_loose))))
kable(diag_tbl, format.args = list(big.mark = ","),
      caption = "KFST notice-ID extraction: recovery of un-padded short-number notices") %>%
  kable_styling(full_width = FALSE)
```

# Notice-ID overlap between KFST and OpenTender

```{r overlap}
ids_kfst <- dat %>% filter(source == "KFST",       !is.na(notice_id)) %>% pull(notice_id) %>% unique()
ids_ot   <- dat %>% filter(source == "OpenTender", !is.na(notice_id)) %>% pull(notice_id) %>% unique()
shared    <- intersect(ids_kfst, ids_ot)
kfst_only <- setdiff(ids_kfst, ids_ot)
ot_only   <- setdiff(ids_ot, ids_kfst)

overlap_tbl <- tibble(
  set = c("Shared (in both)", "KFST only", "OpenTender only", "Union (distinct total)"),
  n_notice_ids = c(length(shared), length(kfst_only), length(ot_only),
                   length(union(ids_kfst, ids_ot))))
kable(overlap_tbl, format.args = list(big.mark = ","),
      caption = sprintf("TED award-notice IDs: KFST has %s, OpenTender has %s",
                        format(length(ids_kfst), big.mark = ","),
                        format(length(ids_ot), big.mark = ","))) %>%
  kable_styling(full_width = FALSE)
```

```{r overlap-plot, fig.align='center', fig.width=7, fig.height=4}
plot_dt <- tibble(
  category = factor(c("KFST only", "Shared", "OpenTender only"),
                    levels = c("KFST only", "Shared", "OpenTender only")),
  n = c(length(kfst_only), length(shared), length(ot_only)))
ggplot(plot_dt, aes(category, n, fill = category)) +
  geom_col(width = 0.65) +
  geom_text(aes(label = comma(n)), vjust = -0.3, size = 3.5) +
  scale_fill_manual(values = c("KFST only" = source_pal[["KFST"]],
                               "Shared" = "grey40",
                               "OpenTender only" = source_pal[["OpenTender"]]),
                    guide = "none") +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.1))) +
  labs(title = "TED award-notice IDs: shared vs source-specific",
       subtitle = "Universe: all non-cancelled preawarded/award tenders",
       x = NULL, y = "Distinct notice IDs")
```

# Unique tenders by award-date year

Number of **distinct `tender_id`s** in each processed source, grouped by the year of
the tender's award date (rows with a missing/undated award are excluded).

```{r tenders-by-year-line, fig.align='center', fig.width=9, fig.height=4.5}
by_year <- dat %>%
  filter(!is.na(award_year), between(award_year, 2006, 2026)) %>%
  group_by(source, award_year) %>%
  summarise(n_tenders = n_distinct(tender_id), .groups = "drop")

ggplot(by_year, aes(award_year, n_tenders, colour = source)) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 1.8) +
  scale_colour_manual(values = source_pal) +
  scale_y_continuous(labels = comma) +
  scale_x_continuous(breaks = scales::breaks_width(2)) +
  labs(title = "Unique tenders by award-date year (processed)",
       x = "Award-decision year", y = "Distinct tender IDs", colour = "Source")
```

```{r tenders-by-year-bar, fig.align='center', fig.width=9, fig.height=4.5}
ggplot(by_year, aes(award_year, n_tenders, fill = source)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.75) +
  scale_fill_manual(values = source_pal) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.05))) +
  scale_x_continuous(breaks = scales::breaks_width(2)) +
  labs(title = "Unique tenders by award-date year, side by side (processed)",
       x = "Award-decision year", y = "Distinct tender IDs", fill = "Source")
```

# Notice-ID composition by award year

Where do the **OpenTender-only** notices sit in time? Each distinct notice ID is
tagged as *KFST only*, *Both*, or *OpenTender only*, and placed in one award year
(preferring OpenTender's award year — present for *Both* and *OpenTender only* — and
falling back to KFST's for *KFST only*). If OpenTender-only notices are simply the
years KFST does not cover, the orange band should dominate outside KFST's window.

```{r notice-year-category}
notice_year <- dat %>%
  filter(!is.na(notice_id)) %>%
  group_by(notice_id) %>%
  summarise(in_k  = any(source == "KFST"),
            in_o  = any(source == "OpenTender"),
            yr_ot = suppressWarnings(min(award_year[source == "OpenTender"], na.rm = TRUE)),
            yr_k  = suppressWarnings(min(award_year[source == "KFST"],       na.rm = TRUE)),
            .groups = "drop") %>%
  mutate(across(c(yr_ot, yr_k), ~ if_else(is.infinite(.x), NA_real_, .x)),
         award_year = as.integer(coalesce(yr_ot, yr_k)),
         category   = factor(if_else(in_k & in_o, "Both",
                              if_else(in_k, "KFST only", "OpenTender only")),
                             levels = c("KFST only", "Both", "OpenTender only")))
```

```{r notice-year-stack, fig.align='center', fig.width=9, fig.height=4.5}
comp <- notice_year %>%
  filter(!is.na(award_year), between(award_year, 2006, 2026)) %>%
  count(award_year, category)
ggplot(comp, aes(award_year, n, fill = category)) +
  geom_col(width = 0.8, colour = "white", linewidth = 0.3) +
  scale_fill_manual(values = c("KFST only" = source_pal[["KFST"]],
                               "Both" = "grey40",
                               "OpenTender only" = source_pal[["OpenTender"]])) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.05))) +
  scale_x_continuous(breaks = scales::breaks_width(2)) +
  labs(title = "Unique TED notice IDs by award year and source coverage",
       x = "Award-decision year", y = "Distinct notice IDs", fill = "Coverage")
```
