---
title: "Validating the matching algorithm against real bidding non-winners"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
    df_print: kable
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    score <- Sys.getenv("VMC_SCORE", "level")
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir,
      output_file = paste0(tools::file_path_sans_ext(basename(inputFile)),
                           if (score == "log") "_log" else "", ".html")
    )
  })
---

<!--
WHAT THIS IS. The matching pipeline picks controls on an industry/kommune cascade plus closeness of
the pre-award FTE path. Nothing in it tests whether those controls behave like the ACTUAL
counterfactual. TED gives us one: firms that bid on the same lot and lost. This report compares
employment outcomes under the two control groups, at TWO event-study windows.

SCOPE: FOUR THINGS ONLY. (1) the event studies under each control group, with the post-period
equality tests in the plot titles; (2) the check that the fitted coefficients are exactly a
hand-computed difference in means; (3) why built events never reach a complete stack; (4) the
full-sample matched event study from stage 4 (04_estimates.rds + 04_estimation_panel.parquet, one
cell: VMC_FULL_PROTOCOL x VMC_FULL_ARM), which stage 4 now fits with the validated spec. The median-FTE
and size-ratio descriptives and the cross-window table were removed; the per-firm eligibility
verdicts (pool_side, buffer_ok, elig_pre, elig_post, eligible, in_both_roles) are still in
05_cobidder_roster_h{h}.rds if they are wanted again.

INPUT. code/matching/5_cobidder_stacks.R builds ONE stack per (contract notice, winner) holding all
three groups -- the winner, its synthetic matched controls, and its real losing co-bidders -- at the
same t = 0, with employment for each. ONE RUN PER WINDOW, h in the filename:

  05_cobidder_panel_h{h}.parquet   the regression-ready panel, one row per (event, firm, quarter)
  05_cobidder_roster_h{h}.rds      one row per (event, firm), plus `event_fate`: one row per event,
                                   the stage and reason it was dropped. Read by the last section.

  MATCH_OVERWRITE=1 [MATCH_SCORE=log] Rscript code/matching/5_cobidder_stacks.R   # builds h = 8 and 4
  Rscript -e 'rmarkdown::render("code/analysis/estudy_matched_vs_cobidder_validation.Rmd")'
  VMC_SCORE=log Rscript -e 'rmarkdown::render("code/analysis/estudy_matched_vs_cobidder_validation.Rmd",
                                              output_file = "estudy_matched_vs_cobidder_validation_log.html")'

The RStudio Knit button goes through the `knit:` hook above, which names the output by VMC_SCORE
automatically (the log knit gets a `_log` suffix). A bare rmarkdown::render() does NOT use the hook,
so pass output_file yourself as in the second line, or the log knit overwrites the level HTML.

Parameters are VMC_* environment variables. This report is READ-ONLY with respect to the pipeline and
writes nothing under match_paths() unless VMC_SAVE=1. The layout is exactly TWO window sections;
VMC_WINDOWS changes WHICH two, not how many. Needs the `car` package for the equality tests.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# opts_knit$get("output.dir") is NULL when running chunks interactively, and nzchar(NULL) errors in
# a bare if(). Fall back to getwd(), then walk up to the .Rproj marker.
.od <- knitr::opts_knit$get("output.dir")
project_dir <- if (!is.null(.od) && nzchar(.od)) .od else getwd()
project_dir <- normalizePath(project_dir, mustWork = TRUE)
while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
       dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)

suppressPackageStartupMessages({
  library(data.table); library(arrow); library(ggplot2); library(knitr); library(fixest)
})
# Sourced, not match_setup(): that setwd()s and re-sources, hostile inside a knit.
source(file.path(project_dir, "config.R"))
source(file.path(project_dir, "code", "functions.R"))
source(file.path(project_dir, "code", "matching", "0_matching_utils.R"))

.envchr <- function(k, d) { v <- Sys.getenv(k, ""); if (nzchar(v)) v else d }
.envint <- function(k, d) { v <- Sys.getenv(k, ""); if (nzchar(v)) as.integer(v) else d }
.envvec <- function(k, d) { v <- Sys.getenv(k, ""); x <- if (nzchar(v)) v else d
                            as.integer(strsplit(trimws(x), "[ ,]+")[[1]]) }

TAG        <- .envchr("VMC_TAG", match_tag())
SCORE      <- .envchr("VMC_SCORE", "level")      # stage-5 MATCH_SCORE to read: level | log
WINDOWS    <- .envvec("VMC_WINDOWS", "8 4")      # +/- quarters; one stage-5 run each
MIN_EVENTS <- .envint("VMC_MIN_EVENTS", 20L)     # mirrors MATCH_MIN_STACKS
SAVE       <- .envint("VMC_SAVE", 0L) == 1L

P   <- match_paths(TAG)
fmt <- function(x) formatC(x, big.mark = ",", format = "d")

# Lifted to the top because the presentation chunks call iplot() on a stored fit and can no longer
# reach `reg_data` for a legend, and because one definition of the clustering means the intervals on
# a plot and the p-values in the table beside it can never come from different assumptions.
CL            <- ~ cvr                    # ~ lot_key + cvr to add the notice dimension
SAMPLE_LEVELS <- c("Synthetic matched control", "Real losing co-bidder")
FATE_STAGES   <- c("matching", "balancing", "kept")

# The full-sample section: which stage-4 cell to show.
# the stage-4 protocol matching what the co-bidder stacks used: same windows, same score
FULL_PROTOCOL <- .envchr("VMC_FULL_PROTOCOL", if (SCORE == "log") "full_full_log" else "full_full")
FULL_ARM      <- .envchr("VMC_FULL_ARM",      "never_winner")

# Label for a plot title. Takes the table rather than closing over it, so it is safe to call from a
# presentation chunk with any window's eq_tests.
eq_note <- function(label, input_dt) {
  row <- input_dt[outcome == label]
  out <- paste0("Post-period joint nullity p = ", round(row$joint_p, 3),
                " | Average nullity p = ", round(row$avg_p, 3))
  return(out)
}
```

```{r analyse, include=FALSE}
# Everything numeric for one window. Returns tables and fitted objects; prints nothing and emits no
# prose, so the per-window subsections below stay thin and identical in structure.
analyse_window <- function(h) {
  meta <- read_obj(P$cobid_roster(h, SCORE))
  # The window and score are in the filename, so a mismatch means a stale artefact under a new name.
  # Rosters written before MATCH_SCORE existed carry no `score` and were all level.
  stopifnot(identical(as.integer(meta$h), as.integer(h)),
            identical(if (is.null(meta$score)) "level" else meta$score, SCORE))

  # event_fate is written by stage 5 from 1 Oct 2026; an older roster predates it.
  fate <- as.data.table(meta$event_fate)
  # The full path and write time are in the message: if stage 5 WAS re-run, the usual cause is that
  # the knit resolved a different dirs$data or tag than the Rscript run did.
  if (!nrow(fate)) stop(sprintf(paste("roster has no event_fate -- re-run 5_cobidder_stacks.R at",
                                      "MATCH_H=%d.\n  read: %s\n  written: %s (run_at %s)"),
                                h, P$cobid_roster(h, SCORE), format(file.mtime(P$cobid_roster(h, SCORE))),
                                format(meta$run_at)), call. = FALSE)

  # complete_stack: the event still holds all three groups after balancing. Everything runs on this.
  panel <- read_tab(P$cobid_panel(h, SCORE))
  d     <- panel[complete_stack == TRUE]
  # The fate table and the panel are two views of the same run, so they must agree on what was kept.
  stopifnot(fate[stage == "kept", .N] == d[, uniqueN(ev)])

  # ---- estimation --------------------------------------------------------------------------------
  # Winner rows are deliberately duplicated across the two stacks. Fine under split = ~sample, which
  # fits each separately -- but never pool reg_data into one regression without dropping a copy.
  nw_d <- d[category %chin% c("treated", "non_winner")][,    sample := "non_winner_stack"]
  sw_d <- d[category %chin% c("treated", "found_control")][, sample := "synthetic_stack"]
  reg_data <- rbindlist(list(nw_d, sw_d), use.names = TRUE, fill = TRUE)
  reg_data[, sample := factor(sample,
                              levels = c("synthetic_stack", "non_winner_stack"),
                              labels = SAMPLE_LEVELS)]

  # Both stacks must rest on the SAME events, or the gap between the lines is part sample composition.
  stopifnot(reg_data[, uniqueN(ev), by = sample][, uniqueN(V1)] == 1L)

  # i(event_time, treated) gives one interaction per k only if treated is numeric 0/1. A factor gets an
  # interaction for each level, collinear with the event_time FE, and fixest may drop the wrong ones --
  # silently moving the omitted period.
  stopifnot(is.numeric(reg_data$treated), all(reg_data$treated %in% c(0, 1)))

  mods <- feols(fte ~ i(event_time, treated, ref = "-1") |
                  treated + event_time,
                data = reg_data[complete_stack == TRUE, ],
                split = ~sample, cluster = CL, weights = ~weight)

  log_mods <- feols(log(fte) ~ i(event_time, treated, ref = "-1") |
                      treated + event_time,
                    data = reg_data[complete_stack == TRUE, ],
                    split = ~sample, cluster = CL, weights = ~weight)

  # t = -1 is the omitted base period, added back at zero so every path is anchored alike.
  # A fixest_multi is indexed by POSITION: m[["label"]] errors. Hence seq_along() plus names()[i],
  # with the "sample: " prefix stripped.
  tidy_es <- function(m, outcome) {
    lbl <- sub("^[^:]+: ", "", names(m))
    stopifnot(length(lbl) == length(m))
    rbindlist(lapply(seq_along(m), function(i) {
      ct <- as.data.table(coeftable(m[[i]]), keep.rownames = "term")[grepl("event_time", term)]
      ct[, event_time := as.integer(gsub(".*event_time::(-?[0-9]+).*", "\\1", term))]
      rbind(ct[, .(event_time, est = Estimate, se = `Std. Error`)],
            data.table(event_time = -1L, est = 0, se = 0))[
              , `:=`(control = lbl[i], outcome = outcome)]
    }))
  }
  coefs <- rbind(tidy_es(mods, "FTE (level)"), tidy_es(log_mods, "log FTE"))
  coefs[, `:=`(lo = est - 1.96 * se, hi = est + 1.96 * se)]
  coefs[, control := gsub("sample; sample: ", "", control)]
  setorder(coefs, outcome, control, event_time)

  # Both designs in ONE fit, so Cov(beta_syn, beta_cob) exists; split = ~sample gives no such term.
  # Every FE carries ^sample -- the winner rows are duplicated, so a shared FE would pool them and
  # force beta_syn == beta_cob exactly. The clustering is NOT interacted: that is what makes the
  # covariance.
  rd <- reg_data[complete_stack == TRUE]
  rd[, D_syn := as.integer(treated == 1L & sample == "Synthetic matched control")]
  rd[, D_cob := as.integer(treated == 1L & sample == "Real losing co-bidder")]
  # Same guard as above, for the two treated indicators this fit interacts with event_time
  stopifnot(is.numeric(rd$D_syn), all(rd$D_syn %in% c(0, 1)),
            is.numeric(rd$D_cob), all(rd$D_cob %in% c(0, 1)))

  st     <- feols(fte ~ i(event_time, D_syn, ref = "-1") + i(event_time, D_cob, ref = "-1") |
                    treated^sample + event_time^sample,
                  data = rd, cluster = CL, weights = ~weight)
  st_log <- feols(log(fte) ~ i(event_time, D_syn, ref = "-1") + i(event_time, D_cob, ref = "-1") |
                    treated^sample + event_time^sample,
                  data = rd, cluster = CL, weights = ~weight)

  # If the stacked estimates do not reproduce the split ones, an FE was left un-interacted.
  .pick <- function(m, sfx) {
    ct <- as.data.table(coeftable(m), keep.rownames = "term")
    ct <- ct[grepl(sprintf("^event_time::-?[0-9]+:%s$", sfx), term)]
    ct[, k := as.integer(gsub("^event_time::(-?[0-9]+):.*$", "\\1", term))]
    ct[order(k), Estimate]
  }
  stack_gap <- max(abs(.pick(st, "D_syn") - coefs[outcome == "FTE (level)" &
                            control == "Synthetic matched control" & event_time != -1L][
                            order(event_time), est]),
                   abs(.pick(st, "D_cob") - coefs[outcome == "FTE (level)" &
                            control == "Real losing co-bidder" & event_time != -1L][
                            order(event_time), est]))
  stopifnot(stack_gap < 1e-8)

  # H0: beta_syn_k = beta_cob_k. Joint over every k in the period, and on their average (1 df).
  # NB the POST period is selected by the regex -- `[0-9]+` with no leading `-?` admits k >= 0 only.
  # `period` is a label on the output, not a filter: passing "pre" would return the post test.
  wald_eq <- function(m, period, label) {

    # Extract objects for running tests
    nm  <- names(coef(m))
    syn <- grep("^event_time::[0-9]+:D_syn$", nm, value = TRUE)
    cob <- sub("D_syn$", "D_cob", syn)
    stopifnot(length(syn) > 0L, all(cob %in% nm))

    # Create vectors for tests
    hyp <- sprintf("%s = %s", syn, cob) # Joint nullity
    avg <- paste0(paste(syn, collapse = " + "),
                  " - ",
                  paste(cob, collapse = " - "),
                  " = 0") # Average/sum

    # Perform tests using car package
    joint_null <- car::linearHypothesis(m, hyp, test = "Chisq")
    avg_null <- car::linearHypothesis(m, avg, test = "Chisq")

    # Create out
    data.table(outcome = label, period = period,
               joint_p = max(joint_null$`Pr(>Chisq)`, na.rm = T),
               avg_p = max(avg_null$`Pr(>Chisq)`, na.rm = T))

  }

  eq_tests <- rbindlist(list(
    wald_eq(st,     "post", "FTE (level)"),
    wald_eq(st_log, "post", "log FTE")))

  # ---- the DiD-of-means check --------------------------------------------------------------------
  # hand-computed weighted DiD, no regression involved
  did_by_hand <- function(dat, samp, yvar) {
    cm <- dat[sample == samp, .(y = weighted.mean(get(yvar), weight)), by = .(treated, event_time)]
    wd <- dcast(cm, event_time ~ treated, value.var = "y")
    setnames(wd, c("0", "1"), c("ctrl", "trt"))
    base <- wd[event_time == -1L, trt - ctrl]
    wd[, .(event_time, ctrl, trt, did = (trt - ctrl) - base)][order(event_time)]
  }

  rd[, log_fte := log(fte)]
  did_cmp <- rbindlist(lapply(levels(rd$sample), function(lbl) rbindlist(list(
    did_by_hand(rd, lbl, "fte")[,     `:=`(control = lbl, outcome = "FTE (level)")],
    did_by_hand(rd, lbl, "log_fte")[, `:=`(control = lbl, outcome = "log FTE")]))))

  # `coefs` is what the tabset plots, read off the fitted objects
  did_cmp <- merge(did_cmp, coefs[, .(control, outcome, event_time, fitted = est)],
                   by = c("control", "outcome", "event_time"))
  did_cmp[, gap := did - fitted]
  stopifnot(did_cmp[, max(abs(gap))] < 1e-8)

  list(h = h, meta = meta, fate = fate,
       n_complete = d[, uniqueN(ev)],
       mods = mods, log_mods = log_mods, coefs = coefs,
       st = st, st_log = st_log, eq_tests = eq_tests, did_cmp = did_cmp)
}

WIN <- lapply(setNames(WINDOWS, paste0("h", WINDOWS)), analyse_window)
# Every section below has exactly two window subsections. Fail loudly rather than drop one silently.
stopifnot(length(WIN) == 2L)
W1 <- WIN[[1]]; W2 <- WIN[[2]]

.short <- function(w) sprintf("+/-%d quarters", w$h)
.warn  <- function(w) if (w$n_complete < MIN_EVENTS)
  sprintf(paste("**INSUFFICIENT EVENTS: %d complete stacks, below VMC_MIN_EVENTS = %d.**",
                "Everything in this section is reported for completeness but should not be",
                "interpreted."), w$n_complete, MIN_EVENTS) else ""
```

# Specification

Let $i$ index firms, $e$ a stack (one contract notice $\times$ winner), and $t$ a calendar quarter. $T_e$ is the award quarter of stack $e$'s notice, so event time is $k = t - T_e$, and the panel is balanced on $k \in \{-h, \dots, h\}$. $D_i = 1$ for the winner of the stack and $0$ for its controls. Then

$$
y_{iet} \;=\; \sum_{\substack{k=-h \\ k \neq -1}}^{h} \beta_k \bigl(\mathbf{1}[t - T_e = k] \cdot D_i\bigr)
\;+\; \delta D_i \;+\; \theta_k \;+\; \varepsilon_{iet}
$$

I cluster **standard errors** at the `cvr` level. 

I perform two **equality tests** to compare the real non-winning bidders to found control group from the matching process. The first is **joint** test, where $H_0$ is $\beta^{syn}_k = \beta^{cob}_k$ at every $k$. This tests the size and shape of the tender award on employment. The second is an **average**, the same equality summed over those $k$. This tests whether the average size of the effect is the same between the two control groups. 

The coefficients should equal the weighted difference in means:

$$\hat\beta_k \;=\; \left[\bar y_T(k) - \bar y_C(k)\right] - \left[\bar y_T(-1) - \bar y_C(-1)\right]$$

with $\bar y$ the weighted mean over a (group, event time) cell. 

# Event studies

## `r .short(W1)` {.tabset}

`r .warn(W1)`

### FTE (level)

```{r w1-plot-fte, fig.width = 9, fig.height = 5.5, fig.align = 'center'}
iplot(W1$mods,
      main = paste0("Winner vs synthetic control and real co-bidder, ", .short(W1), "\n",
                    eq_note("FTE (level)", input_dt = W1$eq_tests)),
      xlab = "Quarters relative to award",
      ylab = "Effect on FTE",
      pt.join = TRUE)
legend("topleft", legend = SAMPLE_LEVELS, col = 1:2, pch = 20, lwd = 1, bty = "n")
```

### log FTE

```{r w1-plot-log, fig.width = 9, fig.height = 5.5, fig.align = 'center'}
iplot(W1$log_mods,
      main = paste0("Winner vs synthetic control and real co-bidder, ", .short(W1), "\n",
                    eq_note("log FTE", input_dt = W1$eq_tests)),
      xlab = "Quarters relative to award",
      ylab = "Effect on log(FTE)",
      pt.join = TRUE)
legend("topleft", legend = SAMPLE_LEVELS, col = 1:2, pch = 20, lwd = 1, bty = "n")
```

## `r .short(W2)` {.tabset}

`r .warn(W2)`

### FTE (level)

```{r w2-plot-fte, fig.width = 9, fig.height = 5.5, fig.align = 'center'}
iplot(W2$mods,
      main = paste0("Winner vs synthetic control and real co-bidder, ", .short(W2), "\n",
                    eq_note("FTE (level)", input_dt = W2$eq_tests)),
      xlab = "Quarters relative to award",
      ylab = "Effect on FTE",
      pt.join = TRUE)
legend("topleft", legend = SAMPLE_LEVELS, col = 1:2, pch = 20, lwd = 1, bty = "n")
```

### log FTE

```{r w2-plot-log, fig.width = 9, fig.height = 5.5, fig.align = 'center'}
iplot(W2$log_mods,
      main = paste0("Winner vs synthetic control and real co-bidder, ", .short(W2), "\n",
                    eq_note("log FTE", input_dt = W2$eq_tests)),
      xlab = "Quarters relative to award",
      ylab = "Effect on log(FTE)",
      pt.join = TRUE)
legend("topleft", legend = SAMPLE_LEVELS, col = 1:2, pch = 20, lwd = 1, bty = "n")
```

# Difference-in-means check

For each window: the largest gap between the hand-computed DiD and the fitted coefficient (should be
numerically zero), then the weighted cell means behind it, which is where any surprising coefficient
should be read from.

## `r .short(W1)`

```{r w1-did}
kable(W1$did_cmp[, .(periods = .N, max_abs_gap = max(abs(gap))), by = .(outcome, control)],
      digits = 12,
      caption = "Hand-computed difference-in-differences against the fitted coefficients.")
```

```{r w1-did-cells}
kable(dcast(W1$did_cmp[outcome == "FTE (level)"], event_time ~ control,
            value.var = c("trt", "ctrl", "did")),
      digits = 2,
      caption = paste("Weighted mean FTE in each cell and the resulting DiD, by event time.",
                      "trt = winners, ctrl = that design's control group."))
```

## `r .short(W2)`

```{r w2-did}
kable(W2$did_cmp[, .(periods = .N, max_abs_gap = max(abs(gap))), by = .(outcome, control)],
      digits = 12,
      caption = "Hand-computed difference-in-differences against the fitted coefficients.")
```

```{r w2-did-cells}
kable(dcast(W2$did_cmp[outcome == "FTE (level)"], event_time ~ control,
            value.var = c("trt", "ctrl", "did")),
      digits = 2,
      caption = paste("Weighted mean FTE in each cell and the resulting DiD, by event time.",
                      "trt = winners, ctrl = that design's control group."))
```

# Why events were discarded

```{r fate}
fate <- rbindlist(lapply(WIN, function(w)
  w$fate[, .(events = .N), by = .(stage, reason)][, window := .short(w)]))
fate[, share := events / sum(events), by = window]
fate[, value := sprintf("%s (%.1f%%)", fmt(events), 100 * share)]
# Factors so dcast keeps the funnel order and puts the windows in VMC_WINDOWS order. Within a stage,
# reasons are ordered by their count in the first window.
fate[, stage  := factor(stage, levels = FATE_STAGES)]
fate[, window := factor(window, levels = vapply(WIN, .short, character(1)))]
r_ord <- fate[, .(n1 = sum(events[window == levels(window)[1]])), by = .(stage, reason)][
  order(stage, -n1), reason]
fate[, reason := factor(reason, levels = unique(r_ord))]

fate_wide <- dcast(fate, stage + reason ~ window, value.var = "value", fill = "0 (0.0%)")
setorder(fate_wide, stage, reason)
fate_wide[, `:=`(stage = as.character(stage), reason = as.character(reason))]
totals <- fate[, .(value = fmt(sum(events))), by = window]
fate_wide <- rbind(fate_wide,
                   as.data.table(c(list(stage = "total", reason = "events built"),
                                   setNames(as.list(totals$value), as.character(totals$window)))))
kable(fate_wide, caption = paste("Outcome of every event built, first failure wins.",
                                 "Count and share of that window's events built."))
```

# Full-sample event study

```{r full, include=FALSE}
# Stage 4's own artefacts, read not rebuilt: the estimation panel is exactly the rows stage 4's feols
# saw (post qscore cutoff, weights rebuilt), and 04_estimates carries its coefficients and sample sizes.
est4 <- read_obj(P$estimates)
H_FULL <- unique(est4$coefs$window)
stopifnot(length(H_FULL) == 1L)

fp    <- load_estimation_panel(FULL_PROTOCOL, FULL_ARM, tag = TAG)
summ4 <- est4$summary[scoring_protocol == FULL_PROTOCOL & arm == FULL_ARM]
if (nrow(summ4) != 1L)
  stop(sprintf(paste("04_estimates has no %s x %s cell (stage 4 has: %s).\n  If it is a new protocol,",
                     "re-run stages 2-4; or knit with VMC_FULL_PROTOCOL set to one that exists."),
               FULL_PROTOCOL, FULL_ARM,
               paste(unique(est4$summary[, paste(scoring_protocol, arm, sep = " x ")]), collapse = ", ")),
       call. = FALSE)
# If these disagree, 04_estimation_panel and 04_estimates come from different stage-4 runs.
stopifnot(nrow(summ4) == 1L, nrow(fp) == summ4$rows, uniqueN(fp$stack_id) == summ4$stacks)

full_cf <- est4$coefs[scoring_protocol == FULL_PROTOCOL & arm == FULL_ARM,
                      .(outcome, event_time, est, se, lo, hi)]
setorder(full_cf, outcome, event_time)

# Stage 4 now runs the validated specification. Re-fit it here on stage 4's own rows: if the
# estimates or SEs differ, stage 4 is stale (still the old cvr + qidx^industry_grp spec) or the two
# have drifted apart again.
stopifnot(is.numeric(fp$treated), all(fp$treated %in% c(0, 1)))   # treated must be numeric 0/1 -- see analyse_window
full_mods <- feols(c(fte, log(fte)) ~ i(event_time, treated, ref = "-1") | treated + event_time,
                   data = fp, cluster = CL, weights = ~weight)
full_val <- rbindlist(lapply(seq_along(full_mods), function(m) {
  ct <- as.data.table(coeftable(full_mods[[m]]), keep.rownames = "term")[grepl("event_time", term)]
  ct[, event_time := as.integer(gsub(".*event_time::(-?[0-9]+).*", "\\1", term))]
  rbind(ct[, .(event_time, est_rmd = Estimate, se_rmd = `Std. Error`)],
        data.table(event_time = -1L, est_rmd = 0, se_rmd = 0))[
          , outcome := c("FTE (level)", "log FTE")[m]]
}))
full_chk <- merge(full_cf, full_val, by = c("outcome", "event_time"))
stopifnot(nrow(full_chk) == nrow(full_cf))
if (full_chk[, max(abs(est - est_rmd), abs(se - se_rmd))] > 1e-8)
  stop("04_estimates does not reproduce the validated spec -- re-run 4_run_regressions.R",
       call. = FALSE)
```

The co-bidder sections test whether the synthetic control reproduces the path of the firm that
really bid and lost, on the small set of lots where both exist. Given that the two broadly agree
there, this section applies the matched design to **every** competitive award in the main pipeline:
stage 4's estimation sample, protocol **`r FULL_PROTOCOL`**, arm **`r FULL_ARM`**, window
$\pm$`r H_FULL` quarters, stacks with `control_qscore` $\leq$ `r summ4$qscore_bound`.

The specification is the one validated above: `treated` and `event_time` fixed effects, weighted,
clustered on `cvr`. Stage 4 estimates it; this report re-fits it on stage 4's rows and stops if the
two disagree, so the plot is guaranteed to be the validated estimator.

The sample still differs from the co-bidder stacks in two ways. The event is a **(firm, quarter)**,
the earliest competitive award in that quarter, not a (notice, winner) pair. And stage 4 drops
stacks with a poor match (the `control_qscore` cutoff), which the co-bidder panel does not do.

```{r full-sample}
kable(summ4[, .(window, scoring_protocol, arm, qscore_bound, stacks_before, stacks,
                kept = sprintf("%.1f%%", 100 * stacks / stacks_before),
                treated_firms, control_firms, rows)],
      format.args = list(big.mark = ","),
      caption = "Stage-4 estimation sample. stacks_before = before the qscore cutoff.")
```

```{r full-plot, fig.width = 10, fig.height = 5, fig.align = 'center'}
ggplot(full_cf, aes(event_time, est)) +
  geom_hline(yintercept = 0, colour = "grey50", linewidth = 0.3) +
  geom_vline(xintercept = -0.5, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.15, fill = "#2c7fb8") +
  geom_line(linewidth = 0.5, colour = "#2c7fb8") + geom_point(size = 1.4, colour = "#2c7fb8") +
  facet_wrap(~ outcome, scales = "free_y") +
  scale_x_continuous(breaks = seq(-H_FULL, H_FULL, 2)) +
  labs(title = sprintf("Competitive award: employment response, full matched sample (+/-%d)", H_FULL),
       subtitle = sprintf("%s | %s | qscore <= %.2f | %s stacks", FULL_PROTOCOL, FULL_ARM,
                          summ4$qscore_bound, fmt(summ4$stacks)),
       x = "Quarters relative to award (t = -1 omitted)", y = "Effect (treated - control)",
       caption = "Shaded = 95% CI, clustered by firm.") +
  theme_light(base_size = 11) +
  theme(plot.title = element_text(face = "bold"), plot.caption = element_text(hjust = 0))
```

## All event studies

```{r full-figs, out.width = "100%"}
figs <- file.path(P$figures, sprintf("estudy_h%d_%s.png", H_FULL, unique(est4$summary$arm)))
figs <- figs[file.exists(figs)]
if (!length(figs)) stop("no stage-4 event-study figures in ", P$figures, " -- re-run 4_run_regressions.R",
                        call. = FALSE)
# rel_path = FALSE: by default knitr rewrites an absolute path relative to the Rmd's folder (code/analysis),
# then checks it from the knit root (the project root, via the knit hook), so a file outside the repo --
# like these, on Box -- is reported missing although it exists.
knitr::include_graphics(figs, rel_path = FALSE)
```

```{r full-pretrend}
# The same tests as the figure labels, read from 04_estimates rather than off the PNGs.
if (!is.null(est4$pretrend_tests) && nrow(est4$pretrend_tests))
  kable(est4$pretrend_tests[, .(scoring_protocol, arm, outcome, k_tested, df, chisq, p)],
        digits = c(0, 0, 0, 0, 0, 2, 4),
        caption = "Pre-trend tests, unmatched pre-period quarters jointly zero (chi-squared).")
```

```{r save, include=FALSE}
if (SAVE) {
  for (w in WIN) {
    out <- file.path(P$dir, sprintf("05_validation_cobidder_h%d%s%s.rds", w$h,
                                    if (SCORE == "log") "_log" else "",
                                    if (nzchar(TAG)) paste0("_", TAG) else ""))
    saveRDS(list(coefs = w$coefs, eq_tests = w$eq_tests, did_check = w$did_cmp,
                 event_fate = w$fate, fate_table = fate_wide, full_coefs = full_cf,
                 params = list(h = w$h, windows = WINDOWS, min_events = MIN_EVENTS, tag = TAG, score = SCORE,
                               pool = w$meta$pool, protocol = w$meta$protocol),
                 run_at = Sys.time()), out)
  }
}
```
