---
title: "Validating the matching algorithm against real bidding non-winners"
author: "Jack Mulqueeney"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    self_contained: true
    df_print: kable
knit: >
  (function(inputFile, encoding) {
    project_dir <- normalizePath(dirname(inputFile), mustWork = TRUE)
    while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
           dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)
    output_dir <- file.path(project_dir, "output", "docs")
    dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
    rmarkdown::render(
      inputFile,
      encoding = encoding,
      knit_root_dir = project_dir,
      output_dir = output_dir
    )
  })
---

<!--
WHAT THIS IS. The matching pipeline picks controls on an industry/kommune cascade plus closeness of
the pre-award FTE path. Nothing in it tests whether those controls behave like the ACTUAL
counterfactual. TED gives us one: firms that bid on the same lot and lost. This report compares
employment outcomes under the two control groups.

SCOPE: FTE ONLY. Eligibility, qscore distributions and covariate balance were all removed -- this
report now answers one question, which is whether the synthetic control reproduces the employment
path of the real losing bidder. The eligibility and balance diagnostics live in the build log of
code/matching/5_cobidder_stacks.R and in 05_cobidder_roster.rds, which carries the per-firm verdicts
(pool_side, buffer_ok, elig_pre, elig_post, eligible, in_both_roles) if they are wanted again.

INPUT. code/matching/5_cobidder_stacks.R builds ONE stack per (contract notice, winner) holding all
three groups -- the winner, its synthetic matched controls, and its real losing co-bidders -- at the
same t = 0, with employment for each:

  05_cobidder_panel.parquet   the regression-ready panel, one row per (event, firm, quarter)
  05_cobidder_roster.rds      one row per (event, firm): qscore, eligibility verdict, flags

  Rscript -e 'rmarkdown::render("code/analysis/estudy_matched_vs_cobidder_validation.Rmd")'

Parameters are VMC_* environment variables. This report is READ-ONLY with respect to the pipeline and
writes nothing under match_paths() unless VMC_SAVE=1.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# opts_knit$get("output.dir") is NULL when running chunks interactively, and nzchar(NULL) errors in
# a bare if(). Fall back to getwd(), then walk up to the .Rproj marker.
.od <- knitr::opts_knit$get("output.dir")
project_dir <- if (!is.null(.od) && nzchar(.od)) .od else getwd()
project_dir <- normalizePath(project_dir, mustWork = TRUE)
while (!file.exists(file.path(project_dir, "cvr-cleaning.Rproj")) &&
       dirname(project_dir) != project_dir) project_dir <- dirname(project_dir)

suppressPackageStartupMessages({
  library(data.table); library(arrow); library(ggplot2); library(knitr); library(fixest)
})
# Sourced, not match_setup(): that setwd()s and re-sources, hostile inside a knit.
source(file.path(project_dir, "config.R"))
source(file.path(project_dir, "code", "functions.R"))
source(file.path(project_dir, "code", "matching", "0_matching_utils.R"))

.envchr <- function(k, d) { v <- Sys.getenv(k, ""); if (nzchar(v)) v else d }
.envint <- function(k, d) { v <- Sys.getenv(k, ""); if (nzchar(v)) as.integer(v) else d }

TAG        <- .envchr("VMC_TAG", match_tag())
MIN_EVENTS <- .envint("VMC_MIN_EVENTS", 20L)     # mirrors MATCH_MIN_STACKS
SAVE       <- .envint("VMC_SAVE", 0L) == 1L

P   <- match_paths(TAG)
fmt <- function(x) formatC(x, big.mark = ",", format = "d")

# Fixed label order, so groups never swap colours between a table and the plot beside it.
CATS <- c(treated = "winner", found_control = "matched control", non_winner = "real co-bidder")
```

# Inputs and scope

```{r inputs}
meta <- read_obj(P$cobid_roster)
H    <- meta$h                         # from the build, never from the environment

# complete_stack: the event still holds all three groups after balancing. Everything runs on this set.
panel <- read_tab(P$cobid_panel)
d     <- panel[complete_stack == TRUE]
d[, series := factor(CATS[category], levels = unname(CATS))]

scope <- data.table(
  item = c("control pool", "scoring protocol", "window (+/- quarters)", "FTE floor",
           "artefact tag", "events built (notice x winner)",
           "events surviving the balance screen",
           "COMPLETE stacks (all three groups)", "panel rows"),
  value = c(meta$pool, meta$protocol, as.character(H), as.character(meta$min_fte),
            if (nzchar(TAG)) TAG else "(full run)",
            fmt(nrow(as.data.table(meta$events))),
            fmt(panel[, uniqueN(ev)]), fmt(d[, uniqueN(ev)]), fmt(nrow(d))))
kable(scope, caption = "Scope of this validation")
```

`r if (d[, uniqueN(ev)] < MIN_EVENTS) sprintf("**INSUFFICIENT EVENTS: %d complete stacks, below VMC_MIN_EVENTS = %d.** Everything below is reported for completeness but should not be interpreted.", d[, uniqueN(ev)], MIN_EVENTS) else ""`

# Median FTE by event time

**Medians, not means.** The winner size distribution spans three orders of magnitude (median 69,
p99 ~2,500, max ~4,000 FTE), so a mean of levels is a statement about the ten largest notices and
almost nothing else. The synthetic control pool reproduces the winners' median well and their right
tail badly — a registry screen on industry and kommune contains no firm the size of the largest
winners — so the two statistics tell opposite stories. The median is the honest one.

Each event contributes one value per group per quarter: the within-event mean over that group's firms
(the `weight` column, which sums to 1 per stack and group). The line is the median of those across
events, with the interquartile range shaded.

```{r series, fig.width = 10, fig.height = 5.5, fig.align = 'center'}
# one value per (event, group, quarter) first, so a 40-way tie counts once
ev_mean <- d[, .(fte = weighted.mean(fte, weight)), by = .(ev, category, series, event_time)]

series_med <- ev_mean[, .(med_fte = as.numeric(median(fte)),
                          p25     = as.numeric(quantile(fte, .25)),
                          p75     = as.numeric(quantile(fte, .75)),
                          n_evt   = uniqueN(ev)),
                      by = .(event_time, series)][order(series, event_time)]

ggplot(series_med, aes(event_time, med_fte, colour = series, fill = series)) +
  geom_ribbon(aes(ymin = p25, ymax = p75), alpha = 0.10, colour = NA) +
  geom_line(linewidth = 0.6) + geom_point(size = 1.1) +
  geom_vline(xintercept = -0.5, linetype = "dashed", colour = "grey40") +
  labs(title = sprintf("Median FTE by event time, %d complete stacks", d[, uniqueN(ev)]),
       subtitle = "Median across events of the within-event group mean; shaded = interquartile range",
       x = sprintf("Quarters relative to award (+/-%d)", H), y = "FTE", colour = NULL, fill = NULL,
       caption = paste("Not the main pipeline's estimand: the event grain here is the LOT, so a",
                       "winner of several lots appears once per lot.")) +
  theme_light(base_size = 11) +
  theme(plot.title = element_text(face = "bold"), legend.position = "top",
        plot.caption = element_text(hjust = 0))

kable(dcast(series_med, event_time ~ series, value.var = "med_fte"), digits = 1,
      caption = "Median FTE by event time")
```

## Size relative to the winner

The scale-free version of the same picture, and the one that says whether each control group is the
right *size*. Computed per event and then medianed, so it is unaffected by the tail that breaks the
level mean. A group tracking the winner sits on 1.

```{r series-ratio, fig.width = 10, fig.height = 4.5, fig.align = 'center'}
# dcast on `category`, not `series`: the labels contain spaces
rat <- dcast(ev_mean, ev + event_time ~ category, value.var = "fte")
rat[, `:=`(`matched control` = found_control / treated,
           `real co-bidder`  = non_winner    / treated)]
rl <- melt(rat, id.vars = "event_time",
           measure.vars = c("matched control", "real co-bidder"),
           variable.name = "series", value.name = "ratio")

rat_med <- rl[is.finite(ratio), .(med = as.numeric(median(ratio)),
                                  p25 = as.numeric(quantile(ratio, .25)),
                                  p75 = as.numeric(quantile(ratio, .75))),
              by = .(event_time, series)][order(series, event_time)]

ggplot(rat_med, aes(event_time, med, colour = series, fill = series)) +
  geom_hline(yintercept = 1, colour = "grey50") +
  geom_ribbon(aes(ymin = p25, ymax = p75), alpha = 0.10, colour = NA) +
  geom_line(linewidth = 0.6) + geom_point(size = 1.1) +
  geom_vline(xintercept = -0.5, linetype = "dashed", colour = "grey40") +
  labs(title = "Control group size relative to the winner",
       subtitle = "Median across events of (group FTE / winner FTE); shaded = interquartile range",
       x = sprintf("Quarters relative to award (+/-%d)", H), y = "Ratio to winner FTE",
       colour = NULL, fill = NULL) +
  theme_light(base_size = 11) +
  theme(plot.title = element_text(face = "bold"), legend.position = "top")

kable(dcast(rat_med, event_time ~ series, value.var = "med"), digits = 3,
      caption = "Median size relative to the winner")
```

# Event studies: the same winners, two control groups

Two estimations on the **same stacks**, differing only in which rows are kept. That is the point of
building the groups together: the contrast between the two lines is the control group and nothing
else — same notices, same winners, same window, same weights.

## Specification

Let $i$ index firms, $e$ a stack (one contract notice $\times$ winner), and $t$ a calendar quarter.
$T_e$ is the award quarter of stack $e$'s notice, so event time is $k = t - T_e$, and the panel is
balanced on $k \in \{-h, \dots, h\}$ with $h = `r H`$. $D_i = 1$ for the winner of the stack and $0$
for its controls. Then

$$
y_{iet} \;=\; \sum_{\substack{k=-h \\ k \neq -1}}^{h} \beta_k \bigl(\mathbf{1}[t - T_e = k] \cdot D_i\bigr)
\;+\; \delta D_i \;+\; \theta_k \;+\; \varepsilon_{iet}
$$

| term | what it is | in code |
|---|---|---|
| $y_{iet}$ | FTE, and $\log$ FTE as a second outcome | `fte`, `log(fte)` |
| $\beta_k$ | the estimand: the winner-vs-control gap at event time $k$, relative to $k = -1$ | `i(event_time, treated, ref = "-1")` |
| $\delta D_i$ | treated main effect — the constant level difference between the two groups | `treated` |
| $\theta_k$ | event-time main effects, common to both groups | `event_time` |

**The $\beta_k$ compute differences in means between the treated and control groups.** There is no firm fixed effect and no calendar-time fixed effect: the only two absorbed terms are the group level and the event-time profile. A later diagnostic confirms the equality (it is convenient to use regression functions since we can easily compute standard errors and hypothesis tests).

**Weights** are $w_{ie} = 1 / n_{e,c(i)}$, where $n_{e,c}$ is the number of firms in group $c$ of
stack $e$. Each of a stack's sides therefore sums to $1$ in every period, so a notice that tied forty
controls at rank 1 does not outvote a notice with one real co-bidder — and because the weights are
defined per (stack, group), the property survives filtering to any two of the three groups, with
nothing to rebuild.

**Standard errors** are clustered on `cvr`, set once as `CL` in the first chunk below and reused by
every fit, so the intervals on the plots and the p-values in the tests can never come from different
assumptions. Clustering on the firm is the dimension that matters most here: the event grain is the
lot, so a winner of four lots contributes the same firm-quarters to four stacks, and a firm can be a
control for dozens of events — `~ cvr` is exactly what absorbs that repetition.
```{r es-prep}
# One definition for every fit: the split fits draw the CIs, the stacked fits the p-values.
CL <- ~ cvr                       # ~ lot_key + cvr to add the notice dimension

# Winner rows are deliberately duplicated across the two stacks. Fine under split = ~sample, which
# fits each separately -- but never pool reg_data into one regression without dropping a copy.
nw_d <- d[category %chin% c("treated", "non_winner")][,    sample := "non_winner_stack"]
sw_d <- d[category %chin% c("treated", "found_control")][, sample := "synthetic_stack"]
reg_data <- rbindlist(list(nw_d, sw_d), use.names = TRUE, fill = TRUE)
reg_data[, sample := factor(sample,
                            levels = c("synthetic_stack", "non_winner_stack"),
                            labels = c("Synthetic matched control", "Real losing co-bidder"))]

# Both stacks must rest on the SAME events, or the gap between the lines is part sample composition.
spec_tab <- reg_data[complete_stack == TRUE,
                     .(events = uniqueN(ev), firms = uniqueN(cvr), rows = .N), by = sample]
kable(spec_tab, caption = "What each specification is estimated on -- the event counts must match")
stopifnot(spec_tab[, uniqueN(events)] == 1L)
```

```{r es-fit}
mods <- feols(fte ~ i(event_time, treated, ref = "-1") |
                treated + event_time,
              data = reg_data[complete_stack == TRUE, ],
              split = ~sample,
              cluster = CL,
              weights = ~weight)

log_mods <- feols(log(fte) ~ i(event_time, treated, ref = "-1") |
                    treated + event_time,
                  data = reg_data[complete_stack == TRUE, ],
                  split = ~sample,
                  cluster = CL,
                  weights = ~weight)

# t = -1 is the omitted base period, added back at zero so every path is anchored alike.
# A fixest_multi is indexed by POSITION: m[["label"]] errors. Hence seq_along() plus names()[i],
# with the "sample: " prefix stripped.
tidy_es <- function(m, outcome) {
  lbl <- sub("^[^:]+: ", "", names(m))
  stopifnot(length(lbl) == length(m))
  rbindlist(lapply(seq_along(m), function(i) {
    ct <- as.data.table(coeftable(m[[i]]), keep.rownames = "term")[grepl("event_time", term)]
    ct[, event_time := as.integer(gsub(".*event_time::(-?[0-9]+).*", "\\1", term))]
    rbind(ct[, .(event_time, est = Estimate, se = `Std. Error`)],
          data.table(event_time = -1L, est = 0, se = 0))[
            , `:=`(control = lbl[i], outcome = outcome)]
  }))
}
coefs <- rbind(tidy_es(mods, "FTE (level)"), tidy_es(log_mods, "log FTE"))
coefs[, `:=`(lo = est - 1.96 * se, hi = est + 1.96 * se)]
coefs[, control := gsub("sample; sample: ", "", control)]
setorder(coefs, outcome, control, event_time)
```

```{r es-stack}
# Both designs in ONE fit, so Cov(beta_syn, beta_cob) exists; split = ~sample gives no such term.
# Every FE carries ^sample -- the winner rows are duplicated, so a shared FE would pool them and force
# beta_syn == beta_cob exactly. The clustering is NOT interacted: that is what makes the covariance.
rd <- reg_data[complete_stack == TRUE]
rd[, D_syn := as.integer(treated == 1L & sample == "Synthetic matched control")]
rd[, D_cob := as.integer(treated == 1L & sample == "Real losing co-bidder")]

st     <- feols(fte ~ i(event_time, D_syn, ref = "-1") + i(event_time, D_cob, ref = "-1") |
                  treated^sample + event_time^sample,
                data = rd, cluster = CL, weights = ~weight)
st_log <- feols(log(fte) ~ i(event_time, D_syn, ref = "-1") + i(event_time, D_cob, ref = "-1") |
                  treated^sample + event_time^sample,
                data = rd, cluster = CL, weights = ~weight)

# If the stacked estimates do not reproduce the split ones, an FE was left un-interacted.
.pick <- function(m, sfx) {
  ct <- as.data.table(coeftable(m), keep.rownames = "term")
  ct <- ct[grepl(sprintf("^event_time::-?[0-9]+:%s$", sfx), term)]
  ct[, k := as.integer(gsub("^event_time::(-?[0-9]+):.*$", "\\1", term))]
  ct[order(k), Estimate]
}
stack_gap <- max(abs(.pick(st, "D_syn") - coefs[outcome == "FTE (level)" &
                          control == "Synthetic matched control" & event_time != -1L][
                          order(event_time), est]),
                 abs(.pick(st, "D_cob") - coefs[outcome == "FTE (level)" &
                          control == "Real losing co-bidder" & event_time != -1L][
                          order(event_time), est]))
stopifnot(stack_gap < 1e-8)

# H0: beta_syn_k = beta_cob_k. Joint over every k in the period, and on their average (1 df).
wald_eq <- function(m, period, label) {
  b <- coef(m); V <- vcov(m); nm <- names(b)
  syn <- grep("^event_time::-?[0-9]+:D_syn$", nm, value = TRUE)
  cob <- sub("D_syn$", "D_cob", syn)
  k   <- as.integer(gsub("^event_time::(-?[0-9]+):.*$", "\\1", syn))
  sel <- if (identical(period, "pre")) k < 0L else k >= 0L
  syn <- syn[sel]; cob <- cob[sel]; kk <- sort(k[sel])
  stopifnot(length(syn) > 0L, all(cob %in% nm))

  R <- matrix(0, length(syn), length(b), dimnames = list(NULL, nm))
  for (j in seq_along(syn)) { R[j, syn[j]] <- 1; R[j, cob[j]] <- -1 }
  Rb <- R %*% b; VR <- R %*% V %*% t(R)
  W  <- as.numeric(t(Rb) %*% solve(VR) %*% Rb); q <- nrow(R)

  Ra <- matrix(colMeans(R), 1)                       # the same R, collapsed to the average
  da <- as.numeric(Ra %*% b); sa <- sqrt(as.numeric(Ra %*% V %*% t(Ra)))

  data.table(outcome = label, period = period,
             k = sprintf("%d..%d", min(kk), max(kk)),
             joint_df = q, joint_chisq = round(W, 2),
             joint_p = signif(pchisq(W, q, lower.tail = FALSE), 3),
             avg_diff = round(da, 4), avg_se = round(sa, 4),
             avg_chisq = round((da / sa)^2, 2),
             avg_p = signif(pchisq((da / sa)^2, 1, lower.tail = FALSE), 3))
}

eq_tests <- rbindlist(list(
  wald_eq(st,     "pre",  "FTE (level)"), wald_eq(st,     "post", "FTE (level)"),
  wald_eq(st_log, "pre",  "log FTE"),     wald_eq(st_log, "post", "log FTE")))

# One-line summary of the post-period tests, for the plot titles. Built from eq_tests rather than
# recomputed, so a figure can never disagree with the table it sits above.
.fp <- function(x) ifelse(x < 0.001, "< 0.001", sprintf("= %.3f", x))
eq_note <- function(out) {
  e <- eq_tests[outcome == out & period == "post"]
  sprintf("Post-period H0 the two designs agree:  joint chi2(%d) p %s   |   average p %s",
          e$joint_df, .fp(e$joint_p), .fp(e$avg_p))
}
```

## {.tabset}

### FTE (level)

```{r es-plot-fte, fig.width = 9, fig.height = 5.5, fig.align = 'center'}
iplot(mods,
      main = paste0("Winner vs synthetic control and real co-bidder\n", eq_note("FTE (level)")),
      xlab = "Quarters relative to award",
      ylab = "Effect on FTE",
      pt.join = TRUE)
legend("topleft", legend = levels(reg_data$sample), col = 1:2, pch = 20, lwd = 1, bty = "n")
```

### log FTE

```{r es-plot-log, fig.width = 9, fig.height = 5.5, fig.align = 'center'}
iplot(log_mods,
      main = paste0("Winner vs synthetic control and real co-bidder\n", eq_note("log FTE")),
      xlab = "Quarters relative to award",
      ylab = "Effect on log(FTE)",
      pt.join = TRUE)
legend("topleft", legend = levels(reg_data$sample), col = 1:2, pch = 20, lwd = 1, bty = "n")
```

### Overlay

```{r es-plot-overlay, fig.width = 10, fig.height = 5.5, fig.align = 'center'}
notes <- coefs[, .(lab = eq_note(outcome[1])), by = outcome]
notes <- merge(notes, coefs[, .(x = min(event_time), y = max(hi)), by = outcome], by = "outcome")

ggplot(coefs, aes(event_time, est, colour = control, fill = control)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_text(data = notes, aes(x, y, label = lab), inherit.aes = FALSE,
            hjust = 0, vjust = 1, size = 2.9, colour = "grey25") +
  geom_vline(xintercept = -0.5, linetype = "dashed", colour = "grey40") +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.12, colour = NA) +
  geom_line() + geom_point(size = 1.1) +
  facet_wrap(~ outcome, scales = "free_y") +
  labs(title = "Same winners, two control groups",
       subtitle = "Shaded = 95% CI, clustered by lot and firm. t = -1 omitted",
       x = "Quarters relative to award", y = "Coefficient", colour = NULL, fill = NULL) +
  theme_light(base_size = 11) + theme(legend.position = "top")
```

### Coefficients

```{r es-table}
kable(dcast(coefs[outcome == "log FTE"], event_time ~ control, value.var = "est"), digits = 3,
      caption = "log FTE event-study coefficients by control group")
```

## {-}

## Do the two designs agree?

Fitted once with both designs in a single regression, so $\mathrm{Cov}(\hat\beta^{syn}_k,
\hat\beta^{cob}_k)$ exists — with `split = ~sample` it does not, and there is then no standard error
for the difference. Point estimates are identical to the split fits (asserted above), so this tests
exactly the paths plotted.

Two nulls per period. **Joint:** $\beta^{syn}_k = \beta^{cob}_k$ at every $k$. **Average:** the same
equality on the mean over those $k$, one restriction. The joint null is the stronger one, so it can
reject while the average does not — that means the designs disagree about *shape*, not magnitude.

```{r es-tests}
kable(eq_tests, caption = paste("H0: the two control groups imply the same treatment effect.",
                                "Chi-squared tests, clustered on the firm."))
```

**The pre-period row is not a placebo.** The matcher selects controls on the FTE path across the whole
of $[-h,-1]$ under the `full_full` protocol, so $\beta^{syn}_k$ is near zero there by construction
while $\beta^{cob}_k$ is unconstrained. A rejection in the pre period says the matching worked, not
that the designs disagree. Only the post row is informative. A genuine placebo would need the
`full_firsthalf` protocol, which ranks on the early pre-period and leaves $[-h/2,-1]$ unused.

# Are these coefficients just differences in means?

Yes, exactly. With `treated + event_time` as the only fixed effects the model is **saturated** in the
(treated $\times$ event time) cells: $2 \times (2h{+}1) = `r 2 * (2 * H + 1)`$ cells against
$1 + (2h{+}1) + 2h = `r 1 + (2 * H + 1) + 2 * H`$ free parameters. A saturated model reproduces the
weighted cell means exactly, so

$$\hat\beta_k \;=\; \left[\bar y_T(k) - \bar y_C(k)\right] - \left[\bar y_T(-1) - \bar y_C(-1)\right]$$

with $\bar y$ the weighted mean over a (group, event time) cell. This section recomputes that by hand
— no regression — and checks it against the coefficients the plots above are drawn from.

It is worth doing rather than asserting. It pins down what the estimates are, it catches a weighting
or balance error that would otherwise surface only as a puzzling coefficient, and it means any
$\beta_k$ that looks odd can be traced to the two cell means behind it.

```{r did-check}
# hand-computed weighted DiD, no regression involved
did_by_hand <- function(dat, samp, yvar) {
  cm <- dat[sample == samp, .(y = weighted.mean(get(yvar), weight)), by = .(treated, event_time)]
  wd <- dcast(cm, event_time ~ treated, value.var = "y")
  setnames(wd, c("0", "1"), c("ctrl", "trt"))
  base <- wd[event_time == -1L, trt - ctrl]
  wd[, .(event_time, ctrl, trt, did = (trt - ctrl) - base)][order(event_time)]
}

rd[, log_fte := log(fte)]
did_cmp <- rbindlist(lapply(levels(rd$sample), function(lbl) rbindlist(list(
  did_by_hand(rd, lbl, "fte")[,     `:=`(control = lbl, outcome = "FTE (level)")],
  did_by_hand(rd, lbl, "log_fte")[, `:=`(control = lbl, outcome = "log FTE")]))))

# `coefs` is what the tabset plots, read off the fitted objects
did_cmp <- merge(did_cmp, coefs[, .(control, outcome, event_time, fitted = est)],
                 by = c("control", "outcome", "event_time"))
did_cmp[, gap := did - fitted]

kable(did_cmp[, .(periods = .N, max_abs_gap = max(abs(gap))), by = .(outcome, control)],
      digits = 12,
      caption ="Hand-computed difference-in-differences against the fitted coefficients.")
stopifnot(did_cmp[, max(abs(gap))] < 1e-8)
```

The cell means themselves, which is where any surprising coefficient should be read from:

```{r did-cells}
kable(dcast(did_cmp[outcome == "FTE (level)"], event_time ~ control,
            value.var = c("trt", "ctrl", "did")),
      digits = 2,
      caption = paste("Weighted mean FTE in each cell and the resulting DiD, by event time.",
                      "trt = winners, ctrl = that design's control group."))
```

```{r save, include=FALSE}
if (SAVE) {
  out <- file.path(P$dir, sprintf("05_validation_cobidder%s.rds",
                                  if (nzchar(TAG)) paste0("_", TAG) else ""))
  saveRDS(list(scope = scope, spec = spec_tab, series = series_med, ratio = rat_med,
               coefs = coefs, eq_tests = eq_tests, did_check = did_cmp,
               params = list(h = H, min_events = MIN_EVENTS, tag = TAG,
                             pool = meta$pool, protocol = meta$protocol),
               run_at = Sys.time()), out)
}
```
